---
title: "Immune marker data"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: cerulean #darkly
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
h1.title {
  font-size: 25px;
}
.figure {
   margin-top: 25px;
   <!-- margin-bottom: 100px; -->
}

table {
    margin-top: 25px;
    <!-- margin-bottom: 100px !important; -->
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      # fig.width = 7, fig.height = 5, 
                      fig.align='center'#, fig.show='hold'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

<style>
div.blue { background-color:#0099CC; border-radius: 5px; padding: 20px; font-size: 38px}
</style>
<div class = "blue">

<span style="color: white;">Heatmaps</span>

</div>
<br>

```{r library, include=FALSE}
# library(drake)
library(tidyverse)
library(data.table)
# library(VennDiagram)
library(gtsummary)
library(survival)
library(survminer)
library(psych)
# library(corrplot)
# library(ggcorrplot)
library(mclust)
library(sensemakr)
```

```{r load}
# loadd(clinical_data, ROI_tumor ,ROI_stroma ,ROI_total,
#       cases_match)

ROI_global <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_AACES_NCOCS/ROI_global.rds")
clinical_data <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_AACES_NCOCS/clinical_data.rds")

# Rewove patients not matched or lost match
ROI_global <- left_join(ROI_global, clinical_data, by="suid") %>% drop_na(pair_id) %>% 
  group_by(pair_id) %>% 
  mutate(have_a_match = dense_rank(interaction(suid, pair_id))) %>% 
  group_by(pair_id) %>% 
  mutate(is_paired = max(have_a_match)) %>% 
  filter(is_paired == 2) %>% 
  select(pair_id, everything(), -c(is_paired, have_a_match)) %>% 
  ungroup()

# markers_match <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_AACES_NCOCS/markers_match.rds")
path <- fs::path("","Volumes","Peres_Research","Christelle Colin-Leitzinger", "IF_AACES_NCOCS", "Disparities manuscript", "Figures")



```
<br>
<br>

***

```{r summarize mean}
markers_ROIi <- ROI_global %>% 
  filter(intratumoral_i_vs_peripheral_p_ == "Intratumoral") %>% 
  group_by(suid) %>% 
  summarize(
    mean_tumor = mean(percent_tumor),
    mean_stroma = mean(percent_stroma),
    mean_total = mean(percent_total),
    # variance_tumor = var(percent_tumor),
    # variance_stroma = var(percent_stroma),
    percent_CD3_tumor = mean(tumor_percent_cd3_opal_650_positive_cells),
    percent_CD8_tumor = mean(tumor_percent_cd8_opal_570_positive_cells),
    percent_CD3_CD8_tumor = mean(tumor_percent_cd3plus_cd8plus_positive_cells),
    percent_FoxP3_tumor = mean(tumor_percent_foxp3_opal_540_positive_cells),
    percent_CD3_FoxP3_tumor = mean(tumor_percent_cd3plus_foxp3plus_positive_cells),
    percent_CD11b_tumor = mean(tumor_percent_cd11b_opal_620_positive_cells),
    percent_CD15_tumor = mean(tumor_percent_cd15_opal_520_positive_cells),
    percent_CD11b_CD15_tumor = mean(tumor_percent_cd11bplus_cd15plus_positive_cells),
    percent_CD3_stroma = mean(stroma_percent_cd3_opal_650_positive_cells),
    percent_CD8_stroma = mean(stroma_percent_cd8_opal_570_positive_cells),
    percent_CD3_CD8_stroma = mean(stroma_percent_cd3plus_cd8plus_positive_cells),
    percent_FoxP3_stroma = mean(stroma_percent_foxp3_opal_540_positive_cells),
    percent_CD3_FoxP3_stroma = mean(stroma_percent_cd3plus_foxp3plus_positive_cells),
    percent_CD11b_stroma = mean(stroma_percent_cd11b_opal_620_positive_cells),
    percent_CD15_stroma = mean(stroma_percent_cd15_opal_520_positive_cells),
    percent_CD11b_CD15_stroma = mean(stroma_percent_cd11bplus_cd15plus_positive_cells),
    
    percent_CD3_total = mean(percent_cd3_opal_650_positive_cells),
    percent_CD8_total = mean(percent_cd8_opal_570_positive_cells),
    percent_CD3_CD8_total = mean(percent_cd3plus_cd8plus_positive_cells),
    percent_FoxP3_total = mean(percent_foxp3_opal_540_positive_cells),
    percent_CD3_FoxP3_total = mean(percent_cd3plus_foxp3plus_positive_cells),
    percent_CD11b_total = mean(percent_cd11b_opal_620_positive_cells),
    percent_CD15_total = mean(percent_cd15_opal_520_positive_cells),
    percent_CD11b_CD15_total = mean(percent_cd11bplus_cd15plus_positive_cells)
  )
markers_ROIi$tumor_variation <- markers_ROIi$mean_tumor - mean(ROI_global$percent_tumor)
markers_ROIi$stroma_variation <- markers_ROIi$mean_stroma - mean(ROI_global$percent_stroma)
markers_ROIi$total_variation <- markers_ROIi$mean_stroma - mean(ROI_global$percent_stroma)
#
markers_ROIp <- ROI_global %>% 
  filter(intratumoral_i_vs_peripheral_p_ == "Peripheral") %>% 
  group_by(suid) %>% 
  summarize(
    mean_tumor = mean(percent_tumor),
    mean_stroma = mean(percent_stroma),
    mean_total = mean(percent_total),
    # variance_tumor = var(percent_tumor),
    # variance_stroma = var(percent_stroma),
    percent_CD3_tumor = mean(tumor_percent_cd3_opal_650_positive_cells),
    percent_CD8_tumor = mean(tumor_percent_cd8_opal_570_positive_cells),
    percent_CD3_CD8_tumor = mean(tumor_percent_cd3plus_cd8plus_positive_cells),
    percent_FoxP3_tumor = mean(tumor_percent_foxp3_opal_540_positive_cells),
    percent_CD3_FoxP3_tumor = mean(tumor_percent_cd3plus_foxp3plus_positive_cells),
    percent_CD11b_tumor = mean(tumor_percent_cd11b_opal_620_positive_cells),
    percent_CD15_tumor = mean(tumor_percent_cd15_opal_520_positive_cells),
    percent_CD11b_CD15_tumor = mean(tumor_percent_cd11bplus_cd15plus_positive_cells),
    percent_CD3_stroma = mean(stroma_percent_cd3_opal_650_positive_cells),
    percent_CD8_stroma = mean(stroma_percent_cd8_opal_570_positive_cells),
    percent_CD3_CD8_stroma = mean(stroma_percent_cd3plus_cd8plus_positive_cells),
    percent_FoxP3_stroma = mean(stroma_percent_foxp3_opal_540_positive_cells),
    percent_CD3_FoxP3_stroma = mean(stroma_percent_cd3plus_foxp3plus_positive_cells),
    percent_CD11b_stroma = mean(stroma_percent_cd11b_opal_620_positive_cells),
    percent_CD15_stroma = mean(stroma_percent_cd15_opal_520_positive_cells),
    percent_CD11b_CD15_stroma = mean(stroma_percent_cd11bplus_cd15plus_positive_cells),
    percent_CD3_total = mean(percent_cd3_opal_650_positive_cells),
    percent_CD8_total = mean(percent_cd8_opal_570_positive_cells),
    percent_CD3_CD8_total = mean(percent_cd3plus_cd8plus_positive_cells),
    percent_FoxP3_total = mean(percent_foxp3_opal_540_positive_cells),
    percent_CD3_FoxP3_total = mean(percent_cd3plus_foxp3plus_positive_cells),
    percent_CD11b_total = mean(percent_cd11b_opal_620_positive_cells),
    percent_CD15_total = mean(percent_cd15_opal_520_positive_cells),
    percent_CD11b_CD15_total = mean(percent_cd11bplus_cd15plus_positive_cells)
  )
markers_ROIp$tumor_variation <- markers_ROIp$mean_tumor - mean(ROI_global$percent_tumor)
markers_ROIp$stroma_variation <- markers_ROIp$mean_stroma - mean(ROI_global$percent_stroma)
markers_ROIp$total_variation <- markers_ROIp$mean_total - mean(ROI_global$percent_total)

# Join Intratumoral and Peropheral ROI
markers_ROI <- full_join(markers_ROIi, markers_ROIp,
                         by= "suid", suffix= c(".i", ".p"))
markers_ROI <- left_join(markers_ROI, clinical_data, by="suid")
# clust_markers <- markers_ROI
```

<!-- Category with absent cells -->

<!-- That is done without removing double stained from single. -->

```{r new median}
markers_ROI <- markers_ROI %>% 
  
  mutate(CD3_tumor.i = case_when(
    
    percent_CD3_tumor.i <= 1      ~ "low",
    percent_CD3_tumor.i > 1       ~ "high"
  ), CD3_tumor.i = factor(CD3_tumor.i, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_tumor.i = case_when(
    percent_CD3_CD8_tumor.i <= 1      ~ "low",
    percent_CD3_CD8_tumor.i > 1       ~ "high"
  ), CD3_CD8_tumor.i = factor(CD3_CD8_tumor.i, levels = c("low","high"))) %>% 
  mutate(CD3_FoxP3_tumor.i = case_when(
    percent_CD3_FoxP3_tumor.i <= 1      ~ "low",
    percent_CD3_FoxP3_tumor.i > 1       ~ "high"
  ), CD3_FoxP3_tumor.i = factor(CD3_FoxP3_tumor.i, levels = c("low","high"))) %>% 
  mutate(CD11b_tumor.i = case_when(
    percent_CD11b_tumor.i == 0      ~ "Absence",
    percent_CD11b_tumor.i > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_CD15_tumor.i = case_when(
    percent_CD11b_CD15_tumor.i == 0      ~ "Absence",
    percent_CD11b_CD15_tumor.i > 0       ~ "Presence"
  )) %>% 
  
  mutate(CD3_stroma.i = case_when(
    percent_CD3_stroma.i <= 1      ~ "low",
    percent_CD3_stroma.i > 1       ~ "high"
  ), CD3_stroma.i = factor(CD3_stroma.i, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_stroma.i = case_when(
    percent_CD3_CD8_stroma.i <= 1      ~ "low",
    percent_CD3_CD8_stroma.i > 1       ~ "high"
  ), CD3_CD8_stroma.i = factor(CD3_CD8_stroma.i, levels = c("low","high"))) %>% 
  mutate(CD3_FoxP3_stroma.i = case_when(
    percent_CD3_FoxP3_stroma.i <= 1      ~ "low",
    percent_CD3_FoxP3_stroma.i > 1       ~ "high"
  ), CD3_FoxP3_stroma.i = factor(CD3_FoxP3_stroma.i, levels = c("low","high"))) %>% 
  mutate(CD11b_stroma.i = case_when(
    percent_CD11b_stroma.i == 0      ~ "Absence",
    percent_CD11b_stroma.i > 0       ~ "Presence"
  )) %>%
  mutate(CD11b_CD15_stroma.i = case_when(
    percent_CD11b_CD15_stroma.i == 0      ~ "Absence",
    percent_CD11b_CD15_stroma.i > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_stroma.i3 = case_when(
    percent_CD11b_stroma.i <= 1      ~ "low",
    percent_CD11b_stroma.i > 1       ~ "high"
  ), CD11b_stroma.i3 = factor(CD11b_stroma.i3, levels = c("low","high"))) %>%
  mutate(CD11b_CD15_stroma.i3 = case_when(
    percent_CD11b_CD15_stroma.i <= 1      ~ "low",
    percent_CD11b_CD15_stroma.i > 1       ~ "high"
  ), CD11b_CD15_stroma.i3 = factor(CD11b_CD15_stroma.i3, levels = c("low","high"))) %>% 
  mutate(CD3_total.i = case_when(
    percent_CD3_total.i <= 1      ~ "low",
    percent_CD3_total.i > 1       ~ "high"
  ), CD3_total.i = factor(CD3_total.i, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_total.i = case_when(
    percent_CD3_CD8_total.i <= 1      ~ "low",
    percent_CD3_CD8_total.i > 1       ~ "high"
  ), CD3_CD8_total.i = factor(CD3_CD8_total.i, levels = c("low","high"))) %>% 
  mutate(CD3_FoxP3_total.i = case_when(
    percent_CD3_FoxP3_total.i <= 1      ~ "low",
    percent_CD3_FoxP3_total.i > 1       ~ "high"
  ), CD3_FoxP3_total.i = factor(CD3_FoxP3_total.i, levels = c("low","high"))) %>% 
  mutate(CD11b_total.i = case_when(
    percent_CD11b_total.i == 0      ~ "Absence",
    percent_CD11b_total.i > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_CD15_total.i = case_when(
    percent_CD11b_CD15_total.i == 0      ~ "Absence",
    percent_CD11b_CD15_total.i > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_total.i3 = case_when(
    percent_CD11b_total.i <= 1      ~ "low",
    percent_CD11b_total.i > 1       ~ "high"
  ), CD11b_total.i3 = factor(CD11b_total.i3, levels = c("low","high"))) %>% 
  mutate(CD11b_CD15_total.i3 = case_when(
    percent_CD11b_CD15_total.i <= 1      ~ "low",
    percent_CD11b_CD15_total.i > 1       ~ "high"
  ), CD11b_CD15_total.i3 = factor(CD11b_CD15_total.i3, levels = c("low","high"))) %>% 
  
  
  mutate(CD3_tumor.p = case_when(
    percent_CD3_tumor.p <= 1      ~ "low",
    percent_CD3_tumor.p > 1       ~ "high"
  ), CD3_tumor.p = factor(CD3_tumor.p, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_tumor.p = case_when(
    percent_CD3_CD8_tumor.p <= 1      ~ "low",
    percent_CD3_CD8_tumor.p > 1       ~ "high"
  ), CD3_CD8_tumor.p = factor(CD3_CD8_tumor.p, levels = c("low","high"))) %>% 
  mutate(CD3_FoxP3_tumor.p = case_when(
    percent_CD3_FoxP3_tumor.p <= 1      ~ "low",
    percent_CD3_FoxP3_tumor.p > 1       ~ "high"
  ), CD3_FoxP3_tumor.p = factor(CD3_FoxP3_tumor.p, levels = c("low","high"))) %>% 
  mutate(CD11b_tumor.p = case_when(
    percent_CD11b_tumor.p == 0      ~ "Absence",
    percent_CD11b_tumor.p > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_CD15_tumor.p = case_when(
    percent_CD11b_CD15_tumor.p == 0      ~ "Absence",
    percent_CD11b_CD15_tumor.p > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_tumor.p3 = case_when(
    percent_CD11b_tumor.p <= 1      ~ "low",
    percent_CD11b_tumor.p > 1         ~ "high"
  ), CD11b_tumor.p3 = factor(CD11b_tumor.p3, levels = c("low","high"))) %>% 
  mutate(CD11b_CD15_tumor.p3 = case_when(
    percent_CD11b_CD15_tumor.p <= 1      ~ "low",
    percent_CD11b_CD15_tumor.p > 1       ~ "high"
  ), CD11b_CD15_tumor.p3 = factor(CD11b_CD15_tumor.p3, levels = c("low","high"))) %>% 
  mutate(CD3_stroma.p = case_when(
    percent_CD3_stroma.p <= 1      ~ "low",
    percent_CD3_stroma.p > 1       ~ "high"
  ), CD3_stroma.p = factor(CD3_stroma.p, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_stroma.p = case_when(
    percent_CD3_CD8_stroma.p <= 1      ~ "low",
    percent_CD3_CD8_stroma.p > 1       ~ "high"
  ), CD3_CD8_stroma.p = factor(CD3_CD8_stroma.p, levels = c("low","high"))) %>% 
  mutate(CD3_FoxP3_stroma.p = case_when(
    percent_CD3_FoxP3_stroma.p <= 1      ~ "low",
    percent_CD3_FoxP3_stroma.p > 1       ~ "high"
  ), CD3_FoxP3_stroma.p = factor(CD3_FoxP3_stroma.p, levels = c("low","high"))) %>% 
  mutate(CD11b_stroma.p = case_when(
    percent_CD11b_stroma.p == 0      ~ "Absence",
    percent_CD11b_stroma.p > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_CD15_stroma.p = case_when(
    percent_CD11b_CD15_stroma.p == 0      ~ "Absence",
    percent_CD11b_CD15_stroma.p > 0       ~ "Presence"
  )) %>% 
    mutate(CD11b_stroma.p3 = case_when(
    percent_CD11b_stroma.p <= 1      ~ "low",
    percent_CD11b_stroma.p > 1       ~ "high"
  ), CD11b_stroma.p3 = factor(CD11b_stroma.p3, levels = c("low","high"))) %>% 
  mutate(CD11b_CD15_stroma.p3 = case_when(
    percent_CD11b_CD15_stroma.p <= 1      ~ "low",
    percent_CD11b_CD15_stroma.p > 1       ~ "high"
  ), CD11b_CD15_stroma.p3 = factor(CD11b_CD15_stroma.p3, levels = c("low","high"))) %>% 
  mutate(CD3_total.p = case_when(
    percent_CD3_total.p <= 1      ~ "low",
    percent_CD3_total.p > 1       ~ "high"
  ), CD3_total.p = factor(CD3_total.p, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_total.p = case_when(
    percent_CD3_CD8_total.p <= 1      ~ "low",
    percent_CD3_CD8_total.p > 1       ~ "high"
  ), CD3_CD8_total.p = factor(CD3_CD8_total.p, levels = c("low","high"))) %>% 
  mutate(CD3_FoxP3_total.p = case_when(
    percent_CD3_FoxP3_total.p <= 1      ~ "low",
    percent_CD3_FoxP3_total.p > 1       ~ "high"
  ), CD3_FoxP3_total.p = factor(CD3_FoxP3_total.p, levels = c("low","high"))) %>% 
  mutate(CD11b_total.p = case_when(
    percent_CD11b_total.p == 0      ~ "Absence",
    percent_CD11b_total.p > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_CD15_total.p = case_when(
    percent_CD11b_CD15_total.p == 0      ~ "Absence",
    percent_CD11b_CD15_total.p > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_total.p3 = case_when(
    percent_CD11b_total.p <= 1      ~ "low",
    percent_CD11b_total.p > 1       ~ "high"
  ), CD11b_total.p3 = factor(CD11b_total.p3, levels = c("low","high"))) %>% 
  mutate(CD11b_CD15_total.p3 = case_when(
    percent_CD11b_CD15_total.p <= 1      ~ "low",
    percent_CD11b_CD15_total.p > 1       ~ "high"
  ), CD11b_CD15_total.p3 = factor(CD11b_CD15_total.p3, levels = c("low","high"))) 



# for(i in 1:length(colnames(markers_ROI))) {
#   
#   
#   if(str_detect(markers_ROI[,i], "percent_CD|percent_Fox")) {
#     
#     markers_ROI <- markers_ROI %>%
#       mutate(.[,i] = case_when(
#     [,i] <= median([,i][[,i]>0])      ~ "low",
#     [,i] > median([,i][[,i]>0])      ~ "high",
#     [,i] == 0                         ~ "zero"
#   ))
#     
#     
#   }
#   print(markers_ROI[,i])
# }
# 
# for (v in colnames(df[ ,grepl(".x",names(df))])) {
#   print(v)
#   df$v <- ifelse(is.na(df$v), ols$coefficients[1]+ols$coefficients[2]*log(df$gsub(".x",".y",v)), df$v)
# }
```

<!-- # Immunoscore -->
<!-- When we decided for every group I can put cluster and immunoscore together in the same table. -->
<!-- I took the immunoscore calculated on the mean of the 3 value per patient. -->
```{r immunoscore per patients mean}
markers_ROI <- markers_ROI %>% 
  mutate(percentile_score_CD3_i = ntile(percent_CD3_total.i, 100) ) %>% 
  mutate(percentile_score_CD3_p = ntile(percent_CD3_total.p, 100) ) %>% 
  mutate(percentile_score_CD8_i = ntile(percent_CD8_total.i, 100) ) %>% 
  mutate(percentile_score_CD8_p = ntile(percent_CD8_total.p, 100) ) 

markers_ROI <- markers_ROI %>%
  mutate(percentile_score_mean = rowMeans( markers_ROI[c("percentile_score_CD3_i", "percentile_score_CD3_p", 
                                                    "percentile_score_CD8_i", "percentile_score_CD8_p")] ))
markers_ROI <- markers_ROI %>%
  mutate(immunoscore_patients = case_when(
    percentile_score_mean <= 10        ~ 0,
    percentile_score_mean <= 25        ~ 1,
    percentile_score_mean <= 70        ~ 2,
    percentile_score_mean <= 95        ~ 3,
    percentile_score_mean > 95         ~ 4 
  )) %>% 
  mutate(immunoscore_patients = factor(immunoscore_patients)) %>% 
  mutate(immunoscore_2018lancet_patients = case_when(
    percentile_score_mean <= 25        ~ "Low",
    percentile_score_mean <= 70        ~ "Intermediate",
    percentile_score_mean > 70         ~ "High"
    )) %>% 
  mutate(immunoscore_2018lancet_patients = factor(immunoscore_2018lancet_patients, levels = c("Low", "Intermediate", "High"))) 
```


<!-- # Cluster -->

<!-- The count of cells double stained (for example CD3+CD8+) **ARE** subtracted from the single stain count (CD3 alone and CD8 alone) to avoid overlapping if we want to use them to cluster.   -->

```{r removing double stain from single stain count}
# markers_ROI <- markers_ROI %>%
#   mutate(percent_CD3_total.i = percent_CD3_total.i - percent_CD3_CD8_total.i - percent_CD3_FoxP3_total.i) %>%
#   mutate(percent_CD8_total.i = percent_CD8_total.i - percent_CD3_CD8_total.i) %>%
#   mutate(percent_FoxP3_total.i = percent_FoxP3_total.i - percent_CD3_FoxP3_total.i) %>%
#   mutate(percent_CD11b_total.i = percent_CD11b_total.i - percent_CD11b_CD15_total.i) %>%
#   mutate(percent_CD15_total.i = percent_CD15_total.i - percent_CD11b_CD15_total.i) %>%
# 
#   mutate(percent_CD3_tumor.i = percent_CD3_tumor.i - percent_CD3_CD8_tumor.i - percent_CD3_FoxP3_tumor.i) %>%
#   mutate(percent_CD8_tumor.i = percent_CD8_tumor.i - percent_CD3_CD8_tumor.i) %>%
#   mutate(percent_FoxP3_tumor.i = percent_FoxP3_tumor.i - percent_CD3_FoxP3_tumor.i) %>%
#   mutate(percent_CD11b_tumor.i = percent_CD11b_tumor.i - percent_CD11b_CD15_tumor.i) %>%
#   mutate(percent_CD15_tumor.i = percent_CD15_tumor.i - percent_CD11b_CD15_tumor.i) %>%
# 
#   mutate(percent_CD3_stroma.i = percent_CD3_stroma.i - percent_CD3_CD8_stroma.i - percent_CD3_FoxP3_stroma.i) %>%
#   mutate(percent_CD8_stroma.i = percent_CD8_stroma.i - percent_CD3_CD8_stroma.i) %>%
#   mutate(percent_FoxP3_stroma.i = percent_FoxP3_stroma.i - percent_CD3_FoxP3_stroma.i) %>%
#   mutate(percent_CD11b_stroma.i = percent_CD11b_stroma.i - percent_CD11b_CD15_stroma.i) %>%
#   mutate(percent_CD15_stroma.i = percent_CD15_stroma.i - percent_CD11b_CD15_stroma.i) %>%
# 
#   mutate(percent_CD3_total.p = percent_CD3_total.p - percent_CD3_CD8_total.p - percent_CD3_FoxP3_total.p) %>%
#   mutate(percent_CD8_total.p = percent_CD8_total.p - percent_CD3_CD8_total.p) %>%
#   mutate(percent_FoxP3_total.p = percent_FoxP3_total.p - percent_CD3_FoxP3_total.p) %>%
#   mutate(percent_CD11b_total.p = percent_CD11b_total.p - percent_CD11b_CD15_total.p) %>%
#   mutate(percent_CD15_total.p = percent_CD15_total.p - percent_CD11b_CD15_total.p) %>%
# 
#   mutate(percent_CD3_tumor.p = percent_CD3_tumor.p - percent_CD3_CD8_tumor.p - percent_CD3_FoxP3_tumor.p) %>%
#   mutate(percent_CD8_tumor.p = percent_CD8_tumor.p - percent_CD3_CD8_tumor.p) %>%
#   mutate(percent_FoxP3_tumor.p = percent_FoxP3_tumor.p - percent_CD3_FoxP3_tumor.p) %>%
#   mutate(percent_CD11b_tumor.p = percent_CD11b_tumor.p - percent_CD11b_CD15_tumor.p) %>%
#   mutate(percent_CD15_tumor.p = percent_CD15_tumor.p - percent_CD11b_CD15_tumor.p) %>%
# 
#   mutate(percent_CD3_stroma.p = percent_CD3_stroma.p - percent_CD3_CD8_stroma.p - percent_CD3_FoxP3_stroma.p) %>%
#   mutate(percent_CD8_stroma.p = percent_CD8_stroma.p - percent_CD3_CD8_stroma.p) %>%
#   mutate(percent_FoxP3_stroma.p = percent_FoxP3_stroma.p - percent_CD3_FoxP3_stroma.p) %>%
#   mutate(percent_CD11b_stroma.p = percent_CD11b_stroma.p - percent_CD11b_CD15_stroma.p) %>%
#   mutate(percent_CD15_stroma.p = percent_CD15_stroma.p - percent_CD11b_CD15_stroma.p)
```
<br>

## Cluster with a non-defined number of cluster **when looking at all intra/periph + tumor/stroma (CD3, CD3/8, CD3/FoxP3, CD11b, CD11b/15)**

```{r clustering}
set.seed(1234)

### Cluster for stroma/tumor in the intratumoral/peritumoral ROIs (include single and double staining, overall are excluded)
clust_markers <- markers_ROI %>% 
  filter(!is.na(markers_ROI$percent_CD3_CD8_tumor.i) & !is.na(markers_ROI$percent_CD3_CD8_tumor.p)) %>% 
  select(suid, c("percent_CD3_tumor.i", "percent_CD3_CD8_tumor.i", "percent_CD3_FoxP3_tumor.i", "percent_CD11b_tumor.i", "percent_CD11b_CD15_tumor.i",
                 "percent_CD3_stroma.i", "percent_CD3_CD8_stroma.i", "percent_CD3_FoxP3_stroma.i", "percent_CD11b_stroma.i", "percent_CD11b_CD15_stroma.i",
                 "percent_CD3_tumor.p", "percent_CD3_CD8_tumor.p", "percent_CD3_FoxP3_tumor.p", "percent_CD11b_tumor.p", "percent_CD11b_CD15_tumor.p",
                 "percent_CD3_stroma.p", "percent_CD3_CD8_stroma.p", "percent_CD3_FoxP3_stroma.p", "percent_CD11b_stroma.p", "percent_CD11b_CD15_stroma.p"
                 ))

clust <- Mclust(scale(clust_markers[,c(2:ncol(clust_markers))]))
summary(clust)

X <- clust_markers[,-1]
head(X)
BIC <- mclustBIC(X)
plot(BIC)
summary(BIC)
mod1 <- Mclust(X, x = BIC)
summary(mod1, parameters = TRUE)

clust_markers$clusters_all_IandP <- clust$classification
# clust_markers$clusters_all_IandP <- factor(clust_markers$clusters_all_IandP,
#                                            levels = c(1, 3, 2),
#                                            labels = c("low", "mid", "high"))
clust_markers$clusters_all_IandP <- factor(clust_markers$clusters_all_IandP,
                                           levels = c(1, 2, 3, 4, 5),
                                           labels = c("mid", "high", "mid-low", "mid-high", "low"))
clust_markers <- clust_markers %>% mutate(clusters_all_IandP = factor(clusters_all_IandP, levels = c("low", "mid-low", "mid", "mid-high", "high")))

clust_markers %>%
tidyr::gather(key = "markers_cat", value = "value",
              c("percent_CD3_tumor.p":"percent_CD11b_CD15_stroma.p")) %>%
  select(suid, clusters_all_IandP, markers_cat, value) %>%
  ggplot(aes(x=suid, y=value, group=markers_cat,  color=markers_cat))+
  geom_boxplot()+
  facet_grid(.~ clusters_all_IandP)
markers_ROI <- full_join(markers_ROI, clust_markers %>% select(suid, clusters_all_IandP), by = "suid")
# 
# 
# ### Cluster for tumor intratumoral all double positive "percent_CD3_CD8_tumor.i", "percent_CD3_FoxP3_tumor.i", "percent_CD11b_CD15_tumor.i"
# clust_markers <- markers_ROI %>% filter(!is.na(markers_ROI$percent_CD3_CD8_tumor.i ))
# clust <-
#   Mclust(clust_markers[,c("percent_CD3_CD8_tumor.i", "percent_CD3_FoxP3_tumor.i", "percent_CD11b_CD15_tumor.i")])
# summary(clust)
# clust_markers$dbl_pos <- clust$classification
# clust_markers$dbl_pos <- factor(clust_markers$dbl_pos,
#                                            levels = c(1, 2, 3),
#                                            labels = c("low", "high", "mid"))
# clust_markers <- clust_markers %>% mutate(dbl_pos = factor(dbl_pos, levels = c("low", "mid", "high")))
# 
# ### Cluster for tumor intratumoral CD3-CD8
# clust <- Mclust(clust_markers$percent_CD3_CD8_tumor.i)
# summary(clust)
# clust_markers$clusters_CD3CD8 <- clust$classification
# clust_markers$clusters_CD3CD8 <- factor(clust_markers$clusters_CD3CD8,
#                                            levels = c(1, 2, 3, 4, 5),
#                                            labels = c("low", "mid-low", "mid", "mid-high", "high"))
# 
# ### Cluster for tumor intratumoral CD3-FoxP3
# clust <- Mclust(clust_markers$percent_CD3_FoxP3_tumor.i)
# summary(clust)
# clust_markers$clusters_CD3FoxP3 <- clust$classification
# clust_markers$clusters_CD3FoxP3 <- factor(clust_markers$clusters_CD3FoxP3,
#                                            levels = c(1, 2, 3),
#                                            labels = c("low", "mid", "high"))
# 
# ### Cluster for tumor intratumoral FoxP3 because it can be expressed by tumor cell
# clust <- Mclust(clust_markers$percent_FoxP3_tumor.i)
# summary(clust)
# clust_markers$clusters_FoxP3_ <- clust$classification
# clust_markers$clusters_FoxP3_ <- factor(clust_markers$clusters_FoxP3_,
#                                            levels = c(1, 2, 3, 4),
#                                            labels = c("low", "mid", "mid-high", "high"))
# 
# ### Cluster for tumor intratumoral CD11b/CD15
# clust <- Mclust(clust_markers$percent_CD11b_CD15_tumor.i)
# summary(clust)
# clust_markers$clusters_CD11bCD15 <- clust$classification
# clust_markers$clusters_CD11bCD15 <- factor(clust_markers$clusters_CD11bCD15,
#                                            levels = c(1, 7, 8),
#                                            labels = c("low", "high", "mid"))
# clust_markers <- clust_markers %>% mutate(clusters_CD11bCD15 = factor(clusters_CD11bCD15, levels = c("low", "mid", "high")))
# 
# markers_ROI <- full_join(markers_ROI, clust_markers %>% select(suid, dbl_pos, clusters_CD3CD8, clusters_CD3FoxP3, clusters_FoxP3_, clusters_CD11bCD15), by = "suid")

```

<!-- # Table 3b. Adjusted hazard ratios and 95% confidence intervals (**include each 3 values and use the cluster option**) -->

```{r create group per sampleon ROI_global}
ROI_global <- ROI_global %>% 
  
  mutate(CD3_tumor = case_when(
    
    tumor_percent_cd3_opal_650_positive_cells <= 1      ~ "low",
    tumor_percent_cd3_opal_650_positive_cells > 1       ~ "high"
  ), CD3_tumor = factor(CD3_tumor, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_tumor = case_when(
    tumor_percent_cd3plus_cd8plus_positive_cells <= 1      ~ "low",
    tumor_percent_cd3plus_cd8plus_positive_cells > 1       ~ "high"
  ), CD3_CD8_tumor = factor(CD3_CD8_tumor, levels = c("low","high"))) %>% 
  mutate(CD3_FoxP3_tumor = case_when(
    tumor_percent_cd3plus_foxp3plus_positive_cells <= 1      ~ "low",
    tumor_percent_cd3plus_foxp3plus_positive_cells > 1       ~ "high"
  ), CD3_FoxP3_tumor = factor(CD3_FoxP3_tumor, levels = c("low","high"))) %>% 
  mutate(CD11b_tumor = case_when(
    tumor_percent_cd11b_opal_620_positive_cells == 0      ~ "Absence",
    tumor_percent_cd11b_opal_620_positive_cells > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_CD15_tumor = case_when(
    tumor_percent_cd15_opal_520_positive_cells == 0      ~ "Absence",
    tumor_percent_cd15_opal_520_positive_cells > 0       ~ "Presence"
  )) %>% 
  
  mutate(CD3_stroma = case_when(
    stroma_percent_cd3_opal_650_positive_cells <= 1      ~ "low",
    stroma_percent_cd3_opal_650_positive_cells > 1       ~ "high"
  ), CD3_stroma = factor(CD3_stroma, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_stroma = case_when(
    stroma_percent_cd3plus_cd8plus_positive_cells <= 1      ~ "low",
    stroma_percent_cd3plus_cd8plus_positive_cells > 1       ~ "high"
  ), CD3_CD8_stroma = factor(CD3_CD8_stroma, levels = c("low","high"))) %>% 
  mutate(CD3_FoxP3_stroma = case_when(
    stroma_percent_cd3plus_foxp3plus_positive_cells <= 1      ~ "low",
    stroma_percent_cd3plus_foxp3plus_positive_cells > 1       ~ "high"
  ), CD3_FoxP3_stroma = factor(CD3_FoxP3_stroma, levels = c("low","high"))) %>% 
  mutate(CD11b_stroma = case_when(
    stroma_percent_cd11b_opal_620_positive_cells == 0      ~ "Absence",
    stroma_percent_cd11b_opal_620_positive_cells > 0       ~ "Presence"
  )) %>%
  mutate(CD11b_CD15_stroma = case_when(
    stroma_percent_cd11bplus_cd15plus_positive_cells == 0      ~ "Absence",
    stroma_percent_cd11bplus_cd15plus_positive_cells > 0       ~ "Presence"
  )) %>% 
  
  mutate(CD3_total = case_when(
    percent_cd3_opal_650_positive_cells <= 1      ~ "low",
    percent_cd3_opal_650_positive_cells > 1       ~ "high"
  ), CD3_total = factor(CD3_total, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_total = case_when(
    percent_cd3plus_cd8plus_positive_cells <= 1      ~ "low",
    percent_cd3plus_cd8plus_positive_cells > 1       ~ "high"
  ), CD3_CD8_total = factor(CD3_CD8_total, levels = c("low","high"))) %>% 
  mutate(CD3_FoxP3_total = case_when(
    percent_cd3plus_foxp3plus_positive_cells <= 1      ~ "low",
    percent_cd3plus_foxp3plus_positive_cells > 1       ~ "high"
  ), CD3_FoxP3_total = factor(CD3_FoxP3_total, levels = c("low","high"))) %>% 
  mutate(CD11b_total = case_when(
    percent_cd11b_opal_620_positive_cells == 0      ~ "Absence",
    percent_cd11b_opal_620_positive_cells > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_CD15_total = case_when(
    percent_cd11bplus_cd15plus_positive_cells == 0      ~ "Absence",
    percent_cd11bplus_cd15plus_positive_cells > 0       ~ "Presence"
  )) 

```

# Intratumoral (pink = White, need to add leg)
```{r}
df1 <- as.data.frame(markers_ROI[,c("percent_CD3_stroma.i", "percent_CD3_tumor.i", 
                                    "percent_CD3_CD8_stroma.i", "percent_CD3_CD8_tumor.i", 
                                    "percent_CD3_FoxP3_stroma.i", "percent_CD3_FoxP3_tumor.i", 
                                    "percent_CD11b_stroma.i", "percent_CD11b_tumor.i", 
                                    "percent_CD11b_CD15_stroma.i", "percent_CD11b_CD15_tumor.i",
                                    "suid", "race")]) %>% 
  arrange(race, percent_CD3_stroma.i, percent_CD3_CD8_stroma.i) %>% 
  # drop_na(percent_CD3_tumor.i) %>% 
  unite(suid, c(suid, race), sep = "_", remove = TRUE) %>% 
  `row.names<-`(.$suid) %>% 
  select(-suid) 
# df1 <- as.matrix(df1)
# df2 <- t(df1)

# Create matrix and drop NA
df2 <- t(scale(t(as.matrix(df1)))) # scale for standardizing the data to make variables comparable
df2 <- df2[complete.cases(df2 * 0), , drop=FALSE]

# Create colors for cluster
condition_colors <- unlist(lapply(rownames(df2), function(x){
  if(grepl("White", x)) "pink"
  else if(grepl("Black", x)) "grey"
}))
# Transpose
df2 <- t(df2)
```

## dist euclidian
Reorder row and col based on row means
```{r plot}
library(gplots)

heatmap.2(df2, #main = "kjh",

          trace = "none", density="none", col=bluered(20), cexRow=1,
          lwid=c(1.2, 10), # decrease width of left dendro
          # lhei=c(1.1, 10), 
          margins = c(1,13), # bottom, right
          ColSideColors = condition_colors,
          scale = "none",
          key.par=list(mgp=c(1.5, 0.5, 0), # pos for value, number, axes
                       mar=c(3.5, 1, 2.5, 1) # color key pos down, left, top, right
                       )
          )
legend(0.83, 0.95, # right, up
       legend = c("White", "Black"), fill = c("pink", "grey"), cex = 0.7,
       bty = "n")
```

No reordering by row
```{r}
heatmap.2(df2, #main = "kjh",

          trace = "none", density="none", col=bluered(20), cexRow=1,
                    lwid=c(1.2, 10), 
          margins = c(1,13), # bottom, right
          ColSideColors = condition_colors,
          scale = "none",
          Rowv = FALSE,
          key.par=list(mgp=c(1.5, 0.5, 0), # pos for value, number, axes
                       mar=c(3.5, 1, 2.5, 1) # color key pos down, left, top, right
                       )
          )
legend(0.83, 0.95, # right, up
       legend = c("White", "Black"), fill = c("pink", "grey"), cex = 0.7,
       bty = "n")
```

No reordering at all
```{r}
heatmap.2(df2, #main = "kjh",

          trace = "none", density="none", col=bluered(20), cexRow=1,
                    lwid=c(1.2, 10), 
          margins = c(1,13), # bottom, right
          ColSideColors = condition_colors,
          scale = "none",
          Colv = FALSE, Rowv = FALSE,
          key.par=list(mgp=c(1.5, 0.5, 0), # pos for value, number, axes
                       mar=c(3.5, 1, 2.5, 1) # color key pos down, left, top, right
                       )
          )
legend(0.83, 0.95, # right, up
       legend = c("White", "Black"), fill = c("pink", "grey"), cex = 0.7,
       bty = "n")

```

## dist euclidian with Ward's linkage

```{r}
heatmap.2(df2, #main = "kjh",

          trace = "none", density="none", col=bluered(20), cexRow=1,
                    lwid=c(1.2, 10), 
          margins = c(1,13), # bottom, right
          ColSideColors = condition_colors,
          scale = "none",
          hclustfun = function(x) hclust(x, method="ward.D2"),
          key.par=list(mgp=c(1.5, 0.5, 0), # pos for value, number, axes
                       mar=c(3.5, 1, 2.5, 1) # color key pos down, left, top, right
                       )
          )
legend(0.83, 0.95, # right, up
       legend = c("White", "Black"), fill = c("pink", "grey"), cex = 0.7,
       bty = "n")

```

## dist euclidian with centroid linkage

```{r}
heatmap.2(df2, #main = "kjh",

          trace = "none", density="none", col=bluered(20), cexRow=1,
                    lwid=c(1.2, 10), 
          margins = c(1,13), # bottom, right
          ColSideColors = condition_colors,
          scale = "none",
          hclustfun = function(x) hclust(x,method = 'centroid'),
          key.par=list(mgp=c(1.5, 0.5, 0), # pos for value, number, axes
                       mar=c(3.5, 1, 2.5, 1) # color key pos down, left, top, right
                       )
          )
legend(0.83, 0.95, # right, up
       legend = c("White", "Black"), fill = c("pink", "grey"), cex = 0.7,
       bty = "n")

```

## 1 minus Pearson correlation distance with average linkage

```{r}
heatmap.2(df2, #main = "kjh",

          trace = "none", density="none", col=bluered(20), cexRow=1,
                    lwid=c(1.2, 10), 
          margins = c(1,13), # bottom, right
          ColSideColors = condition_colors,
          scale = "none",
          distfun = function(x) as.dist(1-cor(t(x))), # 1 minus Pearson correlation distance with average linkage
          hclustfun = function(x) hclust(x, method="average"),
          key.par=list(mgp=c(1.5, 0.5, 0), # pos for value, number, axes
                       mar=c(3.5, 1, 2.5, 1) # color key pos down, left, top, right
                       )
          )
legend(0.83, 0.95, # right, up
       legend = c("White", "Black"), fill = c("pink", "grey"), cex = 0.7,
       bty = "n")

```

# visualize the differences in the clusters
heatmaps with the legend as the five immune signatures that you found using mclust - and then sort the heatmap according to the signatures

## dist euclidian
Not reorder row and col
```{r }
df1 <- as.data.frame(markers_ROI[,c("percent_CD3_stroma.i", "percent_CD3_tumor.i", 
                                    "percent_CD3_CD8_stroma.i", "percent_CD3_CD8_tumor.i", 
                                    "percent_CD3_FoxP3_stroma.i", "percent_CD3_FoxP3_tumor.i", 
                                    "percent_CD11b_stroma.i", "percent_CD11b_tumor.i", 
                                    "percent_CD11b_CD15_stroma.i", "percent_CD11b_CD15_tumor.i",
                                    "suid", "clusters_all_IandP")]) %>% 
  arrange(clusters_all_IandP, percent_CD3_stroma.i, percent_CD3_CD8_stroma.i) %>% 
  # drop_na(percent_CD3_tumor.i) %>% 
  unite(suid, c(suid, clusters_all_IandP), sep = "_", remove = TRUE) %>% 
  `row.names<-`(.$suid) %>% 
  select(-suid) 

# Create matrix and drop NA
df2 <- t(scale(t(as.matrix(df1)))) # scale for standardizing the data to make variables comparable
# df2 <- t((t(as.matrix(df1))))
df2 <- df2[complete.cases(df2 * 0), , drop=FALSE]

# Create colors for cluster
condition_colors <- unlist(lapply(rownames(df2), function(x){
  if(grepl("White", x)) "pink"
  else if(grepl("Black", x)) "blue"
}))

condition_colors1 <- unlist(lapply(rownames(df2), function(x){
  case_when(
    # str_detect(x, "mid-low") ~ "red",
    # str_detect(x, "mid-high") ~ "grey",
    str_detect(x, "low") ~ "steelblue1",
    str_detect(x, "mid") ~ "black",
    str_detect(x, "high") ~ "tan1",
    TRUE          ~ NA_character_)
}))

# Transpose
df2 <- t(df2)

heatmap.2(df2, #main = "kjh",

          trace = "none", density="none", col=bluered(20), cexRow=1,
          lwid=c(1.2, 10), # decrease width of left dendro
          # lhei=c(1.1, 10),
          margins = c(1,13), # bottom, right
          ColSideColors = condition_colors1,
          scale = "none",
          Colv = FALSE, Rowv = FALSE,
          dendrogram = "none",
          key.par=list(mgp=c(1.5, 0.5, 0), # pos for value, number, axes
                       mar=c(3.5, 1, 2.5, 1) # color key pos down, left, top, right
                       )
          )
legend("topright", # right, up
       legend = c("low", "mid", "high"), fill = c("steelblue1", "black", "tan1"), cex = 0.7,
       bty = "n")
```








# Peripheral (pink = White, need to add leg)
```{r periph}
df3 <- as.data.frame(markers_ROI[,c("percent_CD3_tumor.p", "percent_CD3_CD8_tumor.p", "percent_CD3_FoxP3_tumor.p", "percent_CD11b_tumor.p", "percent_CD11b_CD15_tumor.p",
                                    "percent_CD3_stroma.p", "percent_CD3_CD8_stroma.p", "percent_CD3_FoxP3_stroma.p", "percent_CD11b_stroma.p", "percent_CD11b_CD15_stroma.p",
                                    "suid", "race")]) %>% 
  arrange(race) %>% 
  # drop_na(percent_CD3_tumor.i) %>% 
  unite(suid, c(suid, race), sep = "_", remove = TRUE) %>% 
  `row.names<-`(.$suid) %>% 
  select(-suid) 
# df1 <- as.matrix(df1)
# df2 <- t(df1)

# Create matrix and drop NA
df4 <- t(scale(t(as.matrix(df3)))) # scale for standardizing the data to make variables comparable
df4 <- df4[complete.cases(df4 * 0), , drop=FALSE]

# Create colors for cluster
condition_colors <- unlist(lapply(rownames(df4), function(x){
  if(grepl("White", x)) "pink"
  else if(grepl("Black", x)) "grey"
}))
# Transpose
df4 <- t(df4)
```

## dist euclidian
```{r}
heatmap.2(df4, #main = "kjh",

          trace = "none", density="none", col=bluered(20), cexRow=1,
          lwid=c(1.2, 10), 
          # lhei=c(1.1, 10), 
          margins = c(1,13), # bottom, right
          ColSideColors = condition_colors,
          scale = "none",
          key.par=list(mgp=c(1.5, 0.5, 0), # pos for value, number, axes
                       mar=c(3.5, 1, 2.5, 1) # color key pos down, left, top, right
                       )
          )
legend(0.83, 0.95, # right, up
       legend = c("White", "Black"), fill = c("pink", "grey"), cex = 0.7,
       bty = "n")

heatmap.2(df4, #main = "kjh",

          trace = "none", density="none", col=bluered(20), cexRow=1,
                    lwid=c(1.2, 10), 
          margins = c(1,13), # bottom, right
          ColSideColors = condition_colors,
          scale = "none",
          Rowv = FALSE,
          key.par=list(mgp=c(1.5, 0.5, 0), # pos for value, number, axes
                       mar=c(3.5, 1, 2.5, 1) # color key pos down, left, top, right
                       )
          )
legend(0.83, 0.95, # right, up
       legend = c("White", "Black"), fill = c("pink", "grey"), cex = 0.7,
       bty = "n")

heatmap.2(df4, #main = "kjh",

          trace = "none", density="none", col=bluered(20), cexRow=1,
                    lwid=c(1.2, 10), 
          margins = c(1,13), # bottom, right
          ColSideColors = condition_colors,
          scale = "none",
          Colv = FALSE,
          key.par=list(mgp=c(1.5, 0.5, 0), # pos for value, number, axes
                       mar=c(3.5, 1, 2.5, 1) # color key pos down, left, top, right
                       )
          )
legend(0.83, 0.95, # right, up
       legend = c("White", "Black"), fill = c("pink", "grey"), cex = 0.7,
       bty = "n")

```

## dist euclidian with Ward's linkage

```{r}
heatmap.2(df4, #main = "kjh",

          trace = "none", density="none", col=bluered(20), cexRow=1,
                    lwid=c(1.2, 10), 
          margins = c(1,13), # bottom, right
          ColSideColors = condition_colors,
          scale = "none",
          hclustfun = function(x) hclust(x, method="ward.D2"),
          key.par=list(mgp=c(1.5, 0.5, 0), # pos for value, number, axes
                       mar=c(3.5, 1, 2.5, 1) # color key pos down, left, top, right
                       )
          )
legend(0.83, 0.95, # right, up
       legend = c("White", "Black"), fill = c("pink", "grey"), cex = 0.7,
       bty = "n")

```

## dist euclidian with centroid linkage

```{r}
heatmap.2(df4, #main = "kjh",

          trace = "none", density="none", col=bluered(20), cexRow=1,
                    lwid=c(1.2, 10), 
          margins = c(1,13), # bottom, right
          ColSideColors = condition_colors,
          scale = "none",
          hclustfun = function(x) hclust(x,method = 'centroid'),
          key.par=list(mgp=c(1.5, 0.5, 0), # pos for value, number, axes
                       mar=c(3.5, 1, 2.5, 1) # color key pos down, left, top, right
                       )
          )
legend(0.83, 0.95, # right, up
       legend = c("White", "Black"), fill = c("pink", "grey"), cex = 0.7,
       bty = "n")

```

## 1 minus Pearson correlation distance with average linkage

```{r}
heatmap.2(df4, #main = "kjh",

          trace = "none", density="none", col=bluered(20), cexRow=1,
                    lwid=c(1.2, 10), 
          margins = c(1,13), # bottom, right
          ColSideColors = condition_colors,
          scale = "none",
          distfun = function(x) as.dist(1-cor(t(x))), # 1 minus Pearson correlation distance with average linkage
          hclustfun = function(x) hclust(x, method="average"),
          key.par=list(mgp=c(1.5, 0.5, 0), # pos for value, number, axes
                       mar=c(3.5, 1, 2.5, 1) # color key pos down, left, top, right
                       )
          )
legend(0.83, 0.95, # right, up
       legend = c("White", "Black"), fill = c("pink", "grey"), cex = 0.7,
       bty = "n")

```

```{r}
# data(mtcars)
#  x  <- as.matrix(mtcars)
# hv <- heatmap.2(x, col=bluered, scale="column", tracecol="#303030")
# 
#  ###
#  ## Look at the return values
#  ###
#  names(hv)
# 
#  ## Show the mapping of z-score values to color bins
#  hv$colorTable
# 
#  ## Extract the range associated with white
#  hv$colorTable[hv$colorTable[,"color"]=="#FFFFFF",]
# 
#  ## Determine the original data values that map to white
#  whiteBin <- unlist(hv$colorTable[hv$colorTable[,"color"]=="#FFFFFF",1:2])
#  rbind(whiteBin[1] * hv$colSDs + hv$colMeans,
#        whiteBin[2] * hv$colSDs + hv$colMeans )
#  ##
#  ## A more decorative heatmap, with z-score scaling along columns
#  ##
#  hv <- heatmap.2(x, col=cm.colors(255), scale="column",
# 	       RowSideColors=rc, ColSideColors=cc, margin=c(5, 10),
# 	       xlab="specification variables", ylab= "Car Models",
# 	       main="heatmap(<Mtcars data>, ..., scale=\"column\")",
#          tracecol="green", density="density")
#  ## Note that the breakpoints are now symmetric about 0
# 
#  ## Color the labels to match RowSideColors and ColSideColors
#  hv <- heatmap.2(x, col=cm.colors(255), scale="column",
#          RowSideColors=rc, ColSideColors=cc, margin=c(5, 10),
# 	       xlab="specification variables", ylab= "Car Models",
# 	       main="heatmap(<Mtcars data>, ..., scale=\"column\")",
#          tracecol="green", density="density", colRow=rc, colCol=cc,
#          srtCol=45, adjCol=c(0.5,1))
```


# visualize the differences in the clusters
could you create the heatmaps just as you did before but put the legend as the five immune signatures that you found using mclust - and then sort the heatmap according to the signatures



