---
title: "Immune marker data"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: cerulean #darkly
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
h1.title {
  font-size: 25px;
}
.figure {
   margin-top: 25px;
   <!-- margin-bottom: 100px; -->
}

table {
    margin-top: 25px;
    <!-- margin-bottom: 100px !important; -->
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      # fig.width = 7, fig.height = 5, 
                      fig.align='center'#, fig.show='hold'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

<style>
div.blue { background-color:#0099CC; border-radius: 5px; padding: 20px; font-size: 38px}
</style>
<div class = "blue">

<span style="color: white;">Immune Marker Data</span>

</div>
<br>

```{r library, include=FALSE}
# library(drake)
library(tidyverse)
library(data.table)
# library(VennDiagram)
library(gtsummary)
library(survival)
library(survminer)
library(psych)
# library(corrplot)
# library(ggcorrplot)
library(mclust)
```

```{r load}
# loadd(clinical_data, ROI_tumor ,ROI_stroma ,ROI_total,
#       cases_match)

ROI_global <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_AACES_NCOCS/ROI_global.rds")
clinical_data <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_AACES_NCOCS/clinical_data.rds")

# Rewove patients not matched or lost match
ROI_global <- left_join(ROI_global, clinical_data, by="suid") %>% drop_na(pair_id) %>% 
  group_by(pair_id) %>% 
  mutate(have_a_match = dense_rank(interaction(suid, pair_id))) %>% 
  group_by(pair_id) %>% 
  mutate(is_paired = max(have_a_match)) %>% 
  filter(is_paired == 2) %>% 
  select(pair_id, everything(), -c(is_paired, have_a_match)) %>% 
  ungroup()

# markers_match <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_AACES_NCOCS/markers_match.rds")
path <- fs::path("","Volumes","Peres_Research","Christelle Colin-Leitzinger", "IF_AACES_NCOCS", "Figures")



```
<br>
<br>

***

# I. ROIs Raw Data
## 1. Cells Distribution
```{r}
p1 <- ROI_global %>% 
  filter(intratumoral_i_vs_peripheral_p_ == "Intratumoral") %>% 
  mutate(Tumor = "Tumor") %>% 
  mutate(Stroma = "Stroma") %>% 
  ggplot()+
  geom_violin(aes(x=Tumor, y=percent_tumor), scale = "count")+
  geom_boxplot(aes(x=Tumor, y=percent_tumor), width=.1) +
  geom_violin(aes(x=Stroma, y=percent_stroma), scale = "count") +
  geom_boxplot(aes(x=Stroma, y=percent_stroma), width=.1) +
  labs(x="Cell type", y=NULL, title="Intratumoral \nROIs")
p2 <- ROI_global %>% 
  filter(intratumoral_i_vs_peripheral_p_ == "Peripheral") %>% 
  mutate(Tumor = "Tumor") %>% 
  mutate(Stroma = "Stroma") %>% 
  ggplot()+
  geom_violin(aes(x=Tumor, y=percent_tumor), scale = "count")+
  geom_boxplot(aes(x=Tumor, y=percent_tumor), width=.1) +
  geom_violin(aes(x=Stroma, y=percent_stroma), scale = "count") +
  geom_boxplot(aes(x=Stroma, y=percent_stroma), width=.1) +
  labs(x="Cell type", y=NULL, title="Peripheral \nROIs")

# tiff(paste0(path, "/violin plot distribution tumor and stroma cells in ROIs intra-periph.tiff"))
gridExtra::grid.arrange(p1, p2, ncol = 2, 
                        top = "% of Cells Present in", left = "% Cells per samples", 
                        bottom = "Data on Race-Matched Patients")
# dev.off()
```

## 2. ICC
```{r}
ICC_roi_periph <- ROI_global %>%
  filter(intratumoral_i_vs_peripheral_p_ == "Peripheral") %>% 
  select(suid, image_tag, #tumor_total_cells, stroma_total_cells, 
         contains("percent"))
class(ICC_roi_periph) <- "data.frame"
ICC_data <- data.frame(matrix(nrow=1, ncol=0))

for(i in 1:length(colnames(ICC_roi_periph))) {
  
  rad <- ICC_roi_periph %>% select(suid)
  
  if(class(ICC_roi_periph[,i]) == "numeric" | class(ICC_roi_periph[,i]) == "integer") {
    
    ICC_df <- cbind(rad, value = ICC_roi_periph[,i])
    ICC_df <- ICC_df %>%
      mutate(Slide = "Slide0") %>%
      group_by(suid) %>%
      mutate(n = row_number(suid)) %>%
      ungroup() %>%
      unite(slide_id, Slide:n, sep = "", remove = TRUE, na.rm = TRUE) %>%
      pivot_wider(names_from = slide_id, values_from = value) %>%
      select(c(starts_with("slide")))
    
    ICC <- ICC(ICC_df)$results[4,2]
    ICC_data <- cbind(ICC_data,ICC)
    
  }
  
}
colnames(ICC_data) <- colnames(ICC_roi_periph)[3:ncol(ICC_roi_periph)]

rm(ICC_df, ICC, i,  rad)
```

## New ICC function
```{r}
new_icc <- function(ROI_global) {
  icc_overall <- ROI_global %>%
    select(suid, image_tag,
           contains("percent"))
  class(icc_overall) <- "data.frame"
  
  icc_intrat <- ROI_global %>%
    filter(intratumoral_i_vs_peripheral_p_ == "Peripheral") %>%
    select(suid, image_tag,
           contains("percent"))
  class(icc_intrat) <- "data.frame"
  
  icc_periph <- ROI_global %>%
    filter(intratumoral_i_vs_peripheral_p_ == "Peripheral") %>%
    select(suid, image_tag,
           contains("percent"))
  class(icc_periph) <- "data.frame"
  
  fct_icc <- function(data) {
    ICC_data <- data.frame(matrix(nrow = 1, ncol = 0))
    lb_data <- data.frame(matrix(nrow = 1, ncol = 0))
    up_data <- data.frame(matrix(nrow = 1, ncol = 0))
    for (i in 1:length(colnames(data))) {
      rad <- data %>% select(suid)
      
      if (class(data[, i]) == "numeric" |
          class(data[, i]) == "integer") {
        ICC_df <- cbind(rad, value = data[, i])
        ICC_df <- ICC_df %>%
          mutate(Slide = "Slide0") %>%
          group_by(suid) %>%
          mutate(n = row_number(suid)) %>%
          ungroup() %>%
          unite(slide_id, Slide:n, sep = "", remove = TRUE, na.rm = TRUE) %>%
          pivot_wider(names_from = slide_id, values_from = value) %>%
          select(c(starts_with("slide")))
        
        ICC <- ICC(ICC_df)$results[4, 2]
        ICC_data <- cbind(ICC_data, ICC)
        ICC <- ICC(ICC_df)$results[4, 7]
        lb_data <- cbind(lb_data, ICC)
        ICC <- ICC(ICC_df)$results[4, 8]
        up_data <- cbind(up_data, ICC)
        
      }
      
    }
    ICCC_data <- bind_rows(ICC_data, lb_data, up_data)
    colnames(ICCC_data) <- colnames(data)[3:ncol(data)]
    ICCC_data <- as.data.frame(t(ICCC_data)) %>%
      mutate(ICC_lb_up = paste(round(V1, 2), " (", round(V2, 2), ", ", round(V3, 2), ")", sep = "")) %>%
      select(ICC_lb_up)
  }
  
  icc_overall <-
    fct_icc(icc_overall) %>% rename(Overall = "ICC_lb_up")
  icc_intrat <-
    fct_icc(icc_intrat) %>% rename(Intratumoral = "ICC_lb_up")
  icc_periph <-
    fct_icc(icc_periph) %>% rename(Peripheral = "ICC_lb_up")
  
  icc_data <- cbind(icc_overall, icc_intrat, icc_periph)
  
}

b <- new_icc(ROI_global)
b
```
<br>
<br>

***

# II. Abundance

```{r summarize mean}
markers_ROIi <- ROI_global %>% 
  filter(intratumoral_i_vs_peripheral_p_ == "Intratumoral") %>% 
  group_by(suid) %>% 
  summarize(
    mean_tumor = mean(percent_tumor),
    mean_stroma = mean(percent_stroma),
    mean_total = mean(percent_total),
    # variance_tumor = var(percent_tumor),
    # variance_stroma = var(percent_stroma),
    percent_CD3_tumor = mean(tumor_percent_cd3_opal_650_positive_cells),
    percent_CD8_tumor = mean(tumor_percent_cd8_opal_570_positive_cells),
    percent_CD3_CD8_tumor = mean(tumor_percent_cd3plus_cd8plus_positive_cells),
    percent_FoxP3_tumor = mean(tumor_percent_foxp3_opal_540_positive_cells),
    percent_CD3_FoxP3_tumor = mean(tumor_percent_cd3plus_foxp3plus_positive_cells),
    percent_CD11b_tumor = mean(tumor_percent_cd11b_opal_620_positive_cells),
    percent_CD15_tumor = mean(tumor_percent_cd15_opal_520_positive_cells),
    percent_CD11b_CD15_tumor = mean(tumor_percent_cd11bplus_cd15plus_positive_cells),
    percent_CD3_stroma = mean(stroma_percent_cd3_opal_650_positive_cells),
    percent_CD8_stroma = mean(stroma_percent_cd8_opal_570_positive_cells),
    percent_CD3_CD8_stroma = mean(stroma_percent_cd3plus_cd8plus_positive_cells),
    percent_FoxP3_stroma = mean(stroma_percent_foxp3_opal_540_positive_cells),
    percent_CD3_FoxP3_stroma = mean(stroma_percent_cd3plus_foxp3plus_positive_cells),
    percent_CD11b_stroma = mean(stroma_percent_cd11b_opal_620_positive_cells),
    percent_CD15_stroma = mean(stroma_percent_cd15_opal_520_positive_cells),
    percent_CD11b_CD15_stroma = mean(stroma_percent_cd11bplus_cd15plus_positive_cells),
    
    percent_CD3_total = mean(percent_cd3_opal_650_positive_cells),
    percent_CD8_total = mean(percent_cd8_opal_570_positive_cells),
    percent_CD3_CD8_total = mean(percent_cd3plus_cd8plus_positive_cells),
    percent_FoxP3_total = mean(percent_foxp3_opal_540_positive_cells),
    percent_CD3_FoxP3_total = mean(percent_cd3plus_foxp3plus_positive_cells),
    percent_CD11b_total = mean(percent_cd11b_opal_620_positive_cells),
    percent_CD15_total = mean(percent_cd15_opal_520_positive_cells),
    percent_CD11b_CD15_total = mean(percent_cd11bplus_cd15plus_positive_cells)
  )
markers_ROIi$tumor_variation <- markers_ROIi$mean_tumor - mean(ROI_global$percent_tumor)
markers_ROIi$stroma_variation <- markers_ROIi$mean_stroma - mean(ROI_global$percent_stroma)
markers_ROIi$total_variation <- markers_ROIi$mean_stroma - mean(ROI_global$percent_stroma)
#
markers_ROIp <- ROI_global %>% 
  filter(intratumoral_i_vs_peripheral_p_ == "Peripheral") %>% 
  group_by(suid) %>% 
  summarize(
    mean_tumor = mean(percent_tumor),
    mean_stroma = mean(percent_stroma),
    mean_total = mean(percent_total),
    # variance_tumor = var(percent_tumor),
    # variance_stroma = var(percent_stroma),
    percent_CD3_tumor = mean(tumor_percent_cd3_opal_650_positive_cells),
    percent_CD8_tumor = mean(tumor_percent_cd8_opal_570_positive_cells),
    percent_CD3_CD8_tumor = mean(tumor_percent_cd3plus_cd8plus_positive_cells),
    percent_FoxP3_tumor = mean(tumor_percent_foxp3_opal_540_positive_cells),
    percent_CD3_FoxP3_tumor = mean(tumor_percent_cd3plus_foxp3plus_positive_cells),
    percent_CD11b_tumor = mean(tumor_percent_cd11b_opal_620_positive_cells),
    percent_CD15_tumor = mean(tumor_percent_cd15_opal_520_positive_cells),
    percent_CD11b_CD15_tumor = mean(tumor_percent_cd11bplus_cd15plus_positive_cells),
    percent_CD3_stroma = mean(stroma_percent_cd3_opal_650_positive_cells),
    percent_CD8_stroma = mean(stroma_percent_cd8_opal_570_positive_cells),
    percent_CD3_CD8_stroma = mean(stroma_percent_cd3plus_cd8plus_positive_cells),
    percent_FoxP3_stroma = mean(stroma_percent_foxp3_opal_540_positive_cells),
    percent_CD3_FoxP3_stroma = mean(stroma_percent_cd3plus_foxp3plus_positive_cells),
    percent_CD11b_stroma = mean(stroma_percent_cd11b_opal_620_positive_cells),
    percent_CD15_stroma = mean(stroma_percent_cd15_opal_520_positive_cells),
    percent_CD11b_CD15_stroma = mean(stroma_percent_cd11bplus_cd15plus_positive_cells),
    percent_CD3_total = mean(percent_cd3_opal_650_positive_cells),
    percent_CD8_total = mean(percent_cd8_opal_570_positive_cells),
    percent_CD3_CD8_total = mean(percent_cd3plus_cd8plus_positive_cells),
    percent_FoxP3_total = mean(percent_foxp3_opal_540_positive_cells),
    percent_CD3_FoxP3_total = mean(percent_cd3plus_foxp3plus_positive_cells),
    percent_CD11b_total = mean(percent_cd11b_opal_620_positive_cells),
    percent_CD15_total = mean(percent_cd15_opal_520_positive_cells),
    percent_CD11b_CD15_total = mean(percent_cd11bplus_cd15plus_positive_cells)
  )
markers_ROIp$tumor_variation <- markers_ROIp$mean_tumor - mean(ROI_global$percent_tumor)
markers_ROIp$stroma_variation <- markers_ROIp$mean_stroma - mean(ROI_global$percent_stroma)
markers_ROIp$total_variation <- markers_ROIp$mean_total - mean(ROI_global$percent_total)

# Join Intratumoral and Peropheral ROI
markers_ROI <- full_join(markers_ROIi, markers_ROIp,
                         by= "suid", suffix= c(".i", ".p"))
markers_ROI <- left_join(markers_ROI, clinical_data, by="suid")
clust_markers <- markers_ROI
```

## 1.Table tumor cells in ROIs
```{r Table tumor cells in ROIs}
tbl1 <-
  markers_ROI %>% 
  select(percent_CD3_tumor.i, percent_CD3_CD8_tumor.i, percent_CD3_FoxP3_tumor.i, 
              percent_CD11b_tumor.i, percent_CD11b_CD15_tumor.i) %>% 
  tbl_summary(statistic = list(all_continuous() ~ "{mean}")) %>% 
  modify_header(list(stat_0 ~ "**Mean**"))

tbl2 <- markers_ROI %>% 
  select(percent_CD3_tumor.i, percent_CD3_CD8_tumor.i, percent_CD3_FoxP3_tumor.i, 
              percent_CD11b_tumor.i, percent_CD11b_CD15_tumor.i) %>% 
  tbl_summary() %>% 
  modify_header(list(stat_0 ~ "**Median** (range)"))

# data <- data.frame(matrix(nrow=1, ncol=0))
# nme <- ""
# for(i in 1:length(colnames(markers_ROI))) {
# 
#   if(class(markers_ROI[,i]) == "numeric" | class(markers_ROI[,i]) == "integer") {
# 
#     nme <- markers_ROI[,i]
#   # data <- markers_ROI %>% mutate(i = case_when(
#   #               i == 0    ~ i,
#   #               TRUE      ~ "others"
#   #             ))
# 
#   }
#   print(nme)
# }
# 
#  i1 <- which(markers_ROI == 0, arr.ind=TRUE)
#  i2 <-  i1[, 2]
#  i3 <- i2[!duplicated(i2)]
# (markers_ROI)[i1] <- names(markers_ROI)[i1]

tbl3 <-
  markers_ROI %>% 
  mutate(across(.cols = c(percent_CD3_tumor.i, percent_CD3_CD8_tumor.i, percent_CD3_FoxP3_tumor.i,
              percent_CD11b_tumor.i, percent_CD11b_CD15_tumor.i),
                ~case_when(
                . == 0    ~ "Yes",
                TRUE      ~ "No"
              ))) %>%
  select(percent_CD3_tumor.i, percent_CD3_CD8_tumor.i, percent_CD3_FoxP3_tumor.i, 
              percent_CD11b_tumor.i, percent_CD11b_CD15_tumor.i) %>% 
  tbl_summary(statistic = list(all_categorical() ~ "{n} ({p})"),
              missing_text = "others",
              missing = "no") %>% 
  modify_header(list(stat_0 ~ "**n (%) with zero cells**"))
  
tbl <- tbl_merge(list(tbl1, tbl2, tbl3)) %>%
  modify_spanning_header(everything() ~ "Tumor ROIs") %>% as_gt()
tbl
# gt::gtsave(tbl, paste0(path, "/Table tumor cells in ROIs.pdf"))

tbl1 <-
  markers_ROI %>% 
  select(percent_CD3_stroma.i, percent_CD3_CD8_stroma.i, percent_CD3_FoxP3_stroma.i, 
              percent_CD11b_stroma.i, percent_CD11b_CD15_stroma.i) %>% 
  tbl_summary(statistic = list(all_continuous() ~ "{mean}")) %>% 
  modify_header(list(stat_0 ~ "**Mean**"))

tbl2 <- markers_ROI %>% 
  select(percent_CD3_stroma.i, percent_CD3_CD8_stroma.i, percent_CD3_FoxP3_stroma.i, 
              percent_CD11b_stroma.i, percent_CD11b_CD15_stroma.i) %>% 
  tbl_summary() %>% 
  modify_header(list(stat_0 ~ "**Median** (range)"))
tbl3 <-
  markers_ROI %>% 
  mutate(across(.cols = c(percent_CD3_stroma.i, percent_CD3_CD8_stroma.i, percent_CD3_FoxP3_stroma.i,
              percent_CD11b_stroma.i, percent_CD11b_CD15_stroma.i),
                ~case_when(
                . == 0    ~ "Yes",
                TRUE      ~ "No"
              ))) %>%
  select(percent_CD3_stroma.i, percent_CD3_CD8_stroma.i, percent_CD3_FoxP3_stroma.i, 
              percent_CD11b_stroma.i, percent_CD11b_CD15_stroma.i) %>% 
  tbl_summary(statistic = list(all_categorical() ~ "{n} ({p})"),
              missing_text = "others",
              missing = "no") %>% 
  modify_header(list(stat_0 ~ "**n (%) with zero cells**"))
  
tbl <- tbl_merge(list(tbl1, tbl2, tbl3)) %>%
  modify_spanning_header(everything() ~ "Stroma ROIs") %>% as_gt()
tbl
# gt::gtsave(tbl, paste0(path, "/Table stroma cells in ROIs.pdf"))

tbl1 <-
  markers_ROI %>% 
  select(percent_CD3_total.i, percent_CD3_CD8_total.i, percent_CD3_FoxP3_total.i, 
              percent_CD11b_total.i, percent_CD11b_CD15_total.i) %>% 
  tbl_summary(statistic = list(all_continuous() ~ "{mean}")) %>% 
  modify_header(list(stat_0 ~ "**Mean**"))

tbl2 <- markers_ROI %>% 
  select(percent_CD3_total.i, percent_CD3_CD8_total.i, percent_CD3_FoxP3_total.i, 
              percent_CD11b_total.i, percent_CD11b_CD15_total.i) %>% 
  tbl_summary() %>% 
  modify_header(list(stat_0 ~ "**Median** (range)"))
tbl3 <-
  markers_ROI %>% 
  mutate(across(.cols = c(percent_CD3_total.i, percent_CD3_CD8_total.i, percent_CD3_FoxP3_total.i,
              percent_CD11b_total.i, percent_CD11b_CD15_total.i),
                ~case_when(
                . == 0    ~ "Yes",
                TRUE      ~ "No"
              ))) %>%
  select(percent_CD3_total.i, percent_CD3_CD8_total.i, percent_CD3_FoxP3_total.i, 
              percent_CD11b_total.i, percent_CD11b_CD15_total.i) %>% 
  tbl_summary(statistic = list(all_categorical() ~ "{n} ({p})"),
              missing_text = "others",
              missing = "no") %>% 
  modify_header(list(stat_0 ~ "**n (%) with zero cells**"))
  
tbl <- tbl_merge(list(tbl1, tbl2, tbl3)) %>%
  modify_spanning_header(everything() ~ "Overall (tmor+stroma) ROIs") %>% as_gt()
tbl
# gt::gtsave(tbl, paste0(path, "/Table overall cells in ROIs.pdf"))
```
<br>


## 2.What happen if we don't ask mclust for a spacific number of cluster?

### Cluster for stroma/tumor in the intratumoral/peritumoral ROIs (include single and double staining, overall are excluded)
```{r code cluster}
set.seed(1234)
clust_markers <- markers_ROI %>% 
  filter(!is.na(markers_ROI$percent_CD3_CD8_tumor.i) & !is.na(markers_ROI$percent_CD3_CD8_tumor.p))

clust <- Mclust(clust_markers[,c(5:20,35:50)])
# clust <- Mclust(clust_markers[,c(21:28,51:58)])
summary(clust)
clust_markers$clusters_all_IandP <- clust$classification
clust_markers$clusters_all_IandP <- factor(clust_markers$clusters_all_IandP,
                                           levels = c(1, 3, 2),
                                           labels = c("low", "mid", "high"))
# clust_markers$clusters_all_IandP <- factor(clust_markers$clusters_all_IandP, 
#                                            levels = c(6, 5, 1, 4, 3, 2),
#                                            labels = c("sublow", "low", "mid-low", "mid", "mid-high", "high"))

clust_markers %>% 
  tidyr::gather(key = "markers_cat", value = "value", 
         c("percent_CD3_tumor.i":"percent_CD11b_CD15_stroma.i")) %>% 
  select(suid, clusters_all_IandP, markers_cat, value) %>% 
  ggplot(aes(x=suid, y=value, group=markers_cat,  color=markers_cat))+
  geom_boxplot()+
  facet_grid(.~ clusters_all_IandP)

clust_markers %>% 
  tidyr::gather(key = "markers_cat", value = "value", 
         c("percent_CD3_tumor.p":"percent_CD11b_CD15_stroma.p")) %>% 
  select(suid, clusters_all_IandP, markers_cat, value) %>% 
  ggplot(aes(x=suid, y=value, group=markers_cat,  color=markers_cat))+
  geom_boxplot()+
  facet_grid(.~ clusters_all_IandP)


ggsurvplot(
  survfit(Surv(time = clust_markers$timelastfu_new, event = clust_markers$surv_vital) ~ clust_markers$clusters_all_IandP), 
  data = clust_markers,
           title = "Survival analysis on match population ROIs",
           font.main = c(16, "bold", "black"),
           xlab = "Time (days)", 
           # legend.title = "clustered by dbl_pos",
           # legend.labs = c("high", "low", "mid", "mid-high", "mid-low"),
           pval = TRUE, # pval.coord = c(2100,.53),
           conf.int = FALSE,
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table (count(%))",
           risk.table = "abs_pct",
           risk.table.y.text = FALSE,
           risk.table.fontsize = 3,
           tables.theme = theme_survminer(font.main = c(13, "bold", "black"),
                                          font.y = c(0, "bold", "transparent"))
) + guides(colour = guide_legend(ncol = 2))
```
<br>

### Cluster for tumor intratumoral all double positive "percent_CD3_CD8_tumor.i", "percent_CD3_FoxP3_tumor.i", "percent_CD11b_CD15_tumor.i"
```{r}
clust_markers <- markers_ROI %>% filter(!is.na(markers_ROI$percent_CD3_CD8_tumor.i ))

clust <- 
  Mclust(clust_markers[,c("percent_CD3_CD8_tumor.i", "percent_CD3_FoxP3_tumor.i", "percent_CD11b_CD15_tumor.i")])
summary(clust)
clust_markers$dbl_pos <- clust$classification
clust_markers$dbl_pos <- factor(clust_markers$dbl_pos, 
                                levels = c(1, 2, 3),
                                labels = c("low","high","mid"))

clust_markers %>% 
  gather(key = "markers_cat", value = "value", c("percent_CD3_tumor.i":"percent_CD11b_CD15_tumor.i")) %>% 
  select(suid, dbl_pos, markers_cat, value) %>% 
  ggplot(aes(x=suid, group=markers_cat, color=markers_cat))+
  geom_boxplot(aes(y=value))+
  facet_grid(.~ dbl_pos)


ggsurvplot(
  survfit(Surv(time = clust_markers$timelastfu_new, event = clust_markers$surv_vital) ~ clust_markers$dbl_pos), 
  data = clust_markers,
           title = "Survival analysis on match population ROIs",
           font.main = c(16, "bold", "black"),
           xlab = "Time (days)", 
           # legend.title = "clustered by dbl_pos",
           # legend.labs = c("high", "low", "mid", "mid-high", "mid-low"),
           pval = TRUE, # pval.coord = c(2100,.53),
           conf.int = FALSE,
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table (count(%))",
           risk.table = "abs_pct",
           risk.table.y.text = FALSE,
           risk.table.fontsize = 3,
           tables.theme = theme_survminer(font.main = c(13, "bold", "black"),
                                          font.y = c(0, "bold", "transparent"))
)
```
<br>

### Cluster for tumor intratumoral CD3-CD8
```{r}
clust <- Mclust(clust_markers$percent_CD3_CD8_tumor.i)
summary(clust)
clust_markers$clusters_CD3CD8 <- clust$classification
# clust_markers$clusters_CD3CD8 <- factor(clust_markers$clusters_CD3CD8, 
#                                         levels = c(1 , 2, 3, 4, 5),
#                                         labels = c("low", "mid-low", "mid", "mid-high", "high"))

clust_markers %>% 
  gather(key = "markers_cat", value = "value", c("percent_CD3_tumor.i":"percent_CD11b_CD15_tumor.i")) %>% 
  select(suid, clusters_CD3CD8, markers_cat, value) %>% 
  ggplot(aes(x=suid, y=value, group=markers_cat, color=markers_cat))+
  geom_boxplot()+
  facet_grid(.~ clusters_CD3CD8)

ggsurvplot(
  survfit(Surv(time = clust_markers$timelastfu_new, event = clust_markers$surv_vital) ~ clust_markers$clusters_CD3CD8), 
  data = clust_markers,
           title = "Survival analysis on match population ROIs",
           font.main = c(16, "bold", "black"),
           xlab = "Time (days)", 
           # legend.title = "clustered by dbl_pos",
           # legend.labs = c("high", "low", "mid", "mid-high", "mid-low"),
           pval = TRUE, # pval.coord = c(2100,.53),
           conf.int = FALSE,
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table (count(%))",
           risk.table = "abs_pct",
           risk.table.y.text = FALSE,
           risk.table.fontsize = 3,
           tables.theme = theme_survminer(font.main = c(13, "bold", "black"),
                                          font.y = c(0, "bold", "transparent"))
) + guides(colour = guide_legend(ncol = 2))
```
<br>

### Cluster for tumor intratumoral CD3-FoxP3
```{r}
clust <- Mclust(clust_markers$percent_CD3_FoxP3_tumor.i)
summary(clust)
clust_markers$clusters_FoxP3 <- clust$classification
# clust_markers$clusters_FoxP3 <- factor(clust_markers$clusters_FoxP3, 
#                            levels = c(1, 2),
#                            labels = c("hot", "immunosuppressed"))

clust_markers %>% 
  gather(key = "markers_cat", value = "value", c("percent_CD3_tumor.i":"percent_CD11b_CD15_tumor.i")) %>% 
  select(suid, clusters_FoxP3, markers_cat, value) %>% 
  ggplot(aes(x=suid, y=value, group=markers_cat, color=markers_cat))+
  geom_boxplot()+
  facet_grid(.~ clusters_FoxP3)

ggsurvplot(
  survfit(Surv(time = clust_markers$timelastfu_new, event = clust_markers$surv_vital) ~ clust_markers$clusters_FoxP3), 
  data = clust_markers,
           title = "Survival analysis on match population ROIs",
           font.main = c(16, "bold", "black"),
           xlab = "Time (days)", 
           # legend.title = "clustered by dbl_pos",
           # legend.labs = c("high", "low", "mid", "mid-high", "mid-low"),
           pval = TRUE, # pval.coord = c(2100,.53),
           conf.int = FALSE,
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table (count(%))",
           risk.table = "abs_pct",
           risk.table.y.text = FALSE,
           risk.table.fontsize = 3,
           tables.theme = theme_survminer(font.main = c(13, "bold", "black"),
                                          font.y = c(0, "bold", "transparent"))
)
```
<br>

### Cluster for tumor intratumoral CD3-FoxP3
```{r}
clust <- Mclust(clust_markers$percent_CD3_FoxP3_tumor.i)
summary(clust)
clust_markers$clusters_FoxP3 <- clust$classification
# clust_markers$clusters_FoxP3 <- factor(clust_markers$clusters_FoxP3, 
#                            levels = c(1, 2),
#                            labels = c("hot", "immunosuppressed"))

clust_markers %>% 
  gather(key = "markers_cat", value = "value", c("percent_CD3_tumor.i":"percent_CD11b_CD15_tumor.i")) %>% 
  select(suid, clusters_FoxP3, markers_cat, value) %>% 
  ggplot(aes(x=suid, y=value, group=markers_cat, color=markers_cat))+
  geom_boxplot()+
  facet_grid(.~ clusters_FoxP3)

ggsurvplot(
  survfit(Surv(time = clust_markers$timelastfu_new, event = clust_markers$surv_vital) ~ clust_markers$clusters_FoxP3), 
  data = clust_markers,
           title = "Survival analysis on match population ROIs",
           font.main = c(16, "bold", "black"),
           xlab = "Time (days)", 
           # legend.title = "clustered by dbl_pos",
           # legend.labs = c("high", "low", "mid", "mid-high", "mid-low"),
           pval = TRUE, # pval.coord = c(2100,.53),
           conf.int = FALSE,
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table (count(%))",
           risk.table = "abs_pct",
           risk.table.y.text = FALSE,
           risk.table.fontsize = 3,
           tables.theme = theme_survminer(font.main = c(13, "bold", "black"),
                                          font.y = c(0, "bold", "transparent"))
)
```
<br>

### Cluster for tumor intratumoral FoxP3 because it can be expressed by tumor cell
```{r}
clust <- Mclust(clust_markers$percent_FoxP3_tumor.i)
summary(clust)
clust_markers$clusters_FoxP3_ <- clust$classification
# clust_markers$clusters_FoxP3_ <- factor(clust_markers$clusters_FoxP3_, 
#                            levels = c(1, 2),
#                            labels = c("hot", "immunosuppressed"))

clust_markers %>% 
  gather(key = "markers_cat", value = "value", c("percent_CD3_tumor.i":"percent_CD11b_CD15_tumor.i")) %>% 
  select(suid, clusters_FoxP3_, markers_cat, value) %>% 
  ggplot(aes(x=suid, y=value, group=markers_cat, color=markers_cat))+
  geom_boxplot()+
  facet_grid(.~ clusters_FoxP3_)

ggsurvplot(
  survfit(Surv(time = clust_markers$timelastfu_new, event = clust_markers$surv_vital) ~ clust_markers$clusters_FoxP3_), 
  data = clust_markers,
           title = "Survival analysis on match population ROIs",
           font.main = c(16, "bold", "black"),
           xlab = "Time (days)", 
           # legend.title = "clustered by dbl_pos",
           # legend.labs = c("high", "low", "mid", "mid-high", "mid-low"),
           pval = TRUE, # pval.coord = c(2100,.53),
           conf.int = FALSE,
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table (count(%))",
           risk.table = "abs_pct",
           risk.table.y.text = FALSE,
           risk.table.fontsize = 3,
           tables.theme = theme_survminer(font.main = c(13, "bold", "black"),
                                          font.y = c(0, "bold", "transparent"))
) + guides(colour = guide_legend(ncol = 2))
```
I don't like that one because we know that FoxP3 usually has a negative effect. But this cluster grouped high FoxP3 with high+low CD8 which at the end bias the survivals.
<br>

### Cluster for tumor intratumoral CD11b/CD15 
```{r}
clust <- Mclust(clust_markers$percent_CD11b_CD15_tumor.i)
summary(clust)
clust_markers$clusters_CD11bCD15 <- clust$classification
# clust_markers$clusters_CD11bCD15 <- factor(clust_markers$clusters_CD11bCD15, 
#                            levels = c(1, 2),
#                            labels = c("hot", "immunosuppressed"))

clust_markers %>% 
  gather(key = "markers_cat", value = "value", c("percent_CD3_tumor.i":"percent_CD11b_CD15_tumor.i")) %>% 
  select(suid, clusters_CD11bCD15, markers_cat, value) %>% 
  ggplot(aes(x=suid, y=value, group=markers_cat, color=markers_cat))+
  geom_boxplot()+
  facet_grid(.~ clusters_CD11bCD15)

ggsurvplot(
  survfit(Surv(time = clust_markers$timelastfu_new, event = clust_markers$surv_vital) ~ clust_markers$clusters_CD11bCD15), 
  data = clust_markers,
           title = "Survival analysis on match population ROIs",
           font.main = c(16, "bold", "black"),
           xlab = "Time (days)", 
           # legend.title = "clustered by dbl_pos",
           # legend.labs = c("high", "low", "mid", "mid-high", "mid-low"),
           pval = TRUE, # pval.coord = c(2100,.53),
           conf.int = FALSE,
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table (count(%))",
           risk.table = "abs_pct",
           risk.table.y.text = FALSE,
           risk.table.fontsize = 3,
           tables.theme = theme_survminer(font.main = c(13, "bold", "black"),
                                          font.y = c(0, "bold", "transparent"))
)
```
<br>







