---
title: "Immune marker time to interview"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: cerulean #darkly
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
h1.title {
  font-size: 25px;
}
.figure {
   margin-top: 25px;
   <!-- margin-bottom: 100px; -->
}

table {
    margin-top: 25px;
    <!-- margin-bottom: 100px !important; -->
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      # fig.width = 7, fig.height = 5, 
                      fig.align='center'#, fig.show='hold'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

<style>
div.blue { background-color:#0099CC; border-radius: 5px; padding: 20px; font-size: 38px}
</style>
<div class = "blue">

<span style="color: white;">Investigate family history</span>

</div>
<br>

```{r library, include=FALSE}
# library(drake)
library(tidyverse)
library(data.table)
# library(VennDiagram)
library(gtsummary)
library(survival)
library(survminer)
library(psych)
# library(corrplot)
# library(ggcorrplot)
library(mclust)
library(sensemakr)
```

```{r load}

ROI_global <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_AACES_NCOCS/ROI_global.rds")
clinical_data <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_AACES_NCOCS/clinical_data.rds")

# Rewove patients not matched or lost match
ROI_global <- left_join(ROI_global, clinical_data, by="suid") %>% drop_na(pair_id) %>% 
  group_by(pair_id) %>% 
  mutate(have_a_match = dense_rank(interaction(suid, pair_id))) %>% 
  group_by(pair_id) %>% 
  mutate(is_paired = max(have_a_match)) %>% 
  filter(is_paired == 2) %>% 
  select(pair_id, everything(), -c(is_paired, have_a_match)) %>% 
  ungroup()

# markers_match <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_AACES_NCOCS/markers_match.rds")
path <- fs::path("","Volumes","Peres_Research","Christelle Colin-Leitzinger", "IF_AACES_NCOCS", "Disparities manuscript", "Figures")

# Remove these IDs from peripheral ROI because 2 are NAs and 2 are there matched
remove_id <- paste0(c("110318", "43220", "42774", "46619"), collapse = "|")
```
<br>
<br>

***

```{r}
ROI_global %>% 
  distinct(suid, .keep_all = TRUE) %>% 
  select(famhxbr, famhxov, ovcancermom_age, ovcancersis_age, brcancermom_age, 
         race) %>% 
  tbl_summary(by = race,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              type = list(c(famhxbr, famhxov) ~ "categorical"),

              digits = list(all_continuous() ~ 1)) %>%
      modify_header(list(label ~ "**Patient characteristics**", all_stat_cols() ~ "**{level}**, N = {n}")) %>% 
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05) %>% as_gt()
```


```{r}
# tbl <- ROI_global %>% 
#   distinct(suid, .keep_all = TRUE) %>% 
#   select(refage, refage_cat, stage, BMI_recent, BMI_recent_grp,
#         smoker, diab,
#          dblkstat_CA125, adj,
#          race) %>% 
#   tbl_summary(by = race,
#               statistic = list(all_continuous() ~ "{mean} ({sd})"),
#               label = list(refage ~ "Age at diagnosis", refage_cat ~ "Age at diagnosis category",
#                            dblkstat_CA125 ~ "Debulking Status", adj ~ "Adjuvant chemotherapy",
#                            smoker ~ "Smoking status"),
#               type = list(diab ~ "categorical"),
#               digits = list(all_continuous() ~ 1)) %>%
#       modify_header(list(label ~ "**Patient characteristics**", all_stat_cols() ~ "**{level}**, N = {n}")) %>% 
#   add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05) %>% as_gt()
# tbl
# # gt::gtsave(tbl, paste0(path, "/Table 1 Patient characteristics overall and by race_ethnicity.pdf"))

```
<br>

***


```{r summarize mean}
markers_ROIi <- ROI_global %>% 
  filter(intratumoral_i_vs_peripheral_p_ == "Intratumoral") %>% 
  group_by(suid) %>% 
  summarize(
    mean_tumor = mean(percent_tumor),
    mean_stroma = mean(percent_stroma),
    mean_total = mean(percent_total),
    # variance_tumor = var(percent_tumor),
    # variance_stroma = var(percent_stroma),
    percent_CD3_tumor = mean(tumor_percent_cd3_opal_650_positive_cells),
    percent_CD8_tumor = mean(tumor_percent_cd8_opal_570_positive_cells),
    percent_CD3_CD8_tumor = mean(tumor_percent_cd3plus_cd8plus_positive_cells),
    percent_FoxP3_tumor = mean(tumor_percent_foxp3_opal_540_positive_cells),
    percent_CD3_FoxP3_tumor = mean(tumor_percent_cd3plus_foxp3plus_positive_cells),
    percent_CD11b_tumor = mean(tumor_percent_cd11b_opal_620_positive_cells),
    percent_CD15_tumor = mean(tumor_percent_cd15_opal_520_positive_cells),
    percent_CD11b_CD15_tumor = mean(tumor_percent_cd11bplus_cd15plus_positive_cells),
    percent_CD3_stroma = mean(stroma_percent_cd3_opal_650_positive_cells),
    percent_CD8_stroma = mean(stroma_percent_cd8_opal_570_positive_cells),
    percent_CD3_CD8_stroma = mean(stroma_percent_cd3plus_cd8plus_positive_cells),
    percent_FoxP3_stroma = mean(stroma_percent_foxp3_opal_540_positive_cells),
    percent_CD3_FoxP3_stroma = mean(stroma_percent_cd3plus_foxp3plus_positive_cells),
    percent_CD11b_stroma = mean(stroma_percent_cd11b_opal_620_positive_cells),
    percent_CD15_stroma = mean(stroma_percent_cd15_opal_520_positive_cells),
    percent_CD11b_CD15_stroma = mean(stroma_percent_cd11bplus_cd15plus_positive_cells),
    
    percent_CD3_total = mean(percent_cd3_opal_650_positive_cells),
    percent_CD8_total = mean(percent_cd8_opal_570_positive_cells),
    percent_CD3_CD8_total = mean(percent_cd3plus_cd8plus_positive_cells),
    percent_FoxP3_total = mean(percent_foxp3_opal_540_positive_cells),
    percent_CD3_FoxP3_total = mean(percent_cd3plus_foxp3plus_positive_cells),
    percent_CD11b_total = mean(percent_cd11b_opal_620_positive_cells),
    percent_CD15_total = mean(percent_cd15_opal_520_positive_cells),
    percent_CD11b_CD15_total = mean(percent_cd11bplus_cd15plus_positive_cells)
  )
markers_ROIi$tumor_variation <- markers_ROIi$mean_tumor - mean(ROI_global$percent_tumor)
markers_ROIi$stroma_variation <- markers_ROIi$mean_stroma - mean(ROI_global$percent_stroma)
markers_ROIi$total_variation <- markers_ROIi$mean_stroma - mean(ROI_global$percent_stroma)
#
markers_ROIp <- ROI_global %>% 
  filter(!str_detect(suid, paste0(remove_id, collapse = "|")), 
         intratumoral_i_vs_peripheral_p_ == "Peripheral") %>% 
  group_by(suid) %>% 
  summarize(
    mean_tumor = mean(percent_tumor),
    mean_stroma = mean(percent_stroma),
    mean_total = mean(percent_total),
    # variance_tumor = var(percent_tumor),
    # variance_stroma = var(percent_stroma),
    percent_CD3_tumor = mean(tumor_percent_cd3_opal_650_positive_cells),
    percent_CD8_tumor = mean(tumor_percent_cd8_opal_570_positive_cells),
    percent_CD3_CD8_tumor = mean(tumor_percent_cd3plus_cd8plus_positive_cells),
    percent_FoxP3_tumor = mean(tumor_percent_foxp3_opal_540_positive_cells),
    percent_CD3_FoxP3_tumor = mean(tumor_percent_cd3plus_foxp3plus_positive_cells),
    percent_CD11b_tumor = mean(tumor_percent_cd11b_opal_620_positive_cells),
    percent_CD15_tumor = mean(tumor_percent_cd15_opal_520_positive_cells),
    percent_CD11b_CD15_tumor = mean(tumor_percent_cd11bplus_cd15plus_positive_cells),
    percent_CD3_stroma = mean(stroma_percent_cd3_opal_650_positive_cells),
    percent_CD8_stroma = mean(stroma_percent_cd8_opal_570_positive_cells),
    percent_CD3_CD8_stroma = mean(stroma_percent_cd3plus_cd8plus_positive_cells),
    percent_FoxP3_stroma = mean(stroma_percent_foxp3_opal_540_positive_cells),
    percent_CD3_FoxP3_stroma = mean(stroma_percent_cd3plus_foxp3plus_positive_cells),
    percent_CD11b_stroma = mean(stroma_percent_cd11b_opal_620_positive_cells),
    percent_CD15_stroma = mean(stroma_percent_cd15_opal_520_positive_cells),
    percent_CD11b_CD15_stroma = mean(stroma_percent_cd11bplus_cd15plus_positive_cells),
    percent_CD3_total = mean(percent_cd3_opal_650_positive_cells),
    percent_CD8_total = mean(percent_cd8_opal_570_positive_cells),
    percent_CD3_CD8_total = mean(percent_cd3plus_cd8plus_positive_cells),
    percent_FoxP3_total = mean(percent_foxp3_opal_540_positive_cells),
    percent_CD3_FoxP3_total = mean(percent_cd3plus_foxp3plus_positive_cells),
    percent_CD11b_total = mean(percent_cd11b_opal_620_positive_cells),
    percent_CD15_total = mean(percent_cd15_opal_520_positive_cells),
    percent_CD11b_CD15_total = mean(percent_cd11bplus_cd15plus_positive_cells)
  )
markers_ROIp$tumor_variation <- markers_ROIp$mean_tumor - mean(ROI_global$percent_tumor)
markers_ROIp$stroma_variation <- markers_ROIp$mean_stroma - mean(ROI_global$percent_stroma)
markers_ROIp$total_variation <- markers_ROIp$mean_total - mean(ROI_global$percent_total)

# Join Intratumoral and Peropheral ROI
markers_ROI <- full_join(markers_ROIi, markers_ROIp,
                         by= "suid", suffix= c(".i", ".p"))
markers_ROI <- left_join(markers_ROI, clinical_data, by="suid")
# clust_markers <- markers_ROI
```

# Abundance countinous by famhxbr
```{r Table tumor cells in ROIs}
# reset_gtsummary_theme()
# theme_gtsummary_journal(journal = "jama")
tbl1 <-
  markers_ROI %>% 
  select(percent_CD3_tumor.i, percent_CD3_CD8_tumor.i, percent_CD3_FoxP3_tumor.i, 
              percent_CD11b_tumor.i, percent_CD11b_CD15_tumor.i,
         famhxbr) %>% 
  rename(percent_CD3_tumor = percent_CD3_tumor.i, percent_CD3_CD8_tumor = percent_CD3_CD8_tumor.i,
         percent_CD3_FoxP3_tumor = percent_CD3_FoxP3_tumor.i, 
         percent_CD11b_tumor = percent_CD11b_tumor.i, percent_CD11b_CD15_tumor = percent_CD11b_CD15_tumor.i) %>% 
  tbl_summary(by = famhxbr,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              label = list(percent_CD3_tumor ~ "percent CD3+", percent_CD3_CD8_tumor ~ "percent CD3+/CD8+",
                           percent_CD3_FoxP3_tumor ~ "percent CD3+/FoxP3+",
                           percent_CD11b_tumor ~ "percent CD11b+", percent_CD11b_CD15_tumor ~ "percent CD11b+/CD15+"),
              missing = "no", digits = list(all_continuous() ~ 2)) %>% 
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05)
tbl2 <-
  markers_ROI %>% 
  select(percent_CD3_stroma.i, percent_CD3_CD8_stroma.i, percent_CD3_FoxP3_stroma.i, 
              percent_CD11b_stroma.i, percent_CD11b_CD15_stroma.i,
         famhxbr) %>% 
  rename(percent_CD3_stroma = percent_CD3_stroma.i, percent_CD3_CD8_stroma = percent_CD3_CD8_stroma.i,
         percent_CD3_FoxP3_stroma = percent_CD3_FoxP3_stroma.i, 
         percent_CD11b_stroma = percent_CD11b_stroma.i, percent_CD11b_CD15_stroma = percent_CD11b_CD15_stroma.i) %>% 
  tbl_summary(by = famhxbr,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
                           label = list(percent_CD3_stroma ~ "percent CD3+", percent_CD3_CD8_stroma ~ "percent CD3+/CD8+",
                           percent_CD3_FoxP3_stroma ~ "percent CD3+/FoxP3+",
                           percent_CD11b_stroma ~ "percent CD11b+", percent_CD11b_CD15_stroma ~ "percent CD11b+/CD15+"),
              missing = "no", digits = list(all_continuous() ~ 2)) %>% 
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05) 
tbl3 <-
  markers_ROI %>% 
  select(percent_CD3_total.i, percent_CD3_CD8_total.i, percent_CD3_FoxP3_total.i, 
              percent_CD11b_total.i, percent_CD11b_CD15_total.i,
         famhxbr) %>% 
  rename(percent_CD3_total = percent_CD3_total.i, percent_CD3_CD8_total = percent_CD3_CD8_total.i,
         percent_CD3_FoxP3_total = percent_CD3_FoxP3_total.i, 
         percent_CD11b_total = percent_CD11b_total.i, percent_CD11b_CD15_total = percent_CD11b_CD15_total.i) %>% 
  tbl_summary(by = famhxbr,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
                           label = list(percent_CD3_total ~ "percent CD3+", percent_CD3_CD8_total ~ "percent CD3+/CD8+",
                           percent_CD3_FoxP3_total ~ "percent CD3+/FoxP3+",
                           percent_CD11b_total ~ "percent CD11b+", percent_CD11b_CD15_total ~ "percent CD11b+/CD15+"),
              missing = "no", digits = list(all_continuous() ~ 2)) %>% 
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05) 


tbl5 <-
  markers_ROI %>% 
  select(percent_CD3_tumor.p, percent_CD3_CD8_tumor.p, percent_CD3_FoxP3_tumor.p, 
              percent_CD11b_tumor.p, percent_CD11b_CD15_tumor.p,
         famhxbr) %>% 
  rename(percent_CD3_tumor = percent_CD3_tumor.p, percent_CD3_CD8_tumor = percent_CD3_CD8_tumor.p,
         percent_CD3_FoxP3_tumor = percent_CD3_FoxP3_tumor.p, 
         percent_CD11b_tumor = percent_CD11b_tumor.p, percent_CD11b_CD15_tumor = percent_CD11b_CD15_tumor.p) %>% 
  tbl_summary(by = famhxbr,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
                            label = list(percent_CD3_tumor ~ "percent CD3+", percent_CD3_CD8_tumor ~ "percent CD3+/CD8+",
                           percent_CD3_FoxP3_tumor ~ "percent CD3+/FoxP3+",
                           percent_CD11b_tumor ~ "percent CD11b+", percent_CD11b_CD15_tumor ~ "percent CD11b+/CD15+"),
              missing = "no", digits = list(all_continuous() ~ 2)) %>% 
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05)
tbl6 <-
  markers_ROI %>% 
  select(percent_CD3_stroma.p, percent_CD3_CD8_stroma.p, percent_CD3_FoxP3_stroma.p, 
              percent_CD11b_stroma.p, percent_CD11b_CD15_stroma.p,
         famhxbr) %>% 
  rename(percent_CD3_stroma = percent_CD3_stroma.p, percent_CD3_CD8_stroma = percent_CD3_CD8_stroma.p,
         percent_CD3_FoxP3_stroma = percent_CD3_FoxP3_stroma.p, 
         percent_CD11b_stroma = percent_CD11b_stroma.p, percent_CD11b_CD15_stroma = percent_CD11b_CD15_stroma.p) %>% 
  tbl_summary(by = famhxbr,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
                            label = list(percent_CD3_stroma ~ "percent CD3+", percent_CD3_CD8_stroma ~ "percent CD3+/CD8+",
                           percent_CD3_FoxP3_stroma ~ "percent CD3+/FoxP3+",
                           percent_CD11b_stroma ~ "percent CD11b+", percent_CD11b_CD15_stroma ~ "percent CD11b+/CD15+"),
              missing = "no", digits = list(all_continuous() ~ 2)) %>% 
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05)
tbl7 <-
  markers_ROI %>% 
  select(percent_CD3_total.p, percent_CD3_CD8_total.p, percent_CD3_FoxP3_total.p, 
              percent_CD11b_total.p, percent_CD11b_CD15_total.p,
         famhxbr) %>% 
  rename(percent_CD3_total = percent_CD3_total.p, percent_CD3_CD8_total = percent_CD3_CD8_total.p,
         percent_CD3_FoxP3_total = percent_CD3_FoxP3_total.p, 
         percent_CD11b_total = percent_CD11b_total.p, percent_CD11b_CD15_total = percent_CD11b_CD15_total.p) %>% 
  tbl_summary(by = famhxbr,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
                            label = list(percent_CD3_total ~ "percent CD3+", percent_CD3_CD8_total ~ "percent CD3+/CD8+",
                           percent_CD3_FoxP3_total ~ "percent CD3+/FoxP3+",
                           percent_CD11b_total ~ "percent CD11b+", percent_CD11b_CD15_total ~ "percent CD11b+/CD15+"),
              missing = "no", digits = list(all_continuous() ~ 2)) %>% 
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05) 

tbl4 <- tbl_merge(list(tbl1, tbl5), tab_spanner = c("**Intratumoral**", "**Peripheral**"))
tbl8 <- tbl_merge(list(tbl2, tbl6), tab_spanner = c("**Intratumoral**", "**Peripheral**"))
tbl9 <- tbl_merge(list(tbl3, tbl7), tab_spanner = c("**Intratumoral**", "**Peripheral**"))


tbl10 <- tbl_stack(list(tbl4, tbl8, tbl9), group_header = c("Tumor", "Stroma", "Overall")) %>% as_gt()
tbl10

# gt::gtsave(tbl10, paste0(path, "/Table 2a Distribution of immune cell abundance in ROIs.pdf"))

# tbl8 <- tbl_stack(list(tbl5, tbl6, tbl7), group_header = c("Tumor", "Stroma", "Overall"))
# tbl8
# 
# tbl <- tbl_merge(list(tbl4, tbl8), tab_spanner = c("**Intratumoral**", "**Peripheral**"))# %>%
#   # modify_spanning_header(everything() ~ "Overall (tmor+stroma) ROIs") %>% as_gt()
# tbl
```
<br>




# Abundance category

```{r new median}
markers_ROI <- markers_ROI %>% 
  
  mutate(CD3_tumor.i = case_when(
    
    percent_CD3_tumor.i <= 1      ~ "low",
    percent_CD3_tumor.i > 1       ~ "high"
  ), CD3_tumor.i = factor(CD3_tumor.i, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_tumor.i = case_when(
    percent_CD3_CD8_tumor.i <= 1      ~ "low",
    percent_CD3_CD8_tumor.i > 1       ~ "high"
  ), CD3_CD8_tumor.i = factor(CD3_CD8_tumor.i, levels = c("low","high"))) %>% 
  mutate(CD3_FoxP3_tumor.i = case_when(
    percent_CD3_FoxP3_tumor.i <= 1      ~ "low",
    percent_CD3_FoxP3_tumor.i > 1       ~ "high"
  ), CD3_FoxP3_tumor.i = factor(CD3_FoxP3_tumor.i, levels = c("low","high"))) %>% 
  mutate(CD11b_tumor.i = case_when(
    percent_CD11b_tumor.i == 0      ~ "Absence",
    percent_CD11b_tumor.i > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_CD15_tumor.i = case_when(
    percent_CD11b_CD15_tumor.i == 0      ~ "Absence",
    percent_CD11b_CD15_tumor.i > 0       ~ "Presence"
  )) %>% 
  
  mutate(CD3_stroma.i = case_when(
    percent_CD3_stroma.i <= 1      ~ "low",
    percent_CD3_stroma.i > 1       ~ "high"
  ), CD3_stroma.i = factor(CD3_stroma.i, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_stroma.i = case_when(
    percent_CD3_CD8_stroma.i <= 1      ~ "low",
    percent_CD3_CD8_stroma.i > 1       ~ "high"
  ), CD3_CD8_stroma.i = factor(CD3_CD8_stroma.i, levels = c("low","high"))) %>% 
  mutate(CD3_FoxP3_stroma.i = case_when(
    percent_CD3_FoxP3_stroma.i <= 1      ~ "low",
    percent_CD3_FoxP3_stroma.i > 1       ~ "high"
  ), CD3_FoxP3_stroma.i = factor(CD3_FoxP3_stroma.i, levels = c("low","high"))) %>% 
  mutate(CD11b_stroma.i = case_when(
    percent_CD11b_stroma.i == 0      ~ "Absence",
    percent_CD11b_stroma.i > 0       ~ "Presence"
  )) %>%
  mutate(CD11b_CD15_stroma.i = case_when(
    percent_CD11b_CD15_stroma.i == 0      ~ "Absence",
    percent_CD11b_CD15_stroma.i > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_stroma.i3 = case_when(
    percent_CD11b_stroma.i <= 1      ~ "low",
    percent_CD11b_stroma.i > 1       ~ "high"
  ), CD11b_stroma.i3 = factor(CD11b_stroma.i3, levels = c("low","high"))) %>%
  mutate(CD11b_CD15_stroma.i3 = case_when(
    percent_CD11b_CD15_stroma.i <= 1      ~ "low",
    percent_CD11b_CD15_stroma.i > 1       ~ "high"
  ), CD11b_CD15_stroma.i3 = factor(CD11b_CD15_stroma.i3, levels = c("low","high"))) %>% 
  mutate(CD3_total.i = case_when(
    percent_CD3_total.i <= 1      ~ "low",
    percent_CD3_total.i > 1       ~ "high"
  ), CD3_total.i = factor(CD3_total.i, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_total.i = case_when(
    percent_CD3_CD8_total.i <= 1      ~ "low",
    percent_CD3_CD8_total.i > 1       ~ "high"
  ), CD3_CD8_total.i = factor(CD3_CD8_total.i, levels = c("low","high"))) %>% 
  mutate(CD3_FoxP3_total.i = case_when(
    percent_CD3_FoxP3_total.i <= 1      ~ "low",
    percent_CD3_FoxP3_total.i > 1       ~ "high"
  ), CD3_FoxP3_total.i = factor(CD3_FoxP3_total.i, levels = c("low","high"))) %>% 
  mutate(CD11b_total.i = case_when(
    percent_CD11b_total.i == 0      ~ "Absence",
    percent_CD11b_total.i > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_CD15_total.i = case_when(
    percent_CD11b_CD15_total.i == 0      ~ "Absence",
    percent_CD11b_CD15_total.i > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_total.i3 = case_when(
    percent_CD11b_total.i <= 1      ~ "low",
    percent_CD11b_total.i > 1       ~ "high"
  ), CD11b_total.i3 = factor(CD11b_total.i3, levels = c("low","high"))) %>% 
  mutate(CD11b_CD15_total.i3 = case_when(
    percent_CD11b_CD15_total.i <= 1      ~ "low",
    percent_CD11b_CD15_total.i > 1       ~ "high"
  ), CD11b_CD15_total.i3 = factor(CD11b_CD15_total.i3, levels = c("low","high"))) %>% 
  
  
  mutate(CD3_tumor.p = case_when(
    percent_CD3_tumor.p <= 1      ~ "low",
    percent_CD3_tumor.p > 1       ~ "high"
  ), CD3_tumor.p = factor(CD3_tumor.p, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_tumor.p = case_when(
    percent_CD3_CD8_tumor.p <= 1      ~ "low",
    percent_CD3_CD8_tumor.p > 1       ~ "high"
  ), CD3_CD8_tumor.p = factor(CD3_CD8_tumor.p, levels = c("low","high"))) %>% 
  mutate(CD3_FoxP3_tumor.p = case_when(
    percent_CD3_FoxP3_tumor.p <= 1      ~ "low",
    percent_CD3_FoxP3_tumor.p > 1       ~ "high"
  ), CD3_FoxP3_tumor.p = factor(CD3_FoxP3_tumor.p, levels = c("low","high"))) %>% 
  mutate(CD11b_tumor.p = case_when(
    percent_CD11b_tumor.p == 0      ~ "Absence",
    percent_CD11b_tumor.p > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_CD15_tumor.p = case_when(
    percent_CD11b_CD15_tumor.p == 0      ~ "Absence",
    percent_CD11b_CD15_tumor.p > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_tumor.p3 = case_when(
    percent_CD11b_tumor.p <= 1      ~ "low",
    percent_CD11b_tumor.p > 1         ~ "high"
  ), CD11b_tumor.p3 = factor(CD11b_tumor.p3, levels = c("low","high"))) %>% 
  mutate(CD11b_CD15_tumor.p3 = case_when(
    percent_CD11b_CD15_tumor.p <= 1      ~ "low",
    percent_CD11b_CD15_tumor.p > 1       ~ "high"
  ), CD11b_CD15_tumor.p3 = factor(CD11b_CD15_tumor.p3, levels = c("low","high"))) %>% 
  mutate(CD3_stroma.p = case_when(
    percent_CD3_stroma.p <= 1      ~ "low",
    percent_CD3_stroma.p > 1       ~ "high"
  ), CD3_stroma.p = factor(CD3_stroma.p, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_stroma.p = case_when(
    percent_CD3_CD8_stroma.p <= 1      ~ "low",
    percent_CD3_CD8_stroma.p > 1       ~ "high"
  ), CD3_CD8_stroma.p = factor(CD3_CD8_stroma.p, levels = c("low","high"))) %>% 
  mutate(CD3_FoxP3_stroma.p = case_when(
    percent_CD3_FoxP3_stroma.p <= 1      ~ "low",
    percent_CD3_FoxP3_stroma.p > 1       ~ "high"
  ), CD3_FoxP3_stroma.p = factor(CD3_FoxP3_stroma.p, levels = c("low","high"))) %>% 
  mutate(CD11b_stroma.p = case_when(
    percent_CD11b_stroma.p == 0      ~ "Absence",
    percent_CD11b_stroma.p > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_CD15_stroma.p = case_when(
    percent_CD11b_CD15_stroma.p == 0      ~ "Absence",
    percent_CD11b_CD15_stroma.p > 0       ~ "Presence"
  )) %>% 
    mutate(CD11b_stroma.p3 = case_when(
    percent_CD11b_stroma.p <= 1      ~ "low",
    percent_CD11b_stroma.p > 1       ~ "high"
  ), CD11b_stroma.p3 = factor(CD11b_stroma.p3, levels = c("low","high"))) %>% 
  mutate(CD11b_CD15_stroma.p3 = case_when(
    percent_CD11b_CD15_stroma.p <= 1      ~ "low",
    percent_CD11b_CD15_stroma.p > 1       ~ "high"
  ), CD11b_CD15_stroma.p3 = factor(CD11b_CD15_stroma.p3, levels = c("low","high"))) %>% 
  mutate(CD3_total.p = case_when(
    percent_CD3_total.p <= 1      ~ "low",
    percent_CD3_total.p > 1       ~ "high"
  ), CD3_total.p = factor(CD3_total.p, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_total.p = case_when(
    percent_CD3_CD8_total.p <= 1      ~ "low",
    percent_CD3_CD8_total.p > 1       ~ "high"
  ), CD3_CD8_total.p = factor(CD3_CD8_total.p, levels = c("low","high"))) %>% 
  mutate(CD3_FoxP3_total.p = case_when(
    percent_CD3_FoxP3_total.p <= 1      ~ "low",
    percent_CD3_FoxP3_total.p > 1       ~ "high"
  ), CD3_FoxP3_total.p = factor(CD3_FoxP3_total.p, levels = c("low","high"))) %>% 
  mutate(CD11b_total.p = case_when(
    percent_CD11b_total.p == 0      ~ "Absence",
    percent_CD11b_total.p > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_CD15_total.p = case_when(
    percent_CD11b_CD15_total.p == 0      ~ "Absence",
    percent_CD11b_CD15_total.p > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_total.p3 = case_when(
    percent_CD11b_total.p <= 1      ~ "low",
    percent_CD11b_total.p > 1       ~ "high"
  ), CD11b_total.p3 = factor(CD11b_total.p3, levels = c("low","high"))) %>% 
  mutate(CD11b_CD15_total.p3 = case_when(
    percent_CD11b_CD15_total.p <= 1      ~ "low",
    percent_CD11b_CD15_total.p > 1       ~ "high"
  ), CD11b_CD15_total.p3 = factor(CD11b_CD15_total.p3, levels = c("low","high"))) 



# for(i in 1:length(colnames(markers_ROI))) {
#   
#   
#   if(str_detect(markers_ROI[,i], "percent_CD|percent_Fox")) {
#     
#     markers_ROI <- markers_ROI %>%
#       mutate(.[,i] = case_when(
#     [,i] <= median([,i][[,i]>0])      ~ "low",
#     [,i] > median([,i][[,i]>0])      ~ "high",
#     [,i] == 0                         ~ "zero"
#   ))
#     
#     
#   }
#   print(markers_ROI[,i])
# }
# 
# for (v in colnames(df[ ,grepl(".x",names(df))])) {
#   print(v)
#   df$v <- ifelse(is.na(df$v), ols$coefficients[1]+ols$coefficients[2]*log(df$gsub(".x",".y",v)), df$v)
# }
```

`r emo::ji("question_mark")`Here do you want n(%) or mean(SD)??

```{r Table classification cells in ROIs}
tbl1 <-
  markers_ROI %>% 
  select(CD3_tumor.i, CD3_CD8_tumor.i, CD3_FoxP3_tumor.i, 
              CD11b_tumor.i, CD11b_CD15_tumor.i,
         famhxbr) %>% 
  rename(CD3_tumor = CD3_tumor.i, CD3_CD8_tumor = CD3_CD8_tumor.i,
         CD3_FoxP3_tumor = CD3_FoxP3_tumor.i, 
         CD11b_tumor = CD11b_tumor.i, CD11b_CD15_tumor = CD11b_CD15_tumor.i) %>% 
  tbl_summary(by = famhxbr,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              label = list(CD3_tumor ~ "percent CD3+", CD3_CD8_tumor ~ "percent CD3+/CD8+",
                           CD3_FoxP3_tumor ~ "percent CD3+/FoxP3+",
                           CD11b_tumor ~ "percent CD11b+", CD11b_CD15_tumor ~ "percent CD11b+/CD15+"),
              missing = "no") %>% 
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05)
tbl2 <-
  markers_ROI %>% 
  select(CD3_stroma.i, CD3_CD8_stroma.i, CD3_FoxP3_stroma.i, 
              CD11b_stroma.i, CD11b_CD15_stroma.i,
famhxbr) %>% 
  rename(CD3_stroma = CD3_stroma.i, CD3_CD8_stroma = CD3_CD8_stroma.i,
         CD3_FoxP3_stroma = CD3_FoxP3_stroma.i, 
CD11b_stroma = CD11b_stroma.i, CD11b_CD15_stroma = CD11b_CD15_stroma.i) %>% 
  tbl_summary(by = famhxbr,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
                           label = list(CD3_stroma ~ "percent CD3+", CD3_CD8_stroma ~ "percent CD3+/CD8+",
                           CD3_FoxP3_stroma ~ "percent CD3+/FoxP3+",
                           CD11b_stroma ~ "percent CD11b+", CD11b_CD15_stroma ~ "percent CD11b+/CD15+"),
              missing = "no") %>% 
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05) 
tbl3 <-
  markers_ROI %>% 
  select(CD3_total.i, CD3_CD8_total.i, CD3_FoxP3_total.i, 
              CD11b_total.i, CD11b_CD15_total.i,
famhxbr) %>% 
  rename(CD3_total = CD3_total.i, CD3_CD8_total = CD3_CD8_total.i,
         CD3_FoxP3_total = CD3_FoxP3_total.i, 
CD11b_total = CD11b_total.i, CD11b_CD15_total = CD11b_CD15_total.i) %>% 
  tbl_summary(by = famhxbr,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
                           label = list(CD3_total ~ "percent CD3+", CD3_CD8_total ~ "percent CD3+/CD8+",
                           CD3_FoxP3_total ~ "percent CD3+/FoxP3+",
                           CD11b_total ~ "percent CD11b+", CD11b_CD15_total ~ "percent CD11b+/CD15+"),
              missing = "no") %>% 
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05) 


tbl5 <-
  markers_ROI %>% 
  select(CD3_tumor.p, CD3_CD8_tumor.p, CD3_FoxP3_tumor.p, 
              CD11b_tumor.p, CD11b_CD15_tumor.p,
famhxbr) %>% 
  rename(CD3_tumor = CD3_tumor.p, CD3_CD8_tumor = CD3_CD8_tumor.p,
         CD3_FoxP3_tumor = CD3_FoxP3_tumor.p, 
CD11b_tumor = CD11b_tumor.p, CD11b_CD15_tumor = CD11b_CD15_tumor.p) %>% 
  tbl_summary(by = famhxbr,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
                            label = list(CD3_tumor ~ "percent CD3+", CD3_CD8_tumor ~ "percent CD3+/CD8+",
                           CD3_FoxP3_tumor ~ "percent CD3+/FoxP3+",
                           CD11b_tumor ~ "percent CD11b+", CD11b_CD15_tumor ~ "percent CD11b+/CD15+"),
              missing = "no") %>% 
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05)
tbl6 <-
  markers_ROI %>% 
  select(CD3_stroma.p, CD3_CD8_stroma.p, CD3_FoxP3_stroma.p, 
              CD11b_stroma.p, CD11b_CD15_stroma.p,
famhxbr) %>% 
  rename(CD3_stroma = CD3_stroma.p, CD3_CD8_stroma = CD3_CD8_stroma.p,
         CD3_FoxP3_stroma = CD3_FoxP3_stroma.p, 
CD11b_stroma = CD11b_stroma.p, CD11b_CD15_stroma = CD11b_CD15_stroma.p) %>% 
  tbl_summary(by = famhxbr,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
                            label = list(CD3_stroma ~ "percent CD3+", CD3_CD8_stroma ~ "percent CD3+/CD8+",
                           CD3_FoxP3_stroma ~ "percent CD3+/FoxP3+",
                           CD11b_stroma ~ "percent CD11b+", CD11b_CD15_stroma ~ "percent CD11b+/CD15+"),
              missing = "no") %>% 
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05)
tbl7 <-
  markers_ROI %>% 
  select(CD3_total.p, CD3_CD8_total.p, CD3_FoxP3_total.p, 
              CD11b_total.p, CD11b_CD15_total.p,
famhxbr) %>% 
  rename(CD3_total = CD3_total.p, CD3_CD8_total = CD3_CD8_total.p,
         CD3_FoxP3_total = CD3_FoxP3_total.p, 
CD11b_total = CD11b_total.p, CD11b_CD15_total = CD11b_CD15_total.p) %>% 
  tbl_summary(by = famhxbr,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
                            label = list(CD3_total ~ "percent CD3+", CD3_CD8_total ~ "percent CD3+/CD8+",
                           CD3_FoxP3_total ~ "percent CD3+/FoxP3+",
                           CD11b_total ~ "percent CD11b+", CD11b_CD15_total ~ "percent CD11b+/CD15+"),
              missing = "no") %>% 
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05) 

tbl4 <- tbl_merge(list(tbl1, tbl5), tab_spanner = c("**Intratumoral**", "**Peripheral**"))
tbl8 <- tbl_merge(list(tbl2, tbl6), tab_spanner = c("**Intratumoral**", "**Peripheral**"))
tbl9 <- tbl_merge(list(tbl3, tbl7), tab_spanner = c("**Intratumoral**", "**Peripheral**"))


tbl10 <- tbl_stack(list(tbl4, tbl8, tbl9), group_header = c("Tumor", "Stroma", "Overall")) %>% as_gt() %>% 
    gt::tab_source_note(gt::md('**"Low" represent categories with less than 1% immune cells detected while "Absent" represent categories with no immune cells detected**'))

tbl10
# gt::gtsave(tbl10, paste0(path, "/Table 2b Distribution of immune cell abundance absent_1percent categories in ROIs.pdf"))
```
<br>

***

# Immunoscore

When we decided for every group I can put cluster and immunoscore together in the same table.
I took the immunoscore calculated on the mean of the 3 value per patient.
```{r immunoscore per patients mean}
markers_ROI <- markers_ROI %>% 
  mutate(percentile_score_CD3_i = ntile(percent_CD3_total.i, 100) ) %>% 
  mutate(percentile_score_CD3_p = ntile(percent_CD3_total.p, 100) ) %>% 
  mutate(percentile_score_CD8_i = ntile(percent_CD8_total.i, 100) ) %>% 
  mutate(percentile_score_CD8_p = ntile(percent_CD8_total.p, 100) ) 

markers_ROI <- markers_ROI %>%
  mutate(percentile_score_mean = rowMeans( markers_ROI[c("percentile_score_CD3_i", "percentile_score_CD3_p", 
                                                    "percentile_score_CD8_i", "percentile_score_CD8_p")] ))
markers_ROI <- markers_ROI %>%
  mutate(immunoscore_patients = case_when(
    percentile_score_mean <= 10        ~ 0,
    percentile_score_mean <= 25        ~ 1,
    percentile_score_mean <= 70        ~ 2,
    percentile_score_mean <= 95        ~ 3,
    percentile_score_mean > 95         ~ 4 
  )) %>% 
  mutate(immunoscore_patients = factor(immunoscore_patients)) %>% 
  mutate(immunoscore_2018lancet_patients = case_when(
    percentile_score_mean <= 25        ~ "Low",
    percentile_score_mean <= 70        ~ "Intermediate",
    percentile_score_mean > 70         ~ "High"
    )) %>% 
  mutate(immunoscore_2018lancet_patients = factor(immunoscore_2018lancet_patients, levels = c("Low", "Intermediate", "High"))) 
```

```{r Table immunoscore}
tbl <- markers_ROI %>% 
  select(immunoscore_patients, immunoscore_2018lancet_patients,
         famhxbr) %>% 
  tbl_summary(by = famhxbr,
              label = list(immunoscore_patients ~ "classic immunoscore", 
                           immunoscore_2018lancet_patients ~ "immunoscore lancet"),
              missing = "no") %>% 
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05) %>% as_gt()
tbl
# gt::gtsave(tbl10, paste0(path, "/Table 2c Immunoscore in ROIs.pdf"))
```
<b>

***
<br>

# Cluster

```{r removing double stain from single stain count}
# markers_ROI <- markers_ROI %>% 
#   mutate(percent_CD3_total.i = percent_CD3_total.i - percent_CD3_CD8_total.i - percent_CD3_FoxP3_total.i) %>% 
#   mutate(percent_CD8_total.i = percent_CD8_total.i - percent_CD3_CD8_total.i) %>% 
#   mutate(percent_FoxP3_total.i = percent_FoxP3_total.i - percent_CD3_FoxP3_total.i) %>% 
#   mutate(percent_CD11b_total.i = percent_CD11b_total.i - percent_CD11b_CD15_total.i) %>% 
#   mutate(percent_CD15_total.i = percent_CD15_total.i - percent_CD11b_CD15_total.i) %>% 
#   
#   mutate(percent_CD3_tumor.i = percent_CD3_tumor.i - percent_CD3_CD8_tumor.i - percent_CD3_FoxP3_tumor.i) %>% 
#   mutate(percent_CD8_tumor.i = percent_CD8_tumor.i - percent_CD3_CD8_tumor.i) %>% 
#   mutate(percent_FoxP3_tumor.i = percent_FoxP3_tumor.i - percent_CD3_FoxP3_tumor.i) %>% 
#   mutate(percent_CD11b_tumor.i = percent_CD11b_tumor.i - percent_CD11b_CD15_tumor.i) %>% 
#   mutate(percent_CD15_tumor.i = percent_CD15_tumor.i - percent_CD11b_CD15_tumor.i) %>% 
#   
#   mutate(percent_CD3_stroma.i = percent_CD3_stroma.i - percent_CD3_CD8_stroma.i - percent_CD3_FoxP3_stroma.i) %>% 
#   mutate(percent_CD8_stroma.i = percent_CD8_stroma.i - percent_CD3_CD8_stroma.i) %>% 
#   mutate(percent_FoxP3_stroma.i = percent_FoxP3_stroma.i - percent_CD3_FoxP3_stroma.i) %>% 
#   mutate(percent_CD11b_stroma.i = percent_CD11b_stroma.i - percent_CD11b_CD15_stroma.i) %>% 
#   mutate(percent_CD15_stroma.i = percent_CD15_stroma.i - percent_CD11b_CD15_stroma.i) %>% 
#   
#   mutate(percent_CD3_total.p = percent_CD3_total.p - percent_CD3_CD8_total.p - percent_CD3_FoxP3_total.p) %>% 
#   mutate(percent_CD8_total.p = percent_CD8_total.p - percent_CD3_CD8_total.p) %>% 
#   mutate(percent_FoxP3_total.p = percent_FoxP3_total.p - percent_CD3_FoxP3_total.p) %>% 
#   mutate(percent_CD11b_total.p = percent_CD11b_total.p - percent_CD11b_CD15_total.p) %>% 
#   mutate(percent_CD15_total.p = percent_CD15_total.p - percent_CD11b_CD15_total.p) %>% 
#   
#   mutate(percent_CD3_tumor.p = percent_CD3_tumor.p - percent_CD3_CD8_tumor.p - percent_CD3_FoxP3_tumor.p) %>% 
#   mutate(percent_CD8_tumor.p = percent_CD8_tumor.p - percent_CD3_CD8_tumor.p) %>% 
#   mutate(percent_FoxP3_tumor.p = percent_FoxP3_tumor.p - percent_CD3_FoxP3_tumor.p) %>% 
#   mutate(percent_CD11b_tumor.p = percent_CD11b_tumor.p - percent_CD11b_CD15_tumor.p) %>% 
#   mutate(percent_CD15_tumor.p = percent_CD15_tumor.p - percent_CD11b_CD15_tumor.p) %>% 
#   
#   mutate(percent_CD3_stroma.p = percent_CD3_stroma.p - percent_CD3_CD8_stroma.p - percent_CD3_FoxP3_stroma.p) %>% 
#   mutate(percent_CD8_stroma.p = percent_CD8_stroma.p - percent_CD3_CD8_stroma.p) %>% 
#   mutate(percent_FoxP3_stroma.p = percent_FoxP3_stroma.p - percent_CD3_FoxP3_stroma.p) %>% 
#   mutate(percent_CD11b_stroma.p = percent_CD11b_stroma.p - percent_CD11b_CD15_stroma.p) %>% 
#   mutate(percent_CD15_stroma.p = percent_CD15_stroma.p - percent_CD11b_CD15_stroma.p)
```
<br>

## Cluster with a non-defined number of cluster **when looking at all intra/periph + tumor/stroma (CD3, CD3/8, CD3/FoxP3, CD11b, CD11b/15)**  
**Each markers are scaled, default method is center**  


```{r clustering}
set.seed(1234)

### Cluster for stroma/tumor in the intratumoral/peritumoral ROIs 
clust_markers <- markers_ROI %>% 
  filter(!is.na(markers_ROI$percent_CD3_CD8_tumor.i) & !is.na(markers_ROI$percent_CD3_CD8_tumor.p)) %>% 
  select(suid, c("percent_CD3_tumor.i", "percent_CD3_CD8_tumor.i", "percent_CD3_FoxP3_tumor.i", "percent_CD11b_tumor.i", "percent_CD11b_CD15_tumor.i",
                 "percent_CD3_stroma.i", "percent_CD3_CD8_stroma.i", "percent_CD3_FoxP3_stroma.i", "percent_CD11b_stroma.i", "percent_CD11b_CD15_stroma.i",
                 "percent_CD3_tumor.p", "percent_CD3_CD8_tumor.p", "percent_CD3_FoxP3_tumor.p", "percent_CD11b_tumor.p", "percent_CD11b_CD15_tumor.p",
                 "percent_CD3_stroma.p", "percent_CD3_CD8_stroma.p", "percent_CD3_FoxP3_stroma.p", "percent_CD11b_stroma.p", "percent_CD11b_CD15_stroma.p"
                 ))

clust <- Mclust(scale(clust_markers[,c(2:ncol(clust_markers))]))
summary(clust)

# X <- clust_markers[,-1]
# BIC <- mclustBIC(X)
# plot(BIC)
# summary(BIC)

clust_markers$clusters_all_IandP <- clust$classification
clust_markers$clusters_all_IandP <- factor(clust_markers$clusters_all_IandP,
                                           levels = c(1, 2, 3),
                                           labels = c("mid", "high", "low"))
# clust_markers$clusters_all_IandP <- factor(clust_markers$clusters_all_IandP,
#                                            levels = c(1, 2, 3, 4, 5),
#                                            labels = c("mid", "high", "mid-low", "mid-high", "low"))
# clust_markers <- clust_markers %>% mutate(clusters_all_IandP = factor(clusters_all_IandP, levels = c("low", "mid-low", "mid", "mid-high", "high")))
clust_markers <- clust_markers %>% mutate(clusters_all_IandP = factor(clusters_all_IandP, levels = c("low", "mid", "high")))

# clust_markers %>% 
# tidyr::gather(key = "markers_cat", value = "value",
#               c("percent_CD3_tumor.i":"percent_CD11b_CD15_stroma.i")) %>% 
#   select(suid, clusters_all_IandP, markers_cat, value) %>% 
#   ggplot(aes(x=suid, y=value, group=markers_cat,  color=markers_cat))+
#   geom_boxplot()+
#   facet_grid(.~ clusters_all_IandP)
# clust_markers %>% 
# tidyr::gather(key = "markers_cat", value = "value",
#               c("percent_CD3_tumor.p":"percent_CD11b_CD15_stroma.p")) %>% 
#   select(suid, clusters_all_IandP, markers_cat, value) %>% 
#   ggplot(aes(x=suid, y=value, group=markers_cat,  color=markers_cat))+
#   geom_boxplot()+
#   facet_grid(.~ clusters_all_IandP)
markers_ROI <- full_join(markers_ROI, clust_markers %>% select(suid, clusters_all_IandP), by = "suid")


### Cluster for tumor intratumoral all double positive "percent_CD3_CD8_tumor.i", "percent_CD3_FoxP3_tumor.i", "percent_CD11b_CD15_tumor.i"
clust_markers <- markers_ROI %>% filter(!is.na(markers_ROI$percent_CD3_CD8_tumor.i ))
clust <- 
  Mclust(clust_markers[,c("percent_CD3_CD8_tumor.i", "percent_CD3_FoxP3_tumor.i", "percent_CD11b_CD15_tumor.i")])
summary(clust)
clust_markers$dbl_pos <- clust$classification
clust_markers$dbl_pos <- factor(clust_markers$dbl_pos,
                                           levels = c(1, 2, 3),
                                           labels = c("low", "high", "mid"))
clust_markers <- clust_markers %>% mutate(dbl_pos = factor(dbl_pos, levels = c("low", "mid", "high")))

### Cluster for tumor intratumoral CD3-CD8
clust <- Mclust(clust_markers$percent_CD3_CD8_tumor.i)
summary(clust)
clust_markers$clusters_CD3CD8 <- clust$classification
clust_markers$clusters_CD3CD8 <- factor(clust_markers$clusters_CD3CD8,
                                           levels = c(1, 2, 3, 4, 5),
                                           labels = c("low", "mid-low", "mid", "mid-high", "high"))

### Cluster for tumor intratumoral CD3-FoxP3
clust <- Mclust(clust_markers$percent_CD3_FoxP3_tumor.i)
summary(clust)
clust_markers$clusters_CD3FoxP3 <- clust$classification
clust_markers$clusters_CD3FoxP3 <- factor(clust_markers$clusters_CD3FoxP3,
                                           levels = c(1, 2, 3),
                                           labels = c("low", "mid", "high"))

### Cluster for tumor intratumoral FoxP3 because it can be expressed by tumor cell
clust <- Mclust(clust_markers$percent_FoxP3_tumor.i)
summary(clust)
clust_markers$clusters_FoxP3_ <- clust$classification
clust_markers$clusters_FoxP3_ <- factor(clust_markers$clusters_FoxP3_,
                                           levels = c(1, 2, 3, 4),
                                           labels = c("low", "mid", "mid-high", "high"))

### Cluster for tumor intratumoral CD11b/CD15 
clust <- Mclust(clust_markers$percent_CD11b_CD15_tumor.i)
summary(clust)
clust_markers$clusters_CD11bCD15 <- clust$classification
clust_markers$clusters_CD11bCD15 <- factor(clust_markers$clusters_CD11bCD15,
                                           levels = c(1, 7, 8),
                                           labels = c("low", "high", "mid"))
clust_markers <- clust_markers %>% mutate(clusters_CD11bCD15 = factor(clusters_CD11bCD15, levels = c("low", "mid", "high")))

markers_ROI <- full_join(markers_ROI, clust_markers %>% select(suid, dbl_pos, clusters_CD3CD8, clusters_CD3FoxP3, clusters_FoxP3_, clusters_CD11bCD15), by = "suid")

```
<br>

```{r Table cluster}
tbl <- markers_ROI %>% 
  select(clusters_all_IandP, dbl_pos, clusters_CD3CD8, clusters_CD3FoxP3, clusters_FoxP3_, clusters_CD11bCD15,
         famhxbr) %>% 
  tbl_summary(by = famhxbr,
              label = list(clusters_all_IandP ~ "intra+periph, tumor+stroma", dbl_pos ~ "all double positive",
                           clusters_CD3CD8 ~ "CD3+/CD8+",
                           clusters_CD3FoxP3 ~ "CD3+/FoxP3+", clusters_FoxP3_ ~ "FoxP3+",
                           clusters_CD11bCD15 ~ "CD11b+/CD15+"),
              missing = "no") %>% 
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05) %>% as_gt()
tbl
# gt::gtsave(tbl, paste0(path, "/Table 2d Cluster in ROIs.pdf"))
```

<!-- # Test visualisation abundance in mclust groups -->
<!-- ## Immunoscore -->
```{r}
library(ggridges)


# # a <- markers_ROI %>% 
# #   filter(!is.na(immunoscore_2018lancet_patients)) %>% 
# #   select(immunoscore_2018lancet_patients, 
# #          percent_CD3_tumor = percent_CD3_tumor.p, 
# #          percent_CD3_CD8_tumor = percent_CD3_CD8_tumor.p, 
# #          percent_CD3_FoxP3_tumor = percent_CD3_FoxP3_tumor.p, 
# #          percent_CD11b_tumor = percent_CD11b_tumor.p, 
# #          percent_CD11b_CD15_tumor = percent_CD11b_CD15_tumor.p) %>% 
# #   pivot_longer(-immunoscore_2018lancet_patients, names_to = "markers", values_to = "value") %>% 
# #   mutate(location = "Peripheral")
# # 
# # 
# # markers_ROI %>% 
# #   filter(!is.na(immunoscore_2018lancet_patients)) %>% 
# #   select(immunoscore_2018lancet_patients, 
# #          percent_CD3_tumor = percent_CD3_tumor.i, 
# #          percent_CD3_CD8_tumor = percent_CD3_CD8_tumor.i, 
# #          percent_CD3_FoxP3_tumor = percent_CD3_FoxP3_tumor.i, 
# #          percent_CD11b_tumor = percent_CD11b_tumor.i, 
# #          percent_CD11b_CD15_tumor = percent_CD11b_CD15_tumor.i) %>% 
# #   pivot_longer(-immunoscore_2018lancet_patients, names_to = "markers", values_to = "value") %>% 
# #   mutate(location = "Intratumoral") %>% 
# #   bind_rows(., a) %>% 
# #   
# #   
# #   ggplot( aes(y=markers, x=value,  fill=markers, 
# #               linetype = location
# #               )) +
# #     geom_density_ridges(alpha=0.6#, 
# #                         # stat="binline", bins=20
# #                         ) +
# #     theme_ridges()+
# #   theme(
# #     axis.text.y = element_blank(),
# #       panel.spacing = unit(0.1, "lines"),
# #       strip.text.x = element_text(size = 8)
# #     ) +
# #   
# #   facet_wrap(~ immunoscore_2018lancet_patients, nrow = 1)
# 
# 
# b <- markers_ROI %>% 
#   filter(!is.na(immunoscore_2018lancet_patients)) %>% 
#   select(immunoscore_2018lancet_patients, 
#          percent_CD3 = percent_CD3_stroma.i, 
#          percent_CD3_CD8 = percent_CD3_CD8_stroma.i, 
#          percent_CD3_FoxP3 = percent_CD3_FoxP3_stroma.i, 
#          percent_CD11b = percent_CD11b_stroma.i, 
#          percent_CD11b_CD15 = percent_CD11b_CD15_stroma.i) %>% 
#   pivot_longer(-immunoscore_2018lancet_patients, names_to = "markers", values_to = "value") %>% 
#   mutate(location = "Stroma")
# 
# markers_ROI %>% 
#   filter(!is.na(immunoscore_2018lancet_patients)) %>% 
#   select(immunoscore_2018lancet_patients, 
#          percent_CD3 = percent_CD3_tumor.i, 
#          percent_CD3_CD8 = percent_CD3_CD8_tumor.i, 
#          percent_CD3_FoxP3 = percent_CD3_FoxP3_tumor.i, 
#          percent_CD11b = percent_CD11b_tumor.i, 
#          percent_CD11b_CD15 = percent_CD11b_CD15_tumor.i) %>% 
#   pivot_longer(-immunoscore_2018lancet_patients, names_to = "markers", values_to = "value") %>% 
#   mutate(location = "Tumor") %>% 
#   bind_rows(., b) %>% 
#   
#   ggplot(aes(y=markers, x=value,  fill=markers, linetype = location)) +
#     geom_density_ridges(alpha=0.5) +
#   ggtitle("Intratumoral")+
#     theme_ridges()+
#   theme(axis.text.y = element_blank(),
#         panel.spacing = unit(0.1, "lines"),
#         strip.text.x = element_text(size = 8)
#     ) +
#   
#   facet_wrap(~ immunoscore_2018lancet_patients, nrow = 1)
# 
# a <- markers_ROI %>% 
#   filter(!is.na(immunoscore_2018lancet_patients)) %>% 
#   select(immunoscore_2018lancet_patients, 
#          percent_CD3 = percent_CD3_stroma.p, 
#          percent_CD3_CD8 = percent_CD3_CD8_stroma.p, 
#          percent_CD3_FoxP3 = percent_CD3_FoxP3_stroma.p, 
#          percent_CD11b = percent_CD11b_stroma.p, 
#          percent_CD11b_CD15 = percent_CD11b_CD15_stroma.p) %>% 
#   pivot_longer(-immunoscore_2018lancet_patients, names_to = "markers", values_to = "value") %>% 
#   mutate(location = "Stroma")
# 
# markers_ROI %>% 
#   filter(!is.na(immunoscore_2018lancet_patients)) %>% 
#   select(immunoscore_2018lancet_patients, 
#          percent_CD3 = percent_CD3_tumor.p, 
#          percent_CD3_CD8 = percent_CD3_CD8_tumor.p, 
#          percent_CD3_FoxP3 = percent_CD3_FoxP3_tumor.p, 
#          percent_CD11b = percent_CD11b_tumor.p, 
#          percent_CD11b_CD15 = percent_CD11b_CD15_tumor.p) %>% 
#   pivot_longer(-immunoscore_2018lancet_patients, names_to = "markers", values_to = "value") %>% 
#   mutate(location = "Tumor") %>% 
#   bind_rows(., b) %>% 
#   
#   ggplot(aes(y=markers, x=value,  fill=markers, linetype = location)) +
#     geom_density_ridges(alpha=0.5) +
#   ggtitle("Peripheral")+
#     theme_ridges()+
#   theme(axis.text.y = element_blank(),
#         panel.spacing = unit(0.1, "lines"),
#         strip.text.x = element_text(size = 8)
#     ) +
#   
#   facet_wrap(~ immunoscore_2018lancet_patients, nrow = 1)
```

<!-- ## mclust -->

```{r ridges}
# b <- markers_ROI %>% 
#   filter(!is.na(clusters_all_IandP)) %>% 
#   select(clusters_all_IandP, 
#          percent_CD3 = percent_CD3_stroma.i, 
#          percent_CD3_CD8 = percent_CD3_CD8_stroma.i, 
#          percent_CD3_FoxP3 = percent_CD3_FoxP3_stroma.i, 
#          percent_CD11b = percent_CD11b_stroma.i, 
#          percent_CD11b_CD15 = percent_CD11b_CD15_stroma.i) %>% 
#   pivot_longer(-clusters_all_IandP, names_to = "markers", values_to = "value") %>% 
#   mutate(location = "Stroma")
# 
# markers_ROI %>% 
#   filter(!is.na(clusters_all_IandP)) %>% 
#   select(clusters_all_IandP, 
#          percent_CD3 = percent_CD3_tumor.i, 
#          percent_CD3_CD8 = percent_CD3_CD8_tumor.i, 
#          percent_CD3_FoxP3 = percent_CD3_FoxP3_tumor.i, 
#          percent_CD11b = percent_CD11b_tumor.i, 
#          percent_CD11b_CD15 = percent_CD11b_CD15_tumor.i) %>% 
#   pivot_longer(-clusters_all_IandP, names_to = "markers", values_to = "value") %>% 
#   mutate(location = "Tumor") %>% 
#   bind_rows(., b) %>% 
#   
#   ggplot(aes(y=markers, x=value,  fill=markers, linetype = location)) +
#     geom_density_ridges(alpha=0.5) +
#   ggtitle("Intratumoral")+
#     theme_ridges()+
#   theme(axis.text.y = element_blank(),
#         panel.spacing = unit(0.1, "lines"),
#         strip.text.x = element_text(size = 8)
#     ) +
#   
#   facet_wrap(~ clusters_all_IandP, nrow = 1)
# 
# a <- markers_ROI %>% 
#   filter(!is.na(clusters_all_IandP)) %>% 
#   select(clusters_all_IandP, 
#          percent_CD3 = percent_CD3_stroma.p, 
#          percent_CD3_CD8 = percent_CD3_CD8_stroma.p, 
#          percent_CD3_FoxP3 = percent_CD3_FoxP3_stroma.p, 
#          percent_CD11b = percent_CD11b_stroma.p, 
#          percent_CD11b_CD15 = percent_CD11b_CD15_stroma.p) %>% 
#   pivot_longer(-clusters_all_IandP, names_to = "markers", values_to = "value") %>% 
#   mutate(location = "Stroma")
# 
# markers_ROI %>% 
#   filter(!is.na(clusters_all_IandP)) %>% 
#   select(clusters_all_IandP, 
#          percent_CD3 = percent_CD3_tumor.p, 
#          percent_CD3_CD8 = percent_CD3_CD8_tumor.p, 
#          percent_CD3_FoxP3 = percent_CD3_FoxP3_tumor.p, 
#          percent_CD11b = percent_CD11b_tumor.p, 
#          percent_CD11b_CD15 = percent_CD11b_CD15_tumor.p) %>% 
#   pivot_longer(-clusters_all_IandP, names_to = "markers", values_to = "value") %>% 
#   mutate(location = "Tumor") %>% 
#   bind_rows(., b) %>% 
#   
#   ggplot(aes(y=markers, x=value,  fill=markers, linetype = location)) +
#     geom_density_ridges(alpha=0.5) +
#   ggtitle("Peripheral")+
#     theme_ridges()+
#   theme(axis.text.y = element_blank(),
#         panel.spacing = unit(0.1, "lines"),
#         strip.text.x = element_text(size = 8)
#     ) +
#   
#   facet_wrap(~ clusters_all_IandP, nrow = 1)
```

# Survival
```{r}
clin_surv <- markers_ROI
mysurv <- Surv(time = clin_surv$timelastfu_new, event = clin_surv$surv_vital)
myplot <- survfit(mysurv~clin_surv$famhxbr)

# pdf(paste0(path, "/Survivals/Immune cell clusters/OS CD3 grp matched pop.pdf"), width = 8, height = 7)
ggsurvplot(myplot, data = clin_surv,
           title = "Survival analysis on matched population",
           font.main = c(14, "bold", "black"), font.subtitle = c(6, "plain", "black"),
           xlab = "Time (days)", legend.title = "famhxbr", 
           # legend.labs = c("high", "low"),
           pval = TRUE,
           conf.int = FALSE,
           xlim = c(-10, 8000),
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table (number(%))",
           risk.table = "abs_pct",
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
)
```

## famhxbr = Yes
## Intratumoral
```{r}
clin_surv <- markers_ROI %>% 
  # filter(intratumoral_i_vs_peripheral_p_ == "Intratumoral") %>% 
  filter(famhxbr == "yes")
mysurv <- Surv(time = clin_surv$timelastfu_new, event = clin_surv$surv_vital)
myplot <- survfit(mysurv~clin_surv$CD3_total.i)

# pdf(paste0(path, "/Survivals/Immune cell clusters/OS CD3 grp matched pop.pdf"), width = 8, height = 7)
ggsurvplot(myplot, data = clin_surv,
           title = "Survival analysis on matched population",
           font.main = c(14, "bold", "black"), font.subtitle = c(6, "plain", "black"),
           xlab = "Time (days)", legend.title = "famhxbr", 
           # legend.labs = c("high", "low"),
           pval = TRUE,
           conf.int = FALSE,
           xlim = c(-10, 8000),
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table (number(%))",
           risk.table = "abs_pct",
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
)
```

## Peripheral
```{r}
clin_surv <- markers_ROI %>% 
  filter(famhxbr == "yes")
mysurv <- Surv(time = clin_surv$timelastfu_new, event = clin_surv$surv_vital)
myplot <- survfit(mysurv~clin_surv$CD3_total.p)

# pdf(paste0(path, "/Survivals/Immune cell clusters/OS CD3 grp matched pop.pdf"), width = 8, height = 7)
ggsurvplot(myplot, data = clin_surv,
           title = "Survival analysis on matched population",
           font.main = c(14, "bold", "black"), font.subtitle = c(6, "plain", "black"),
           xlab = "Time (days)", legend.title = "famhxbr", 
           # legend.labs = c("high", "low"),
           pval = TRUE,
           conf.int = FALSE,
           xlim = c(-10, 8000),
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table (number(%))",
           risk.table = "abs_pct",
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
)
```

## White
## Intratumoral
```{r}
clin_surv <- markers_ROI %>% 
  filter(famhxbr == "yes") %>% 
  filter(race == "White")
mysurv <- Surv(time = clin_surv$timelastfu_new, event = clin_surv$surv_vital)
myplot <- survfit(mysurv~clin_surv$CD3_total.i)

# pdf(paste0(path, "/Survivals/Immune cell clusters/OS CD3 grp matched pop.pdf"), width = 8, height = 7)
ggsurvplot(myplot, data = clin_surv,
           title = "Survival analysis on matched population",
           font.main = c(14, "bold", "black"), font.subtitle = c(6, "plain", "black"),
           xlab = "Time (days)", legend.title = "famhxbr", 
           # legend.labs = c("high", "low"),
           pval = TRUE,
           conf.int = FALSE,
           xlim = c(-10, 8000),
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table (number(%))",
           risk.table = "abs_pct",
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
)
```

# Peripheral
```{r}
clin_surv <- markers_ROI %>% 
  filter(famhxbr == "yes") %>% 
  filter(race == "White")
mysurv <- Surv(time = clin_surv$timelastfu_new, event = clin_surv$surv_vital)
myplot <- survfit(mysurv~clin_surv$CD3_total.p)

# pdf(paste0(path, "/Survivals/Immune cell clusters/OS CD3 grp matched pop.pdf"), width = 8, height = 7)
ggsurvplot(myplot, data = clin_surv,
           title = "Survival analysis on matched population",
           font.main = c(14, "bold", "black"), font.subtitle = c(6, "plain", "black"),
           xlab = "Time (days)", legend.title = "famhxbr", 
           # legend.labs = c("high", "low"),
           pval = TRUE,
           conf.int = FALSE,
           xlim = c(-10, 8000),
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table (number(%))",
           risk.table = "abs_pct",
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
)
```

## Black
## Intratumoral
```{r}
clin_surv <- markers_ROI %>% 
  filter(famhxbr == "yes") %>% 
  filter(race == "Black")
mysurv <- Surv(time = clin_surv$timelastfu_new, event = clin_surv$surv_vital)
myplot <- survfit(mysurv~clin_surv$CD3_total.i)

# pdf(paste0(path, "/Survivals/Immune cell clusters/OS CD3 grp matched pop.pdf"), width = 8, height = 7)
ggsurvplot(myplot, data = clin_surv,
           title = "Survival analysis on matched population",
           font.main = c(14, "bold", "black"), font.subtitle = c(6, "plain", "black"),
           xlab = "Time (days)", legend.title = "famhxbr", 
           # legend.labs = c("high", "low"),
           pval = TRUE,
           conf.int = FALSE,
           xlim = c(-10, 8000),
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table (number(%))",
           risk.table = "abs_pct",
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
)
```

# Peripheral
```{r}
clin_surv <- markers_ROI %>% 
  filter(famhxbr == "yes") %>% 
  filter(race == "Black")
mysurv <- Surv(time = clin_surv$timelastfu_new, event = clin_surv$surv_vital)
myplot <- survfit(mysurv~clin_surv$CD3_total.p)

# pdf(paste0(path, "/Survivals/Immune cell clusters/OS CD3 grp matched pop.pdf"), width = 8, height = 7)
ggsurvplot(myplot, data = clin_surv,
           title = "Survival analysis on matched population",
           font.main = c(14, "bold", "black"), font.subtitle = c(6, "plain", "black"),
           xlab = "Time (days)", legend.title = "famhxbr", 
           # legend.labs = c("high", "low"),
           pval = TRUE,
           conf.int = FALSE,
           xlim = c(-10, 8000),
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table (number(%))",
           risk.table = "abs_pct",
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
)
```