---
title: "Report June 11th 2020"
author: "Christelle M Colin-Leitzinger"
date: "6/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.width = 10, fig.height = 7)
```
<br>

# Report
***
```{r library, include=FALSE}
library(drake)
library(tidyverse)
library(data.table)
```

```{r}
loadd(clinical_data, ROI_tumor ,ROI_stroma ,TMA_tumor ,TMA_stroma, 
      TMA2_tumor, TMA2_stroma, TMAcases_remove,
      common_ROITMA_IDs)
```
## Data
Loading of clinical data, TMAs and ROIs data.  
**Clinical Data** is not cleaned yet.
```{r }
head(clinical_data)
```
I separated tumor and stroma in different dataframes.
```{r}
dim(TMA_tumor)
dim(TMA_stroma)
dim(ROI_tumor)
dim(ROI_stroma)
```
## Cleaning 
I made sure that all "removed core" the present in the 3rd tab of TMAs and ROIs files were removed.  
I also removed the 4 cases which were excluded in TMAs.
```{r}
# III-Remove the TMA IDs from patient excluded from the study
# Should only be done for TMAs
# Plus remove TMA with no IDs = controls images
uid <- paste(unique(TMAcases_remove$Subject_IDs), collapse = "|")
TMA_tumor <-
  TMA_tumor[(!grepl(uid, TMA_tumor$suid)), ] %>% 
  filter(!is.na(suid))
TMA_stroma <-
  TMA_stroma[(!grepl(uid, TMA_stroma$suid)),] %>% 
  filter(!is.na(suid))

# Did it for ROIs too in case  #------------------ All good so don't run anymore but still create suid 
ROI_tumor$suid <- substr(ROI_tumor$image_tag, start = 10, stop = 15)
# ROI_tumor <-
#   ROI_tumor[(!grepl(uid, ROI_tumor$suid)), ]
ROI_stroma$suid <- substr(ROI_stroma$image_tag, start = 10, stop = 15)
# ROI_stroma <-
#   ROI_stroma[(!grepl(uid, ROI_stroma$suid)), ]

# Cleaning
rm(TMA2_tumor, TMA2_stroma, uid, fct_name_repair, # roir_import,
   data_import, roit_import, rois_import, tmat_import, tmas_import,
   tma2t_import, tma2s_import, common_ROITMA_import, # tmar_import, 
   TMAcases_remove, case_remove_import)


#-----------------------------------------------------------------------------------------------------------------

# 1.	Calculate the % tumor and % stroma within each ROI/TMA core. 
# Provide the mean, median, and range of the % tumor and % stroma 
# for the TMA cores, intratumoral ROIs, and peripheral ROIs. 
# Also assess the variation by case in terms of the % tumor and % stroma. 



ROI_global <- merge.data.frame(ROI_tumor, ROI_stroma,
                               by.x = "image_tag", by.y = "image_tag",
                               all = TRUE) %>% 
  mutate(total_cell_number = tumor__total_cells + stroma__total_cells
         ) %>% 
  mutate(percent_tumor = round((tumor__total_cells / total_cell_number)*100, 2)
         ) %>% 
  mutate(percent_stroma = round((stroma__total_cells / total_cell_number)*100, 2)
         ) %>% 
  mutate_at(("intratumoral__i__vs_peripheral__p_.x"), ~ case_when(
    intratumoral__i__vs_peripheral__p_.x == "p" ~ "Peripheral",
    intratumoral__i__vs_peripheral__p_.x == "i" ~ "Intratumoral")
    ) %>% 
  mutate(suid.x = factor(suid.x))

TMA_global <- merge.data.frame(TMA_tumor, TMA_stroma,
                               by.x = "image_tag", by.y = "image_tag",
                               all = TRUE) %>% 
  mutate(total_cell_number = tumor__total_cells + stroma__total_cells
         ) %>% 
  mutate(percent_tumor = round((tumor__total_cells / total_cell_number)*100, 2)
         ) %>% 
  mutate(percent_stroma = round((stroma__total_cells / total_cell_number)*100, 2)
         ) %>% 
  mutate(suid.x = factor(suid.x))
dim(TMA_tumor)
dim(TMA_stroma)
dim(ROI_tumor)
dim(ROI_stroma)
```
I merged tumor and stroma data using image_tag into the same dataframe.  
**TMA_global dimension**
```{r }
dim(TMA_global)
print(paste("We have", length(unique(TMA_global$suid.x)), "unique ID in TMA with a total of", 
             length(TMA_global$image_tag), "samples"
             ))
```

**ROI_global dimension**
```{r }
dim(ROI_global)
print(paste("We have", length(unique(ROI_global$suid.x)), "unique ID in ROI with a total of", 
             length(ROI_global$image_tag), "samples"
             ))
```

## Tables
```{r}
variations_TMA <- group_by(TMA_global, suid.x) %>% 
  summarize(mean_tumor = mean(percent_tumor), mean_stroma = mean(percent_stroma)) %>% 
  mutate(ID = seq(1:nrow(.)))# %>% 
# mutate(suid.x = factor(suid.x))

variations_ROIip <- group_by(ROI_global, suid.x, intratumoral__i__vs_peripheral__p_.x) %>% 
  summarize(mean_tumor = mean(percent_tumor), mean_stroma = mean(percent_stroma))
setDT(variations_ROIip)[, ID := .GRP, .(suid.x)]

variations_ROI <- group_by(variations_ROIip, suid.x) %>% 
  summarize(mean_tumor = mean(mean_tumor), mean_stroma = mean(mean_stroma)) %>% 
  mutate(ID = seq(1:nrow(.)))

variations_TMA$tumor_variation <- variations_TMA$mean_tumor - mean(TMA_global$percent_tumor)
variations_TMA$stroma_variation <- variations_TMA$mean_stroma - mean(TMA_global$percent_stroma)
variations_ROIip$tumor_variation <- variations_ROIip$mean_tumor - mean(ROI_global$percent_tumor)
variations_ROIip$stroma_variation <- variations_ROIip$mean_stroma - mean(ROI_global$percent_stroma)
variations_ROI$tumor_variation <- variations_ROI$mean_tumor - mean(ROI_global$percent_tumor)
variations_ROI$stroma_variation <- variations_ROI$mean_stroma - mean(ROI_global$percent_stroma)


```
Here is a table with the different characteristics:

```{r table}
table <- matrix(c("", "Tumor", "Stroma",
                  "TMA", "", "",
                  "mean", round(mean(TMA_global$percent_tumor),2), round(mean(TMA_global$percent_stroma),2),
                  "median", median(TMA_global$percent_tumor), median(TMA_global$percent_stroma),
                  "range", 
                  paste(range(TMA_global$percent_tumor)[1],range(TMA_global$percent_tumor)[2], sep = "-"), 
                  paste(range(TMA_global$percent_stroma)[1],range(TMA_global$percent_stroma)[2], sep = "-"),
                  "variance", 
                  round(var(x= TMA_global$percent_tumor),2),
                  round(var(x= TMA_global$percent_stroma),2),
                  "sd",
                  round(sd(x= TMA_global$percent_tumor),2),
                  round(sd(x= TMA_global$percent_stroma),2),
                  "ROIs", "", "",
                  "intratumoral", "", "",
                  "mean",
                  round(mean(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Intratumoral")$percent_tumor),2),
                  round(mean(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Intratumoral")$percent_stroma),2),
                  "median",
                  median(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Intratumoral")$percent_tumor),
                  median(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Intratumoral")$percent_stroma),
                  "range",
                  paste(
                    range(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Intratumoral")$percent_tumor)[1],
                    range(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Intratumoral")$percent_tumor)[2],
                    sep = "-"
                  ),
                  paste(
                    range(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Intratumoral")$percent_stroma)[1],
                    range(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Intratumoral")$percent_stroma)[2],
                    sep = "-"
                  ),
                  "variance", 
                  round(var(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Intratumoral")$percent_tumor),2),
                  round(var(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Intratumoral")$percent_stroma),2),
                  "sd",
                  round(sd(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Intratumoral")$percent_tumor),2),
                  round(sd(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Intratumoral")$percent_stroma),2),
                  "peripheral", "", "",
                  "mean",
                  round(mean(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Peripheral")$percent_tumor),2),
                  round(mean(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Peripheral")$percent_stroma),2),
                  "median",
                  median(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Peripheral")$percent_tumor),
                  median(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Peripheral")$percent_stroma),
                  "range",
                  paste(
                    range(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Peripheral")$percent_tumor)[1],
                    range(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Peripheral")$percent_tumor)[2],
                    sep = "-"
                  ),
                  paste(
                    range(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Peripheral")$percent_stroma)[1],
                    range(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Peripheral")$percent_stroma)[2],
                    sep = "-"
                  ),
                  "variance", 
                  round(var(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Peripheral")$percent_tumor),2),
                  round(var(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Peripheral")$percent_stroma),2),
                  "sd",
                  round(sd(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Peripheral")$percent_tumor),2),
                  round(sd(x= filter(ROI_global, intratumoral__i__vs_peripheral__p_.x == "Peripheral")$percent_stroma),2)
), ncol = 3, byrow = TRUE)
print(table)
```

## Plots

```{r}
p1 <- ggplot(TMA_global) +
  geom_histogram(aes(tumor__total_cells), color = "grey", fill="darkred") +
  theme_minimal() +
  ylim(0,100) +
  labs(x="Tumor", y="count", title="Cell Type Repartition in TMAs")
p2 <- ggplot(TMA_global) +
  geom_histogram(aes(stroma__total_cells), color = "grey", fill="steelblue") +
  theme_minimal() +
  labs(x="Stroma", y="count", title="Cell Type Repartition in TMAs")
p3 <- ggplot(ROI_global) +
  geom_histogram(aes(tumor__total_cells), color = "grey", fill="darkred") +
  theme_minimal() +
  scale_y_continuous(limits=c(0,175)) +
  labs(x="Tumor", y="count", title="Cell Type Repartition in ROIs")
p4 <- ggplot(ROI_global) +
  geom_histogram(aes(stroma__total_cells), color = "grey", fill="steelblue") +
  theme_minimal() +
  scale_y_continuous(limits=c(0,175)) +
  labs(x="Stroma", y="count", title="Cell Type Repartition in ROIs")
gridExtra::grid.arrange(p1, p2, p3, p4, ncol = 2)




```
But it is a difference between Intratumoral vs Peripheral ROI.
```{r}
p1 <- ggplot(ROI_global) +
  geom_histogram(aes(tumor__total_cells), color = "grey", fill="darkred") +
  theme_minimal() +
  scale_y_continuous(limits=c(0,175)) +
  labs(x="Tumor", y="count") +
  facet_grid(.~intratumoral__i__vs_peripheral__p_.x)
p2 <- ggplot(ROI_global) +
  geom_histogram(aes(stroma__total_cells), color = "grey", fill="steelblue") +
  theme_minimal() +
  scale_y_continuous(limits=c(0,175)) +
  labs(x="Stroma", y="count") +
  facet_grid(.~intratumoral__i__vs_peripheral__p_.x)
gridExtra::grid.arrange(p1, p2, nrow = 2,
                        top = "Cell Type Repartition in ROIs")
```
It is easier to see with density plot
```{r}
p1 <- ggplot(ROI_global, aes(tumor__total_cells, colour = intratumoral__i__vs_peripheral__p_.x)) +
  geom_density(alpha=.3) +
  # scale_color_discrete(labels = c("intra", "periph")) +
  theme_minimal() +
  labs(x="Tumor", y="Sample Count", color='Sample \nPosition')
p2 <- ggplot(ROI_global, aes(stroma__total_cells, colour = intratumoral__i__vs_peripheral__p_.x)) +
  geom_density(alpha=.3) +
  # scale_color_discrete(labels = c("intra", "periph")) +
  theme_minimal() +
  labs(x="Stroma", y="Sample Count", color='Sample \nPosition')
p3 <- ggplot(ROI_global, aes(tumor__total_cells, linetype=intratumoral__i__vs_peripheral__p_.x, color = "tumor")) +
  geom_density(fill = "darkred", alpha = .3) +
  geom_density(aes(stroma__total_cells, linetype=intratumoral__i__vs_peripheral__p_.x), color = "steelblue") +
  theme_minimal() +
  scale_linetype_manual(name = "Sample \nPosition", labels = c("Intratumoral", "Peripheral"), values = 1:2) +
  labs(x="Amount of Cell", y="Sample Count", color="Cell Type")
gridExtra::grid.arrange(p1, p2, p3, ncol = 2,
                        top = "Cell Type Repartition in ROIs")
```
In TMA, it is more simple
```{r}
ggplot(TMA_global, aes(tumor__total_cells, color = "Tumor")) +
  geom_density() +
  geom_density(aes(stroma__total_cells, color = "Stroma")) +
  theme_minimal() +
  scale_linetype_manual(name = "Sample \nPosition", values = 1:2) +
  labs(x="Amount of Cell", y="Sample Count", title="Cell Type Repartition in TMAs", color="Cell Type")
```
***
## Variations

```{r}
p1 <- ggplot(variations_TMA, aes(x=suid.x, y=mean_tumor)) +
  geom_segment( aes(x=suid.x, xend=suid.x, y=0, yend=mean_tumor), color="skyblue") +
  geom_point(color="blue", size=1, alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  labs(x=paste(length(variations_TMA$ID), "Patients IDs"), y="% Tumor Cell (mean)", title="% of Tumor Cell Present in TMAs per Patient",
       subtitle = "Each point represent the mean of up to 3 values")


p2 <- ggplot(variations_ROI, aes(x=suid.x, y=mean_tumor)) +
  geom_segment( aes(x=suid.x, xend=suid.x, y=0, yend=mean_tumor), color="skyblue") +
  geom_point(color="blue", size=1, alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  labs(x=paste(length(variations_ROI$ID), "Patients IDs"), y="% Tumor Cell (mean)", title="% of Tumor Cell Present in ROIs per Patient",
       subtitle = "Each point represent the mean of up to 3 values")
gridExtra::grid.arrange(p1, p2, ncol = 2,
                        top = "Cell Type Repartition in ROIs")
```
We may have less variations between patients with the ROI but need to look at intratumoral vs Peripheral.  
I tried to take a look at the variation of samples compare to the mean of all samples.

```{r}
ggplot(variations_TMA, aes(x=ID, y=tumor_variation, colour = tumor_variation>0)) +
  annotate("text", x = .25, y = "mean", label = "High", color = "#8707A6FF", size = 3, hjust = 0, vjust = 1) +
  annotate("text", x = .25, y = "", label = "Low", color = "#00204DFF", size = 3, hjust = 2, vjust = 1) +
  geom_segment(aes(x=ID, xend=ID, y=0, yend=tumor_variation)) +
  geom_point(size=1, alpha=0.6) +
  theme_minimal() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  scale_color_manual(values = c("#00204DFF", "#8707A6FF")) +
  labs(x=paste(length(variations_TMA$ID), "Patients IDs"), y="% Tumor Cell (mean)", title="% Tumor Cell Present in TMAs per Patient",
       subtitle = "Each point represent the mean of up to 3 values")


ggplot(variations_TMA, aes(x=ID, y=stroma_variation, colour = stroma_variation>0)) +
  annotate("text", x = .25, y = "mean", label = "High", color = "#8707A6FF", size = 3, hjust = 0, vjust = 1) +
  annotate("text", x = .25, y = "", label = "Low", color = "#00204DFF", size = 3, hjust = 2, vjust = 1) +
  geom_segment(aes(x=ID, xend=ID, y=0, yend=stroma_variation)) +
  geom_point(size=1, alpha=0.6) +
  theme_minimal() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  scale_color_manual(values = c("#00204DFF", "#8707A6FF")) +
  labs(x=paste(length(variations_TMA$ID), "Patients IDs"), y="% Stromal Cell (mean)", title="% Stromal Cell Present in TMAs per Patient",
       subtitle = "Each point represent the mean of up to 3 values")


ggplot(variations_ROI, aes(x=ID, y=tumor_variation, colour = tumor_variation>0)) +
  annotate("text", x = .25, y = "mean", label = "High", color = "#8707A6FF", size = 3, hjust = 0, vjust = 1) +
  annotate("text", x = .25, y = "", label = "Low", color = "#00204DFF", size = 3, hjust = 2, vjust = 1) +
  geom_segment(aes(x=ID, xend=ID, y=0, yend=tumor_variation)) +
  geom_point(size=1, alpha=0.6) +
  theme_minimal() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  scale_color_manual(values = c("#00204DFF", "#8707A6FF")) +
  labs(x=paste(length(variations_ROI$ID), "Patients IDs"), y="% Tumor Cell (mean)", title="% Tumor Cell Present in ROIs per Patient",
       subtitle = "Each point represent the mean of up to 6 values")


ggplot(variations_ROI, aes(x=ID, y=stroma_variation, colour = stroma_variation>0)) +
  annotate("text", x = .25, y = "mean", label = "High", color = "#8707A6FF", size = 3, hjust = 0, vjust = 1) +
  annotate("text", x = .25, y = "", label = "Low", color = "#00204DFF", size = 3, hjust = 2, vjust = 1) +
  geom_segment(aes(x=ID, xend=ID, y=0, yend=stroma_variation)) +
  geom_point(size=1, alpha=0.6) +
  theme_minimal() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  scale_color_manual(values = c("#00204DFF", "#8707A6FF")) +
  labs(x=paste(length(variations_ROI$ID), "Patients IDs"), y="% Stromal Cell (mean)", title="% Stromal Cell Present in ROIs per Patient",
       subtitle = "Each point represent the mean of up to 6 values")


variations_ROIip %>% 
  filter(intratumoral__i__vs_peripheral__p_.x == "Intratumoral") %>% 
ggplot( aes(x=ID, y=tumor_variation, colour = tumor_variation>0)) +
  annotate("text", x = .25, y = "mean", label = "High", color = "#8707A6FF", size = 3, hjust = 0, vjust = 1) +
  annotate("text", x = .25, y = "", label = "Low", color = "#00204DFF", size = 3, hjust = 2, vjust = 1) +
  geom_segment(aes(x=ID, xend=ID, y=0, yend=tumor_variation)) +
  geom_point(size=1, alpha=0.6) +
  theme_minimal() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  scale_color_manual(values = c("#00204DFF", "#8707A6FF")) +
  labs(x=paste(length(variations_ROI$ID), "Patients IDs"), y="% Tumor Cell (mean)", title="% Tumor Cell Present in Intratumoral ROIs per Patient",
       subtitle = "Each point represent the mean of up to 3 values")


variations_ROIip %>% 
  filter(intratumoral__i__vs_peripheral__p_.x == "Peripheral") %>% 
  ggplot( aes(x=ID, y=tumor_variation, colour = tumor_variation>0)) +
  annotate("text", x = .25, y = "mean", label = "High", color = "#8707A6FF", size = 3, hjust = 0, vjust = 1) +
  annotate("text", x = .25, y = "", label = "Low", color = "#00204DFF", size = 3, hjust = 2, vjust = 1) +
  geom_segment(aes(x=ID, xend=ID, y=0, yend=tumor_variation)) +
  geom_point(size=1, alpha=0.6) +
  theme_minimal() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  scale_color_manual(values = c("#00204DFF", "#8707A6FF")) +
  labs(x=paste(length(variations_ROI$ID), "Patients IDs"), y="% Tumor Cell (mean)", title="% Tumor Cell Present in Peripheral ROIs per Patient",
       subtitle = "Each point represent the mean of up to 3 values")


variations_ROIip %>% 
  filter(intratumoral__i__vs_peripheral__p_.x == "Intratumoral") %>% 
  ggplot( aes(x=ID, y=stroma_variation, colour = stroma_variation>0)) +
  annotate("text", x = .25, y = "mean", label = "High", color = "#8707A6FF", size = 3, hjust = 0, vjust = 1) +
  annotate("text", x = .25, y = "", label = "Low", color = "#00204DFF", size = 3, hjust = 2, vjust = 1) +
  geom_segment(aes(x=ID, xend=ID, y=0, yend=stroma_variation)) +
  geom_point(size=1, alpha=0.6) +
  theme_minimal() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  scale_color_manual(values = c("#00204DFF", "#8707A6FF")) +
  labs(x=paste(nrow(variations_ROIip %>% filter(intratumoral__i__vs_peripheral__p_.x == "Intratumoral")), "Patients IDs"), y="% Stromal Cell (mean)", title="% Stromal Cell Present in Intratumoral ROIs per Patient",
       subtitle = "Each point represent the mean of up to 3 values")


variations_ROIip %>% 
  filter(intratumoral__i__vs_peripheral__p_.x == "Peripheral") %>% 
  ggplot( aes(x=ID, y=stroma_variation, colour = stroma_variation>0)) +
  annotate("text", x = .25, y = "mean", label = "High", color = "#8707A6FF", size = 3, hjust = 0, vjust = 1) +
  annotate("text", x = .25, y = "", label = "Low", color = "#00204DFF", size = 3, hjust = 2, vjust = 1) +
  geom_segment(aes(x=ID, xend=ID, y=0, yend=stroma_variation)) +
  geom_point(size=1, alpha=0.6) +
  theme_minimal() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  scale_color_manual(values = c("#00204DFF", "#8707A6FF")) +
  labs(x=paste(nrow(variations_ROIip %>% filter(intratumoral__i__vs_peripheral__p_.x == "Peripheral")), "Patients IDs"), y="% Stromal Cell (mean)", title="% Stromal Cell Present in Peripheral ROIs per Patient",
       subtitle = "Each point represent the mean of up to 3 values")
```
***
## Comparison for the patients whith ROIs and TMA
**variations dataframe**
```{r}
uid <- paste(unique(common_ROITMA_IDs$Subject_IDs), collapse = '|')
variations_TMA <- variations_TMA[(grepl(uid, variations_TMA$suid.x)),]
variations_ROI <- variations_ROI[(grepl(uid, variations_ROI$suid.x)),]
variations_ROIi <- variations_ROIip[(grepl(uid, variations_ROIip$suid.x)),] %>% 
  filter(intratumoral__i__vs_peripheral__p_.x == "Intratumoral")
variations_ROIp <- variations_ROIip[(grepl(uid, variations_ROIip$suid.x)),] %>% 
  filter(intratumoral__i__vs_peripheral__p_.x == "Peripheral")

variations <- merge.data.frame(variations_TMA %>% 
                                 select(-ID), 
                               variations_ROI %>% 
                                 select(-ID),
                               by.x = "suid.x", by.y = "suid.x",
                               all = TRUE, suffixes = c("_tma", "_roi"))
variations_ROIip <- merge.data.frame(variations_ROIi %>% 
                                       select(-ID),
                                     variations_ROIp %>% 
                                       select(-ID),
                                     by.x = "suid.x", by.y = "suid.x",
                                     all = TRUE, suffixes = c("_roi_i", "_roi_p"))
variations <- merge.data.frame(variations, variations_ROIip,
                               by.x = "suid.x", by.y = "suid.x",
                               all = TRUE) %>% 
  mutate(ID = seq(1:nrow(.)))
dim(variations)
```
### Plots
```{r}
ggplot(variations, aes(x=suid.x, y=mean_tumor_tma)) +
  geom_segment( aes(x=suid.x, xend=suid.x, y=0, yend=mean_tumor_tma), color="skyblue") +
  geom_point(color="blue", size=1, alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  labs(x=paste(length(variations$ID), "Patients IDs"), y="% Tumor Cell (mean)", title="% of Tumor Cell Present in TMAs per Patient",
       subtitle = "Each point represent the mean of up to 3 values")
# dev.off()

# peg(paste0(path, "/Christelle Colin-Leitzinger/IF_AACES_NCOCS/variation 28 patients_2.jpg"))
ggplot(variations, aes(x=suid.x, y=mean_tumor_roi)) +
  geom_segment( aes(x=suid.x, xend=suid.x, y=0, yend=mean_tumor_roi), color="skyblue") +
  geom_point(color="blue", size=1, alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  labs(x=paste(length(variations$ID), "Patients IDs"), y="% Tumor Cell (mean)", title="% of Tumor Cell Present in ROIs per Patient",
       subtitle = "Each point represent the mean of up to 3 values")
# dev.off()

# jpeg(paste0(path, "/Christelle Colin-Leitzinger/IF_AACES_NCOCS/variation 28 patients_1.jpg"))
ggplot(variations, aes(x=ID, y=tumor_variation_tma, colour = tumor_variation_tma>0)) +
  annotate("text", x = .25, y = "mean", label = "High", color = "#8707A6FF", size = 3, hjust = 0, vjust = 1) +
  annotate("text", x = .25, y = "", label = "Low", color = "#00204DFF", size = 3, hjust = 2, vjust = 1) +
  geom_segment(aes(x=ID, xend=ID, y=0, yend=tumor_variation_tma)) +
  geom_point(size=1, alpha=0.6) +
  theme_minimal() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  scale_color_manual(values = c("#00204DFF", "#8707A6FF")) +
  labs(x=paste(length(variations$ID), "Patients IDs"), y="% Tumor Cell (mean)", title="% Tumor Cell Present in TMAs per Patient",
       subtitle = "Each point represent the mean of up to 3 values")
# dev.off()

# jpeg(paste0(path, "/Christelle Colin-Leitzinger/IF_AACES_NCOCS/variation 28 patients_3.jpg"))
ggplot(variations, aes(x=ID, y=stroma_variation_tma, colour = stroma_variation_tma>0)) +
  annotate("text", x = .25, y = "mean", label = "High", color = "#8707A6FF", size = 3, hjust = 0, vjust = 1) +
  annotate("text", x = .25, y = "", label = "Low", color = "#00204DFF", size = 3, hjust = 2, vjust = 1) +
  geom_segment(aes(x=ID, xend=ID, y=0, yend=stroma_variation_tma)) +
  geom_point(size=1, alpha=0.6) +
  theme_minimal() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  scale_color_manual(values = c("#00204DFF", "#8707A6FF")) +
  labs(x=paste(length(variations$ID), "Patients IDs"), y="% Stromal Cell (mean)", title="% Stromal Cell Present in TMAs per Patient",
       subtitle = "Each point represent the mean of up to 3 values")
# dev.off()

# jpeg(paste0(path, "/Christelle Colin-Leitzinger/IF_AACES_NCOCS/variation 28 patients_4.jpg"))
ggplot(variations, aes(x=ID, y=tumor_variation_roi, colour = tumor_variation_roi>0)) +
  annotate("text", x = .25, y = "mean", label = "High", color = "#8707A6FF", size = 3, hjust = 0, vjust = 1) +
  annotate("text", x = .25, y = "", label = "Low", color = "#00204DFF", size = 3, hjust = 2, vjust = 1) +
  geom_segment(aes(x=ID, xend=ID, y=0, yend=tumor_variation_roi)) +
  geom_point(size=1, alpha=0.6) +
  theme_minimal() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  scale_color_manual(values = c("#00204DFF", "#8707A6FF")) +
  labs(x=paste(length(variations$ID), "Patients IDs"), y="% Tumor Cell (mean)", title="% Tumor Cell Present in ROIs per Patient",
       subtitle = "Each point represent the mean of up to 6 values")
# dev.off()

# jpeg(paste0(path, "/Christelle Colin-Leitzinger/IF_AACES_NCOCS/variation 28 patients_5.jpg"))
ggplot(variations, aes(x=ID, y=stroma_variation_roi, colour = stroma_variation_roi>0)) +
  annotate("text", x = .25, y = "mean", label = "High", color = "#8707A6FF", size = 3, hjust = 0, vjust = 1) +
  annotate("text", x = .25, y = "", label = "Low", color = "#00204DFF", size = 3, hjust = 2, vjust = 1) +
  geom_segment(aes(x=ID, xend=ID, y=0, yend=stroma_variation_roi)) +
  geom_point(size=1, alpha=0.6) +
  theme_minimal() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  scale_color_manual(values = c("#00204DFF", "#8707A6FF")) +
  labs(x=paste(length(variations$ID), "Patients IDs"), y="% Stromal Cell (mean)", title="% Stromal Cell Present in ROIs per Patient",
       subtitle = "Each point represent the mean of up to 6 values")
# dev.off()

# jpeg(paste0(path, "/Christelle Colin-Leitzinger/IF_AACES_NCOCS/variation 28 patients_6.jpg"))
ggplot(variations, aes(x=ID, y=tumor_variation_roi_i, colour = tumor_variation_roi_i>0)) +
  annotate("text", x = .25, y = "mean", label = "High", color = "#8707A6FF", size = 3, hjust = 0, vjust = 1) +
  annotate("text", x = .25, y = "", label = "Low", color = "#00204DFF", size = 3, hjust = 2, vjust = 1) +
  geom_segment(aes(x=ID, xend=ID, y=0, yend=tumor_variation_roi_i)) +
  geom_point(size=1, alpha=0.6) +
  theme_minimal() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  scale_color_manual(values = c("#00204DFF", "#8707A6FF")) +
  labs(x=paste(length(variations$ID), "Patients IDs"), y="% Tumor Cell (mean)", title="% Tumor Cell Present in Intratumoral ROIs per Patient",
       subtitle = "Each point represent the mean of up to 3 values")
# dev.off()

# jpeg(paste0(path, "/Christelle Colin-Leitzinger/IF_AACES_NCOCS/variation 28 patients_7.jpg"))
ggplot(variations, aes(x=ID, y=stroma_variation_roi_i, colour = stroma_variation_roi_i>0)) +
  annotate("text", x = .25, y = "mean", label = "High", color = "#8707A6FF", size = 3, hjust = 0, vjust = 1) +
  annotate("text", x = .25, y = "", label = "Low", color = "#00204DFF", size = 3, hjust = 2, vjust = 1) +
  geom_segment(aes(x=ID, xend=ID, y=0, yend=stroma_variation_roi_i)) +
  geom_point(size=1, alpha=0.6) +
  theme_minimal() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  scale_color_manual(values = c("#00204DFF", "#8707A6FF")) +
  labs(x=paste(length(variations$ID), "Patients IDs"), y="% Stromal Cell (mean)", title="% Stromal Cell Present in Intratumoral ROIs per Patient",
       subtitle = "Each point represent the mean of up to 3 values")
# dev.off()

# jpeg(paste0(path, "/Christelle Colin-Leitzinger/IF_AACES_NCOCS/variation 28 patients_8.jpg"))
ggplot(variations, aes(x=ID, y=tumor_variation_roi_p, colour = tumor_variation_roi_p>0)) +
  annotate("text", x = .25, y = "mean", label = "High", color = "#8707A6FF", size = 3, hjust = 0, vjust = 1) +
  annotate("text", x = .25, y = "", label = "Low", color = "#00204DFF", size = 3, hjust = 2, vjust = 1) +
  geom_segment(aes(x=ID, xend=ID, y=0, yend=tumor_variation_roi_p)) +
  geom_point(size=1, alpha=0.6) +
  theme_minimal() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  scale_color_manual(values = c("#00204DFF", "#8707A6FF")) +
  labs(x=paste(length(variations$ID), "Patients IDs"), y="% Tumor Cell (mean)", title="% Tumor Cell Present in Peripheral ROIs per Patient",
       subtitle = "Each point represent the mean of up to 3 values")
# dev.off()

# jpeg(paste0(path, "/Christelle Colin-Leitzinger/IF_AACES_NCOCS/variation 28 patients_9.jpg"))
ggplot(variations, aes(x=ID, y=stroma_variation_roi_p, colour = stroma_variation_roi_p>0)) +
  annotate("text", x = .25, y = "mean", label = "High", color = "#8707A6FF", size = 3, hjust = 0, vjust = 1) +
  annotate("text", x = .25, y = "", label = "Low", color = "#00204DFF", size = 3, hjust = 2, vjust = 1) +
  geom_segment(aes(x=ID, xend=ID, y=0, yend=stroma_variation_roi_p)) +
  geom_point(size=1, alpha=0.6) +
  theme_minimal() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) +
  scale_color_manual(values = c("#00204DFF", "#8707A6FF")) +
  labs(x=paste(length(variations$ID), "Patients IDs"), y="% Stromal Cell (mean)", title="% Stromal Cell Present in Peripheral ROIs per Patient",
       subtitle = "Each point represent the mean of up to 3 values")
# dev.off()


#
# Back to back 
  # geom_segment(aes(x = 2, y = 15, xend = 2, yend = 25),
  #                arrow = arrow(length = unit(0.5, "cm")))

ggplot(variations, aes(x=suid.x)) +
  geom_segment( aes(x=suid.x, xend=suid.x, y=0, yend=mean_tumor_tma, color="TMA"))+
  geom_point(aes(y=mean_tumor_tma), color="blue", size=1, alpha=0.6) +
  geom_segment( aes(x=suid.x, xend=suid.x, y=0, yend=mean_tumor_roi, color="ROI"), 
                position = position_nudge(x = 0.5, y = 0))+
  geom_point(aes(y=mean_tumor_roi) , color="red", size=1, alpha=0.6, 
             position = position_nudge(x = 0.5, y = 0)) + 
  theme_minimal() + 
  coord_flip()+
  scale_color_discrete(name="Samples from")+
  scale_color_manual(values = c("#FF9999", "skyblue")) +
  labs(x=paste(length(variations$ID), "Patients IDs"), y="% Tumor Cell (mean)", title="% Tumor Cell Present in TMAs vs ROIs per Patient",
       subtitle = "Each point represent the mean of up to 3 values for TMA, 6 values fro ROI")


variations %>% mutate(mean_tumor_roi = -1*mean_tumor_roi) %>% 
  ggplot(aes(x=suid.x)) +
  geom_segment( aes(x=suid.x, xend=suid.x, y=0, yend=mean_tumor_tma, color="TMA")) +
  geom_point(aes(y=mean_tumor_tma), color="blue", size=1, alpha=0.6) +
  geom_segment( aes(x=suid.x, xend=suid.x, y=0, yend=mean_tumor_roi, color="ROI")) +
  geom_point(aes(y=mean_tumor_roi) , color="red", size=1, alpha=0.6) +
  scale_y_continuous(breaks = c(-100, -50, 0, 50, 100),
                     labels = abs(c(-100, -50, 0, 50, 100))) +
  geom_hline(yintercept = 0) +
  theme_minimal() + 
  coord_flip()+
  scale_color_discrete(name="Samples from")+
  scale_color_manual(values = c("#FF9999", "skyblue")) +
  labs(x=paste(length(variations$ID), "Patients IDs"), y="% Tumor Cell (mean)", title="% Tumor Cell Present in TMAs vs ROIs per Patient",
       subtitle = "Each point represent the mean of up to 3 values for TMA, 6 values fro ROI")
```
The next plot is probably the most informative

```{r}
# TMA vs ROI vs I vs P
par(mar=c(5, 5, 20, 3.1)) # bottom left top right
ggplot(variations, aes(x=suid.x)) +
  geom_segment( aes(x=suid.x, xend=suid.x, y=0, yend=mean_tumor_tma, color="TMA")) +
  geom_point(aes(y=mean_tumor_tma), color="blue", size=1, alpha=0.6) +
  geom_segment( aes(x=suid.x, xend=suid.x, y=0, yend=mean_tumor_roi_i, color="ROIi"), 
                position = position_nudge(x = 0.25, y = 0)) +
  geom_point(aes(y=mean_tumor_roi_i) , color="limegreen", size=1, alpha=0.6, 
             position = position_nudge(x = 0.25, y = 0)) + 
  geom_segment( aes(x=suid.x, xend=suid.x, y=0, yend=mean_tumor_roi_p, color="ROIp"), 
                position = position_nudge(x = 0.5, y = 0)) +
  geom_point(aes(y=mean_tumor_roi_p) , color="purple", size=1, alpha=0.6, 
             position = position_nudge(x = 0.5, y = 0)) + 
  geom_segment( aes(x=suid.x, xend=suid.x, y=0, yend=mean_tumor_roi, color="ROI"), 
                position = position_nudge(x = 0.75, y = 0)) +
  geom_point(aes(y=mean_tumor_roi) , color="red", size=1, alpha=0.6, 
             position = position_nudge(x = 0.75, y = 0)) + 
  theme_minimal() + 
  coord_flip()+
  scale_x_discrete(expand=c(0.05, 0)) +
  scale_color_manual(name="Samples \nfrom", values = c("skyblue", "palegreen", "plum1", "#FF9999"), breaks=c("TMA","ROIi", "ROIp","ROI")) +
  labs(x=paste(length(variations$ID), "Patients IDs"), y="% Tumor Cell (mean)", title="% Tumor Cell Present in TMAs vs ROIs per Patient",
       subtitle = "Each point represent the mean of up to 3 values for TMA, 6 values fro ROI")
```

## Immune Markers


