---
title: "Immune marker time to interview adjusted bmi smoker diab"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: cerulean #darkly
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
h1.title {
  font-size: 25px;
}
.figure {
   margin-top: 25px;
   <!-- margin-bottom: 100px; -->
}

table {
    margin-top: 25px;
    <!-- margin-bottom: 100px !important; -->
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      # fig.width = 7, fig.height = 5, 
                      fig.align='center'#, fig.show='hold'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

<style>
div.blue { background-color:#0099CC; border-radius: 5px; padding: 20px; font-size: 38px}
</style>
<div class = "blue">

<span style="color: white;">adjusted bmi smoker diab</span>

</div>
<br>

```{r library, include=FALSE}
# library(drake)
library(tidyverse)
library(data.table)
# library(VennDiagram)
library(gtsummary)
library(survival)
library(survminer)
library(psych)
# library(corrplot)
# library(ggcorrplot)
library(mclust)
library(sensemakr)
```

```{r load}
# loadd(clinical_data, ROI_tumor ,ROI_stroma ,ROI_total,
#       cases_match)

# Remove these IDs from whole data because 2 are NAs in BMI and 2 are there matched
remove_id_bmi <- paste0(c("45142", "45809", "181810", "42204"), collapse = "|")

ROI_global <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_AACES_NCOCS/ROI_global.rds")
clinical_data <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_AACES_NCOCS/clinical_data.rds")

# Rewove patients not matched or lost match
ROI_global <- left_join(ROI_global, clinical_data, by="suid") %>%
  filter(!image_tag %in% c("Peres_P1_150163  3D_[44113,18531].tif", 
                           "Peres_P1_43004 A2_[45654,5840].tif",
                           "Peres_P1_43773 D2_[60849,15244].tif", 
                         "Peres_P1_AACES 130033_[37754,17929].tif",
                         "Peres_P1_AACES 130033_[38351,13944].tif"
                           )) %>% 
  select(suid, pair_id, everything()) %>% 
  drop_na(pair_id) %>% 
  group_by(pair_id) %>% 
  mutate(have_a_match = dense_rank(interaction(suid, pair_id))) %>% 
  group_by(pair_id) %>% 
  mutate(is_paired = max(have_a_match)) %>% 
  filter(is_paired == 2) %>% 
  select(pair_id, everything(), -c(is_paired, have_a_match)) %>% 
  ungroup()

# markers_match <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_AACES_NCOCS/markers_match.rds")
path <- fs::path("","Volumes","Peres_Research","Christelle Colin-Leitzinger", "IF_AACES_NCOCS", "Disparities manuscript", "Figures")

# Remove these IDs from peripheral ROI because 2 are NAs and 2 are there matched
remove_id <- paste0(c("110318", "43220", "42774", "46619"), collapse = "|")
```
<br>
<br>

***

<br>

```{r summarize mean}
# markers_ROIi <- ROI_global %>% 
#   filter(intratumoral_i_vs_peripheral_p_ == "Intratumoral") %>% 
#   group_by(suid) %>% 
#   summarize(
#     mean_tumor = mean(percent_tumor),
#     mean_stroma = mean(percent_stroma),
#     mean_total = mean(percent_total),
#     # variance_tumor = var(percent_tumor),
#     # variance_stroma = var(percent_stroma),
#     percent_CD3_tumor = mean(tumor_percent_cd3_opal_650_positive_cells),
#     percent_CD8_tumor = mean(tumor_percent_cd8_opal_570_positive_cells),
#     percent_CD3_CD8_tumor = mean(tumor_percent_cd3plus_cd8plus_positive_cells),
#     percent_FoxP3_tumor = mean(tumor_percent_foxp3_opal_540_positive_cells),
#     percent_CD3_FoxP3_tumor = mean(tumor_percent_cd3plus_foxp3plus_positive_cells),
#     percent_CD11b_tumor = mean(tumor_percent_cd11b_opal_620_positive_cells),
#     percent_CD15_tumor = mean(tumor_percent_cd15_opal_520_positive_cells),
#     percent_CD11b_CD15_tumor = mean(tumor_percent_cd11bplus_cd15plus_positive_cells),
#     percent_CD3_stroma = mean(stroma_percent_cd3_opal_650_positive_cells),
#     percent_CD8_stroma = mean(stroma_percent_cd8_opal_570_positive_cells),
#     percent_CD3_CD8_stroma = mean(stroma_percent_cd3plus_cd8plus_positive_cells),
#     percent_FoxP3_stroma = mean(stroma_percent_foxp3_opal_540_positive_cells),
#     percent_CD3_FoxP3_stroma = mean(stroma_percent_cd3plus_foxp3plus_positive_cells),
#     percent_CD11b_stroma = mean(stroma_percent_cd11b_opal_620_positive_cells),
#     percent_CD15_stroma = mean(stroma_percent_cd15_opal_520_positive_cells),
#     percent_CD11b_CD15_stroma = mean(stroma_percent_cd11bplus_cd15plus_positive_cells),
#     
#     percent_CD3_total = mean(percent_cd3_opal_650_positive_cells),
#     percent_CD8_total = mean(percent_cd8_opal_570_positive_cells),
#     percent_CD3_CD8_total = mean(percent_cd3plus_cd8plus_positive_cells),
#     percent_FoxP3_total = mean(percent_foxp3_opal_540_positive_cells),
#     percent_CD3_FoxP3_total = mean(percent_cd3plus_foxp3plus_positive_cells),
#     percent_CD11b_total = mean(percent_cd11b_opal_620_positive_cells),
#     percent_CD15_total = mean(percent_cd15_opal_520_positive_cells),
#     percent_CD11b_CD15_total = mean(percent_cd11bplus_cd15plus_positive_cells)
#   )
# markers_ROIi$tumor_variation <- markers_ROIi$mean_tumor - mean(ROI_global$percent_tumor)
# markers_ROIi$stroma_variation <- markers_ROIi$mean_stroma - mean(ROI_global$percent_stroma)
# markers_ROIi$total_variation <- markers_ROIi$mean_stroma - mean(ROI_global$percent_stroma)
# #
# markers_ROIp <- ROI_global %>% 
#   filter(!str_detect(suid, paste0(remove_id, collapse = "|")), 
#          intratumoral_i_vs_peripheral_p_ == "Peripheral") %>% 
#   group_by(suid) %>% 
#   summarize(
#     mean_tumor = mean(percent_tumor),
#     mean_stroma = mean(percent_stroma),
#     mean_total = mean(percent_total),
#     # variance_tumor = var(percent_tumor),
#     # variance_stroma = var(percent_stroma),
#     percent_CD3_tumor = mean(tumor_percent_cd3_opal_650_positive_cells),
#     percent_CD8_tumor = mean(tumor_percent_cd8_opal_570_positive_cells),
#     percent_CD3_CD8_tumor = mean(tumor_percent_cd3plus_cd8plus_positive_cells),
#     percent_FoxP3_tumor = mean(tumor_percent_foxp3_opal_540_positive_cells),
#     percent_CD3_FoxP3_tumor = mean(tumor_percent_cd3plus_foxp3plus_positive_cells),
#     percent_CD11b_tumor = mean(tumor_percent_cd11b_opal_620_positive_cells),
#     percent_CD15_tumor = mean(tumor_percent_cd15_opal_520_positive_cells),
#     percent_CD11b_CD15_tumor = mean(tumor_percent_cd11bplus_cd15plus_positive_cells),
#     percent_CD3_stroma = mean(stroma_percent_cd3_opal_650_positive_cells),
#     percent_CD8_stroma = mean(stroma_percent_cd8_opal_570_positive_cells),
#     percent_CD3_CD8_stroma = mean(stroma_percent_cd3plus_cd8plus_positive_cells),
#     percent_FoxP3_stroma = mean(stroma_percent_foxp3_opal_540_positive_cells),
#     percent_CD3_FoxP3_stroma = mean(stroma_percent_cd3plus_foxp3plus_positive_cells),
#     percent_CD11b_stroma = mean(stroma_percent_cd11b_opal_620_positive_cells),
#     percent_CD15_stroma = mean(stroma_percent_cd15_opal_520_positive_cells),
#     percent_CD11b_CD15_stroma = mean(stroma_percent_cd11bplus_cd15plus_positive_cells),
#     percent_CD3_total = mean(percent_cd3_opal_650_positive_cells),
#     percent_CD8_total = mean(percent_cd8_opal_570_positive_cells),
#     percent_CD3_CD8_total = mean(percent_cd3plus_cd8plus_positive_cells),
#     percent_FoxP3_total = mean(percent_foxp3_opal_540_positive_cells),
#     percent_CD3_FoxP3_total = mean(percent_cd3plus_foxp3plus_positive_cells),
#     percent_CD11b_total = mean(percent_cd11b_opal_620_positive_cells),
#     percent_CD15_total = mean(percent_cd15_opal_520_positive_cells),
#     percent_CD11b_CD15_total = mean(percent_cd11bplus_cd15plus_positive_cells)
#   )
# markers_ROIp$tumor_variation <- markers_ROIp$mean_tumor - mean(ROI_global$percent_tumor)
# markers_ROIp$stroma_variation <- markers_ROIp$mean_stroma - mean(ROI_global$percent_stroma)
# markers_ROIp$total_variation <- markers_ROIp$mean_total - mean(ROI_global$percent_total)
# 
# # Join Intratumoral and Peropheral ROI
# markers_ROI <- full_join(markers_ROIi, markers_ROIp,
#                          by= "suid", suffix= c(".i", ".p"))
# markers_ROI <- left_join(markers_ROI, clinical_data, by="suid")
# # clust_markers <- markers_ROI

markers_ROI <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_AACES_NCOCS/markers_ROI.rds")
```


```{r new median}
# markers_ROI <- markers_ROI %>% 
#   
#   mutate(CD3_tumor.i = case_when(
#     
#     percent_CD3_tumor.i <= 1      ~ "low",
#     percent_CD3_tumor.i > 1       ~ "high"
#   ), CD3_tumor.i = factor(CD3_tumor.i, levels = c("low","high"))) %>% 
#   mutate(CD3_CD8_tumor.i = case_when(
#     percent_CD3_CD8_tumor.i <= 1      ~ "low",
#     percent_CD3_CD8_tumor.i > 1       ~ "high"
#   ), CD3_CD8_tumor.i = factor(CD3_CD8_tumor.i, levels = c("low","high"))) %>% 
#   mutate(CD3_FoxP3_tumor.i = case_when(
#     percent_CD3_FoxP3_tumor.i <= 1      ~ "low",
#     percent_CD3_FoxP3_tumor.i > 1       ~ "high"
#   ), CD3_FoxP3_tumor.i = factor(CD3_FoxP3_tumor.i, levels = c("low","high"))) %>% 
#   mutate(CD11b_tumor.i = case_when(
#     percent_CD11b_tumor.i == 0      ~ "Absence",
#     percent_CD11b_tumor.i > 0       ~ "Presence"
#   )) %>% 
#   mutate(CD11b_CD15_tumor.i = case_when(
#     percent_CD11b_CD15_tumor.i == 0      ~ "Absence",
#     percent_CD11b_CD15_tumor.i > 0       ~ "Presence"
#   )) %>% 
#   
#   mutate(CD3_stroma.i = case_when(
#     percent_CD3_stroma.i <= 1      ~ "low",
#     percent_CD3_stroma.i > 1       ~ "high"
#   ), CD3_stroma.i = factor(CD3_stroma.i, levels = c("low","high"))) %>% 
#   mutate(CD3_CD8_stroma.i = case_when(
#     percent_CD3_CD8_stroma.i <= 1      ~ "low",
#     percent_CD3_CD8_stroma.i > 1       ~ "high"
#   ), CD3_CD8_stroma.i = factor(CD3_CD8_stroma.i, levels = c("low","high"))) %>% 
#   mutate(CD3_FoxP3_stroma.i = case_when(
#     percent_CD3_FoxP3_stroma.i <= 1      ~ "low",
#     percent_CD3_FoxP3_stroma.i > 1       ~ "high"
#   ), CD3_FoxP3_stroma.i = factor(CD3_FoxP3_stroma.i, levels = c("low","high"))) %>% 
#   mutate(CD11b_stroma.i = case_when(
#     percent_CD11b_stroma.i == 0      ~ "Absence",
#     percent_CD11b_stroma.i > 0       ~ "Presence"
#   )) %>%
#   mutate(CD11b_CD15_stroma.i = case_when(
#     percent_CD11b_CD15_stroma.i == 0      ~ "Absence",
#     percent_CD11b_CD15_stroma.i > 0       ~ "Presence"
#   )) %>% 
#   mutate(CD11b_stroma.i3 = case_when(
#     percent_CD11b_stroma.i <= 1      ~ "low",
#     percent_CD11b_stroma.i > 1       ~ "high"
#   ), CD11b_stroma.i3 = factor(CD11b_stroma.i3, levels = c("low","high"))) %>%
#   mutate(CD11b_CD15_stroma.i3 = case_when(
#     percent_CD11b_CD15_stroma.i <= 1      ~ "low",
#     percent_CD11b_CD15_stroma.i > 1       ~ "high"
#   ), CD11b_CD15_stroma.i3 = factor(CD11b_CD15_stroma.i3, levels = c("low","high"))) %>% 
#   mutate(CD3_total.i = case_when(
#     percent_CD3_total.i <= 1      ~ "low",
#     percent_CD3_total.i > 1       ~ "high"
#   ), CD3_total.i = factor(CD3_total.i, levels = c("low","high"))) %>% 
#   mutate(CD3_CD8_total.i = case_when(
#     percent_CD3_CD8_total.i <= 1      ~ "low",
#     percent_CD3_CD8_total.i > 1       ~ "high"
#   ), CD3_CD8_total.i = factor(CD3_CD8_total.i, levels = c("low","high"))) %>% 
#   mutate(CD3_FoxP3_total.i = case_when(
#     percent_CD3_FoxP3_total.i <= 1      ~ "low",
#     percent_CD3_FoxP3_total.i > 1       ~ "high"
#   ), CD3_FoxP3_total.i = factor(CD3_FoxP3_total.i, levels = c("low","high"))) %>% 
#   mutate(CD11b_total.i = case_when(
#     percent_CD11b_total.i == 0      ~ "Absence",
#     percent_CD11b_total.i > 0       ~ "Presence"
#   )) %>% 
#   mutate(CD11b_CD15_total.i = case_when(
#     percent_CD11b_CD15_total.i == 0      ~ "Absence",
#     percent_CD11b_CD15_total.i > 0       ~ "Presence"
#   )) %>% 
#   mutate(CD11b_total.i3 = case_when(
#     percent_CD11b_total.i <= 1      ~ "low",
#     percent_CD11b_total.i > 1       ~ "high"
#   ), CD11b_total.i3 = factor(CD11b_total.i3, levels = c("low","high"))) %>% 
#   mutate(CD11b_CD15_total.i3 = case_when(
#     percent_CD11b_CD15_total.i <= 1      ~ "low",
#     percent_CD11b_CD15_total.i > 1       ~ "high"
#   ), CD11b_CD15_total.i3 = factor(CD11b_CD15_total.i3, levels = c("low","high"))) %>% 
#   
#   
#   mutate(CD3_tumor.p = case_when(
#     percent_CD3_tumor.p <= 1      ~ "low",
#     percent_CD3_tumor.p > 1       ~ "high"
#   ), CD3_tumor.p = factor(CD3_tumor.p, levels = c("low","high"))) %>% 
#   mutate(CD3_CD8_tumor.p = case_when(
#     percent_CD3_CD8_tumor.p <= 1      ~ "low",
#     percent_CD3_CD8_tumor.p > 1       ~ "high"
#   ), CD3_CD8_tumor.p = factor(CD3_CD8_tumor.p, levels = c("low","high"))) %>% 
#   mutate(CD3_FoxP3_tumor.p = case_when(
#     percent_CD3_FoxP3_tumor.p <= 1      ~ "low",
#     percent_CD3_FoxP3_tumor.p > 1       ~ "high"
#   ), CD3_FoxP3_tumor.p = factor(CD3_FoxP3_tumor.p, levels = c("low","high"))) %>% 
#   mutate(CD11b_tumor.p = case_when(
#     percent_CD11b_tumor.p == 0      ~ "Absence",
#     percent_CD11b_tumor.p > 0       ~ "Presence"
#   )) %>% 
#   mutate(CD11b_CD15_tumor.p = case_when(
#     percent_CD11b_CD15_tumor.p == 0      ~ "Absence",
#     percent_CD11b_CD15_tumor.p > 0       ~ "Presence"
#   )) %>% 
#   mutate(CD11b_tumor.p3 = case_when(
#     percent_CD11b_tumor.p <= 1      ~ "low",
#     percent_CD11b_tumor.p > 1         ~ "high"
#   ), CD11b_tumor.p3 = factor(CD11b_tumor.p3, levels = c("low","high"))) %>% 
#   mutate(CD11b_CD15_tumor.p3 = case_when(
#     percent_CD11b_CD15_tumor.p <= 1      ~ "low",
#     percent_CD11b_CD15_tumor.p > 1       ~ "high"
#   ), CD11b_CD15_tumor.p3 = factor(CD11b_CD15_tumor.p3, levels = c("low","high"))) %>% 
#   mutate(CD3_stroma.p = case_when(
#     percent_CD3_stroma.p <= 1      ~ "low",
#     percent_CD3_stroma.p > 1       ~ "high"
#   ), CD3_stroma.p = factor(CD3_stroma.p, levels = c("low","high"))) %>% 
#   mutate(CD3_CD8_stroma.p = case_when(
#     percent_CD3_CD8_stroma.p <= 1      ~ "low",
#     percent_CD3_CD8_stroma.p > 1       ~ "high"
#   ), CD3_CD8_stroma.p = factor(CD3_CD8_stroma.p, levels = c("low","high"))) %>% 
#   mutate(CD3_FoxP3_stroma.p = case_when(
#     percent_CD3_FoxP3_stroma.p <= 1      ~ "low",
#     percent_CD3_FoxP3_stroma.p > 1       ~ "high"
#   ), CD3_FoxP3_stroma.p = factor(CD3_FoxP3_stroma.p, levels = c("low","high"))) %>% 
#   mutate(CD11b_stroma.p = case_when(
#     percent_CD11b_stroma.p == 0      ~ "Absence",
#     percent_CD11b_stroma.p > 0       ~ "Presence"
#   )) %>% 
#   mutate(CD11b_CD15_stroma.p = case_when(
#     percent_CD11b_CD15_stroma.p == 0      ~ "Absence",
#     percent_CD11b_CD15_stroma.p > 0       ~ "Presence"
#   )) %>% 
#     mutate(CD11b_stroma.p3 = case_when(
#     percent_CD11b_stroma.p <= 1      ~ "low",
#     percent_CD11b_stroma.p > 1       ~ "high"
#   ), CD11b_stroma.p3 = factor(CD11b_stroma.p3, levels = c("low","high"))) %>% 
#   mutate(CD11b_CD15_stroma.p3 = case_when(
#     percent_CD11b_CD15_stroma.p <= 1      ~ "low",
#     percent_CD11b_CD15_stroma.p > 1       ~ "high"
#   ), CD11b_CD15_stroma.p3 = factor(CD11b_CD15_stroma.p3, levels = c("low","high"))) %>% 
#   mutate(CD3_total.p = case_when(
#     percent_CD3_total.p <= 1      ~ "low",
#     percent_CD3_total.p > 1       ~ "high"
#   ), CD3_total.p = factor(CD3_total.p, levels = c("low","high"))) %>% 
#   mutate(CD3_CD8_total.p = case_when(
#     percent_CD3_CD8_total.p <= 1      ~ "low",
#     percent_CD3_CD8_total.p > 1       ~ "high"
#   ), CD3_CD8_total.p = factor(CD3_CD8_total.p, levels = c("low","high"))) %>% 
#   mutate(CD3_FoxP3_total.p = case_when(
#     percent_CD3_FoxP3_total.p <= 1      ~ "low",
#     percent_CD3_FoxP3_total.p > 1       ~ "high"
#   ), CD3_FoxP3_total.p = factor(CD3_FoxP3_total.p, levels = c("low","high"))) %>% 
#   mutate(CD11b_total.p = case_when(
#     percent_CD11b_total.p == 0      ~ "Absence",
#     percent_CD11b_total.p > 0       ~ "Presence"
#   )) %>% 
#   mutate(CD11b_CD15_total.p = case_when(
#     percent_CD11b_CD15_total.p == 0      ~ "Absence",
#     percent_CD11b_CD15_total.p > 0       ~ "Presence"
#   )) %>% 
#   mutate(CD11b_total.p3 = case_when(
#     percent_CD11b_total.p <= 1      ~ "low",
#     percent_CD11b_total.p > 1       ~ "high"
#   ), CD11b_total.p3 = factor(CD11b_total.p3, levels = c("low","high"))) %>% 
#   mutate(CD11b_CD15_total.p3 = case_when(
#     percent_CD11b_CD15_total.p <= 1      ~ "low",
#     percent_CD11b_CD15_total.p > 1       ~ "high"
#   ), CD11b_CD15_total.p3 = factor(CD11b_CD15_total.p3, levels = c("low","high"))) 

```


```{r immunoscore per patients mean}
# markers_ROI <- markers_ROI %>% 
#   mutate(percentile_score_CD3_i = ntile(percent_CD3_total.i, 100) ) %>% 
#   mutate(percentile_score_CD3_p = ntile(percent_CD3_total.p, 100) ) %>% 
#   mutate(percentile_score_CD8_i = ntile(percent_CD8_total.i, 100) ) %>% 
#   mutate(percentile_score_CD8_p = ntile(percent_CD8_total.p, 100) ) 
# 
# markers_ROI <- markers_ROI %>%
#   mutate(percentile_score_mean = rowMeans( markers_ROI[c("percentile_score_CD3_i", "percentile_score_CD3_p", 
#                                                     "percentile_score_CD8_i", "percentile_score_CD8_p")] ))
# markers_ROI <- markers_ROI %>%
#   mutate(immunoscore_patients = case_when(
#     percentile_score_mean <= 10        ~ 0,
#     percentile_score_mean <= 25        ~ 1,
#     percentile_score_mean <= 70        ~ 2,
#     percentile_score_mean <= 95        ~ 3,
#     percentile_score_mean > 95         ~ 4 
#   )) %>% 
#   mutate(immunoscore_patients = factor(immunoscore_patients)) %>% 
#   mutate(immunoscore_2018lancet_patients = case_when(
#     percentile_score_mean <= 25        ~ "Low",
#     percentile_score_mean <= 70        ~ "Intermediate",
#     percentile_score_mean > 70         ~ "High"
#     )) %>% 
#   mutate(immunoscore_2018lancet_patients = factor(immunoscore_2018lancet_patients, levels = c("Low", "Intermediate", "High"))) 
```


```{r removing double stain from single stain count}
# markers_ROI <- markers_ROI %>% 
#   mutate(percent_CD3_total.i = percent_CD3_total.i - percent_CD3_CD8_total.i - percent_CD3_FoxP3_total.i) %>% 
#   mutate(percent_CD8_total.i = percent_CD8_total.i - percent_CD3_CD8_total.i) %>% 
#   mutate(percent_FoxP3_total.i = percent_FoxP3_total.i - percent_CD3_FoxP3_total.i) %>% 
#   mutate(percent_CD11b_total.i = percent_CD11b_total.i - percent_CD11b_CD15_total.i) %>% 
#   mutate(percent_CD15_total.i = percent_CD15_total.i - percent_CD11b_CD15_total.i) %>% 
#   
#   mutate(percent_CD3_tumor.i = percent_CD3_tumor.i - percent_CD3_CD8_tumor.i - percent_CD3_FoxP3_tumor.i) %>% 
#   mutate(percent_CD8_tumor.i = percent_CD8_tumor.i - percent_CD3_CD8_tumor.i) %>% 
#   mutate(percent_FoxP3_tumor.i = percent_FoxP3_tumor.i - percent_CD3_FoxP3_tumor.i) %>% 
#   mutate(percent_CD11b_tumor.i = percent_CD11b_tumor.i - percent_CD11b_CD15_tumor.i) %>% 
#   mutate(percent_CD15_tumor.i = percent_CD15_tumor.i - percent_CD11b_CD15_tumor.i) %>% 
#   
#   mutate(percent_CD3_stroma.i = percent_CD3_stroma.i - percent_CD3_CD8_stroma.i - percent_CD3_FoxP3_stroma.i) %>% 
#   mutate(percent_CD8_stroma.i = percent_CD8_stroma.i - percent_CD3_CD8_stroma.i) %>% 
#   mutate(percent_FoxP3_stroma.i = percent_FoxP3_stroma.i - percent_CD3_FoxP3_stroma.i) %>% 
#   mutate(percent_CD11b_stroma.i = percent_CD11b_stroma.i - percent_CD11b_CD15_stroma.i) %>% 
#   mutate(percent_CD15_stroma.i = percent_CD15_stroma.i - percent_CD11b_CD15_stroma.i) %>% 
#   
#   mutate(percent_CD3_total.p = percent_CD3_total.p - percent_CD3_CD8_total.p - percent_CD3_FoxP3_total.p) %>% 
#   mutate(percent_CD8_total.p = percent_CD8_total.p - percent_CD3_CD8_total.p) %>% 
#   mutate(percent_FoxP3_total.p = percent_FoxP3_total.p - percent_CD3_FoxP3_total.p) %>% 
#   mutate(percent_CD11b_total.p = percent_CD11b_total.p - percent_CD11b_CD15_total.p) %>% 
#   mutate(percent_CD15_total.p = percent_CD15_total.p - percent_CD11b_CD15_total.p) %>% 
#   
#   mutate(percent_CD3_tumor.p = percent_CD3_tumor.p - percent_CD3_CD8_tumor.p - percent_CD3_FoxP3_tumor.p) %>% 
#   mutate(percent_CD8_tumor.p = percent_CD8_tumor.p - percent_CD3_CD8_tumor.p) %>% 
#   mutate(percent_FoxP3_tumor.p = percent_FoxP3_tumor.p - percent_CD3_FoxP3_tumor.p) %>% 
#   mutate(percent_CD11b_tumor.p = percent_CD11b_tumor.p - percent_CD11b_CD15_tumor.p) %>% 
#   mutate(percent_CD15_tumor.p = percent_CD15_tumor.p - percent_CD11b_CD15_tumor.p) %>% 
#   
#   mutate(percent_CD3_stroma.p = percent_CD3_stroma.p - percent_CD3_CD8_stroma.p - percent_CD3_FoxP3_stroma.p) %>% 
#   mutate(percent_CD8_stroma.p = percent_CD8_stroma.p - percent_CD3_CD8_stroma.p) %>% 
#   mutate(percent_FoxP3_stroma.p = percent_FoxP3_stroma.p - percent_CD3_FoxP3_stroma.p) %>% 
#   mutate(percent_CD11b_stroma.p = percent_CD11b_stroma.p - percent_CD11b_CD15_stroma.p) %>% 
#   mutate(percent_CD15_stroma.p = percent_CD15_stroma.p - percent_CD11b_CD15_stroma.p)
```
<br>

**All clustering and variables creation are done without removing the 4 patients no BMI**

```{r clustering}
# set.seed(1234)
# 
# ### Cluster for stroma/tumor in the intratumoral/peritumoral ROIs 
# clust_markers <- markers_ROI %>% 
#   filter(!is.na(markers_ROI$percent_CD3_CD8_tumor.i) & !is.na(markers_ROI$percent_CD3_CD8_tumor.p)) %>% 
#   select(suid, c("percent_CD3_tumor.i", "percent_CD3_CD8_tumor.i", "percent_CD3_FoxP3_tumor.i", "percent_CD11b_tumor.i", "percent_CD11b_CD15_tumor.i",
#                  "percent_CD3_stroma.i", "percent_CD3_CD8_stroma.i", "percent_CD3_FoxP3_stroma.i", "percent_CD11b_stroma.i", "percent_CD11b_CD15_stroma.i",
#                  "percent_CD3_tumor.p", "percent_CD3_CD8_tumor.p", "percent_CD3_FoxP3_tumor.p", "percent_CD11b_tumor.p", "percent_CD11b_CD15_tumor.p",
#                  "percent_CD3_stroma.p", "percent_CD3_CD8_stroma.p", "percent_CD3_FoxP3_stroma.p", "percent_CD11b_stroma.p", "percent_CD11b_CD15_stroma.p"
#                  ))
# 
# clust <- Mclust(scale(clust_markers[,c(2:ncol(clust_markers))]))
# 
# clust_markers$clusters_all_IandP <- clust$classification
# # clust_markers$clusters_all_IandP <- factor(clust_markers$clusters_all_IandP,
# #                                            levels = c(1, 2, 3),
# #                                            labels = c("mid", "high", "low"))
# clust_markers$clusters_all_IandP <- factor(clust_markers$clusters_all_IandP,
#                                            levels = c(1, 2, 3, 4, 5),
#                                            labels = c("mid", "high", "mid-high", "mid-low", "low"))
# clust_markers <- clust_markers %>% mutate(clusters_all_IandP = factor(clusters_all_IandP, levels = c("low", "mid-low", "mid", "mid-high", "high")))
# # clust_markers <- clust_markers %>% mutate(clusters_all_IandP = factor(clusters_all_IandP, levels = c("low", "mid", "high")))
# 
# # clust_markers %>% 
# # tidyr::gather(key = "markers_cat", value = "value",
# #               c("percent_CD3_tumor.i":"percent_CD11b_CD15_stroma.i")) %>% 
# #   select(suid, clusters_all_IandP, markers_cat, value) %>% 
# #   ggplot(aes(x=suid, y=value, group=markers_cat,  color=markers_cat))+
# #   geom_boxplot()+
# #   facet_grid(.~ clusters_all_IandP)
# # clust_markers %>% 
# # tidyr::gather(key = "markers_cat", value = "value",
# #               c("percent_CD3_tumor.p":"percent_CD11b_CD15_stroma.p")) %>% 
# #   select(suid, clusters_all_IandP, markers_cat, value) %>% 
# #   ggplot(aes(x=suid, y=value, group=markers_cat,  color=markers_cat))+
# #   geom_boxplot()+
# #   facet_grid(.~ clusters_all_IandP)
# markers_ROI <- full_join(markers_ROI, clust_markers %>% select(suid, clusters_all_IandP), by = "suid")
# 
# 
# ### Cluster for tumor intratumoral all double positive "percent_CD3_CD8_tumor.i", "percent_CD3_FoxP3_tumor.i", "percent_CD11b_CD15_tumor.i"
# clust_markers <- markers_ROI %>% filter(!is.na(markers_ROI$percent_CD3_CD8_tumor.i ))
# clust <- 
#   Mclust(clust_markers[,c("percent_CD3_CD8_tumor.i", "percent_CD3_FoxP3_tumor.i", "percent_CD11b_CD15_tumor.i")])
# # summary(clust)
# clust_markers$dbl_pos <- clust$classification
# clust_markers$dbl_pos <- factor(clust_markers$dbl_pos,
#                                            levels = c(1, 2, 3),
#                                            labels = c("low", "high", "mid"))
# clust_markers <- clust_markers %>% mutate(dbl_pos = factor(dbl_pos, levels = c("low", "mid", "high")))
# 
# ### Cluster for tumor intratumoral CD3-CD8
# clust <- Mclust(clust_markers$percent_CD3_CD8_tumor.i)
# # summary(clust)
# clust_markers$clusters_CD3CD8 <- clust$classification
# clust_markers$clusters_CD3CD8 <- factor(clust_markers$clusters_CD3CD8,
#                                            levels = c(1, 2, 3, 4, 5),
#                                            labels = c("low", "mid-low", "mid", "mid-high", "high"))
# 
# ### Cluster for tumor intratumoral CD3-FoxP3
# clust <- Mclust(clust_markers$percent_CD3_FoxP3_tumor.i)
# # summary(clust)
# clust_markers$clusters_CD3FoxP3 <- clust$classification
# clust_markers$clusters_CD3FoxP3 <- factor(clust_markers$clusters_CD3FoxP3,
#                                            levels = c(1, 2, 3),
#                                            labels = c("low", "mid", "high"))
# 
# ### Cluster for tumor intratumoral FoxP3 because it can be expressed by tumor cell
# clust <- Mclust(clust_markers$percent_FoxP3_tumor.i)
# # summary(clust)
# clust_markers$clusters_FoxP3_ <- clust$classification
# clust_markers$clusters_FoxP3_ <- factor(clust_markers$clusters_FoxP3_,
#                                            levels = c(1, 2, 3, 4),
#                                            labels = c("low", "mid", "mid-high", "high"))
# 
# ### Cluster for tumor intratumoral CD11b/CD15 
# clust <- Mclust(clust_markers$percent_CD11b_CD15_tumor.i)
# # summary(clust)
# clust_markers$clusters_CD11bCD15 <- clust$classification
# clust_markers$clusters_CD11bCD15 <- factor(clust_markers$clusters_CD11bCD15,
#                                            levels = c(1, 7, 8),
#                                            labels = c("low", "high", "mid"))
# clust_markers <- clust_markers %>% mutate(clusters_CD11bCD15 = factor(clusters_CD11bCD15, levels = c("low", "mid", "high")))
# 
# markers_ROI <- full_join(markers_ROI, clust_markers %>% select(suid, dbl_pos, clusters_CD3CD8, clusters_CD3FoxP3, clusters_FoxP3_, clusters_CD11bCD15), by = "suid")

```
<br>

# Table 3. Adjusted hazard ratios and 95% confidence intervals
## 1% group- absensece /presece
<br>

**Remove the 4 patients no BMI for analysis + adjust for BMI_recent_grp + diab + smoker**

## Whole population
```{r}
markers_ROI_o <- markers_ROI %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  rename(CD3 = CD3_total.i, CD3_CD8 = CD3_CD8_total.i,
         CD3_FoxP3 = CD3_FoxP3_total.i, 
         CD11b = CD11b_total.i, CD11b_CD15 = CD11b_CD15_total.i)
  
tbl1 <- coxph(Surv(time = markers_ROI_o$timeint_fu, 
                   event = markers_ROI_o$surv_vital) ~ CD3 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_o)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROI_o$timeint_fu, 
                   event = markers_ROI_o$surv_vital) ~ CD3_CD8 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- coxph(Surv(time = markers_ROI_o$timeint_fu, 
                   event = markers_ROI_o$surv_vital) ~ CD3_FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROI_o$timeint_fu, 
                   event = markers_ROI_o$surv_vital) ~ CD11b + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROI_o$timeint_fu, 
                   event = markers_ROI_o$surv_vital) ~ CD11b_CD15 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl10 <- tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5))

markers_ROI_t <- markers_ROI %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  rename(CD3 = CD3_tumor.i, CD3_CD8 = CD3_CD8_tumor.i,
         CD3_FoxP3 = CD3_FoxP3_tumor.i, 
         CD11b = CD11b_tumor.i, CD11b_CD15 = CD11b_CD15_tumor.i)
  
tbl1 <- coxph(Surv(time = markers_ROI_t$timeint_fu, 
                   event = markers_ROI_t$surv_vital) ~ CD3 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_t)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROI_t$timeint_fu, 
                   event = markers_ROI_t$surv_vital) ~ CD3_CD8 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- coxph(Surv(time = markers_ROI_t$timeint_fu, 
                   event = markers_ROI_t$surv_vital) ~ CD3_FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROI_t$timeint_fu, 
                   event = markers_ROI_t$surv_vital) ~ CD11b + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROI_t$timeint_fu, 
                   event = markers_ROI_t$surv_vital) ~ CD11b_CD15 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl11 <- tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5))

markers_ROI_s <- markers_ROI %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  rename(CD3 = CD3_stroma.i, CD3_CD8 = CD3_CD8_stroma.i,
         CD3_FoxP3 = CD3_FoxP3_stroma.i, 
         CD11b = CD11b_stroma.i, CD11b_CD15 = CD11b_CD15_stroma.i)

tbl1 <- coxph(Surv(time = markers_ROI_s$timeint_fu, 
                   event = markers_ROI_s$surv_vital) ~ CD3 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROI_s$timeint_fu, 
                   event = markers_ROI_s$surv_vital) ~ CD3_CD8 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- coxph(Surv(time = markers_ROI_s$timeint_fu, 
                   event = markers_ROI_s$surv_vital) ~ CD3_FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROI_s$timeint_fu, 
                   event = markers_ROI_s$surv_vital) ~ CD11b + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROI_s$timeint_fu, 
                   event = markers_ROI_s$surv_vital) ~ CD11b_CD15 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl12 <- tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5))
# tbl13 <- tbl_merge(list(tbl10, tbl11, tbl12), tab_spanner = c("**Overall**", "**Tumor**", "**Stroma**"))



markers_ROI_o <- markers_ROI %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  rename(CD3 = CD3_total.p, CD3_CD8 = CD3_CD8_total.p,
         CD3_FoxP3 = CD3_FoxP3_total.p, 
         CD11b = CD11b_total.p, CD11b_CD15 = CD11b_CD15_total.p)
  
tbl1 <- coxph(Surv(time = markers_ROI_o$timeint_fu, 
                   event = markers_ROI_o$surv_vital) ~ CD3 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_o)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROI_o$timeint_fu, 
                   event = markers_ROI_o$surv_vital) ~ CD3_CD8 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- coxph(Surv(time = markers_ROI_o$timeint_fu, 
                   event = markers_ROI_o$surv_vital) ~ CD3_FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROI_o$timeint_fu, 
                   event = markers_ROI_o$surv_vital) ~ CD11b + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROI_o$timeint_fu, 
                   event = markers_ROI_o$surv_vital) ~ CD11b_CD15 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl13 <- tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5))

markers_ROI_t <- markers_ROI %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  rename(CD3 = CD3_tumor.p, CD3_CD8 = CD3_CD8_tumor.p,
         CD3_FoxP3 = CD3_FoxP3_tumor.p, 
         CD11b = CD11b_tumor.p, CD11b_CD15 = CD11b_CD15_tumor.p)
  
tbl1 <- coxph(Surv(time = markers_ROI_t$timeint_fu, 
                   event = markers_ROI_t$surv_vital) ~ CD3 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_t)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROI_t$timeint_fu, 
                   event = markers_ROI_t$surv_vital) ~ CD3_CD8 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- coxph(Surv(time = markers_ROI_t$timeint_fu, 
                   event = markers_ROI_t$surv_vital) ~ CD3_FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROI_t$timeint_fu, 
                   event = markers_ROI_t$surv_vital) ~ CD11b + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROI_t$timeint_fu, 
                   event = markers_ROI_t$surv_vital) ~ CD11b_CD15 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl14 <- tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5))

markers_ROI_s <- markers_ROI %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  rename(CD3 = CD3_stroma.p, CD3_CD8 = CD3_CD8_stroma.p,
         CD3_FoxP3 = CD3_FoxP3_stroma.p, 
         CD11b = CD11b_stroma.p, CD11b_CD15 = CD11b_CD15_stroma.p)

tbl1 <- coxph(Surv(time = markers_ROI_s$timeint_fu, 
                   event = markers_ROI_s$surv_vital) ~ CD3 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROI_s$timeint_fu, 
                   event = markers_ROI_s$surv_vital) ~ CD3_CD8 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- coxph(Surv(time = markers_ROI_s$timeint_fu, 
                   event = markers_ROI_s$surv_vital) ~ CD3_FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROI_s$timeint_fu, 
                   event = markers_ROI_s$surv_vital) ~ CD11b + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROI_s$timeint_fu, 
                   event = markers_ROI_s$surv_vital) ~ CD11b_CD15 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl15 <- tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5))

# tbl14 <- tbl_merge(list(tbl13, tbl14, tbl15), tab_spanner = c("**Overall**", "**Tumor**", "**Stroma**"))
```

## Overall
```{r}
tbl16 <- tbl_stack(list(tbl10, tbl13), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl16
# gt::gtsave(tbl16, paste0(path, "/Table 3. Adjusted hazard ratios and 95% confidence intervals in Overall ROIs.pdf"))
```

## Tumor
```{r}
tbl17 <- tbl_stack(list(tbl11, tbl14), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl17
# gt::gtsave(tbl17, paste0(path, "/Table 3. Adjusted hazard ratios and 95% confidence intervals in Tumor ROIs.pdf"))
```

## Stroma
```{r}
tbl18 <- tbl_stack(list(tbl12, tbl15), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl18
# gt::gtsave(tbl18, paste0(path, "/Table 3. Adjusted hazard ratios and 95% confidence intervals in Stroma ROIs.pdf"))
```


# Table 3b. Adjusted hazard ratios and 95% confidence intervals (**include each 3 values and use the cluster option**)

```{r create group per sampleon ROI_global}
ROI_global <- ROI_global %>% 
  
  mutate(CD3_tumor = case_when(
    
    tumor_percent_cd3_opal_650_positive_cells <= 1      ~ "low",
    tumor_percent_cd3_opal_650_positive_cells > 1       ~ "high"
  ), CD3_tumor = factor(CD3_tumor, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_tumor = case_when(
    tumor_percent_cd3plus_cd8plus_positive_cells <= 1      ~ "low",
    tumor_percent_cd3plus_cd8plus_positive_cells > 1       ~ "high"
  ), CD3_CD8_tumor = factor(CD3_CD8_tumor, levels = c("low","high"))) %>% 
  mutate(CD3_FoxP3_tumor = case_when(
    tumor_percent_cd3plus_foxp3plus_positive_cells <= 1      ~ "low",
    tumor_percent_cd3plus_foxp3plus_positive_cells > 1       ~ "high"
  ), CD3_FoxP3_tumor = factor(CD3_FoxP3_tumor, levels = c("low","high"))) %>% 
  mutate(CD11b_tumor = case_when(
    tumor_percent_cd11b_opal_620_positive_cells == 0      ~ "Absence",
    tumor_percent_cd11b_opal_620_positive_cells > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_CD15_tumor = case_when(
    tumor_percent_cd15_opal_520_positive_cells == 0      ~ "Absence",
    tumor_percent_cd15_opal_520_positive_cells > 0       ~ "Presence"
  )) %>% 
  
  mutate(CD3_stroma = case_when(
    stroma_percent_cd3_opal_650_positive_cells <= 1      ~ "low",
    stroma_percent_cd3_opal_650_positive_cells > 1       ~ "high"
  ), CD3_stroma = factor(CD3_stroma, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_stroma = case_when(
    stroma_percent_cd3plus_cd8plus_positive_cells <= 1      ~ "low",
    stroma_percent_cd3plus_cd8plus_positive_cells > 1       ~ "high"
  ), CD3_CD8_stroma = factor(CD3_CD8_stroma, levels = c("low","high"))) %>% 
  mutate(CD3_FoxP3_stroma = case_when(
    stroma_percent_cd3plus_foxp3plus_positive_cells <= 1      ~ "low",
    stroma_percent_cd3plus_foxp3plus_positive_cells > 1       ~ "high"
  ), CD3_FoxP3_stroma = factor(CD3_FoxP3_stroma, levels = c("low","high"))) %>% 
  mutate(CD11b_stroma = case_when(
    stroma_percent_cd11b_opal_620_positive_cells == 0      ~ "Absence",
    stroma_percent_cd11b_opal_620_positive_cells > 0       ~ "Presence"
  )) %>%
  mutate(CD11b_CD15_stroma = case_when(
    stroma_percent_cd11bplus_cd15plus_positive_cells == 0      ~ "Absence",
    stroma_percent_cd11bplus_cd15plus_positive_cells > 0       ~ "Presence"
  )) %>% 
  
  mutate(CD3_total = case_when(
    percent_cd3_opal_650_positive_cells <= 1      ~ "low",
    percent_cd3_opal_650_positive_cells > 1       ~ "high"
  ), CD3_total = factor(CD3_total, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_total = case_when(
    percent_cd3plus_cd8plus_positive_cells <= 1      ~ "low",
    percent_cd3plus_cd8plus_positive_cells > 1       ~ "high"
  ), CD3_CD8_total = factor(CD3_CD8_total, levels = c("low","high"))) %>% 
  mutate(CD3_FoxP3_total = case_when(
    percent_cd3plus_foxp3plus_positive_cells <= 1      ~ "low",
    percent_cd3plus_foxp3plus_positive_cells > 1       ~ "high"
  ), CD3_FoxP3_total = factor(CD3_FoxP3_total, levels = c("low","high"))) %>% 
  mutate(CD11b_total = case_when(
    percent_cd11b_opal_620_positive_cells == 0      ~ "Absence",
    percent_cd11b_opal_620_positive_cells > 0       ~ "Presence"
  )) %>% 
  mutate(CD11b_CD15_total = case_when(
    percent_cd11bplus_cd15plus_positive_cells == 0      ~ "Absence",
    percent_cd11bplus_cd15plus_positive_cells > 0       ~ "Presence"
  )) 

```

**Removed 4 patients no BMI**

```{r Table % cluster option}
markers_ROIclust_o <- ROI_global %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  filter(intratumoral_i_vs_peripheral_p_ == "Intratumoral") %>% 
  rename(CD3 = CD3_total, CD3_CD8 = CD3_CD8_total,
         CD3_FoxP3 = CD3_FoxP3_total, 
         CD11b = CD11b_total, CD11b_CD15 = CD11b_CD15_total)
  
tbl1 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD3 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD3_CD8 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl3 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu,
#                    event = markers_ROIclust_o$surv_vital) ~ CD3_FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
#   tbl_regression(exponentiate = TRUE,
#                  include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")


# newdata <- survSplit(Surv(time = markers_ROIclust_o$timeint_fu, 
#                    event = markers_ROIclust_o$surv_vital) ~ CD3_FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, id = "suid", data = markers_ROIclust_o, cut=1700, episode='tgroup')
# 
# coxph(Surv(newdata$tstart, newdata$tstop,
#                    event = newdata$event) ~ CD3_FoxP3 + CD3_FoxP3:tstop + strata(stage) + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, 
#               data =  newdata)
# 
# coxph(Surv(newdata$tstart, newdata$tstop,
#                    event = newdata$event) ~ CD3_FoxP3:strata(tgroup) + strata(stage) + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, 
#               data =  newdata)
# 
# survcheck(Surv(newdata$tstart, newdata$tstop,
#                    event = newdata$event) ~ CD3_FoxP3:strata(tgroup) + strata(stage) + refage + race + BMI_recent_grp + diab + smoker, id = suid, 
#               data =  newdata)
# 
# survfit(Surv(newdata$tstart, newdata$tstop,
#                    event = newdata$event) ~ CD3_FoxP3 + strata(tgroup) + strata(stage) + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, influence = TRUE,
#               data =  newdata)



# tbl3 <-
#   coxph(Surv(time = newdata$tstart, newdata$tstop,
#                    event = newdata$event) ~ CD3_FoxP3 + CD3_FoxP3:tstop + strata(stage) + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, 
#               data =  newdata) %>% 
#   tbl_regression(exponentiate = TRUE,
#                  include = 'CD3_FoxP3:tstop') %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl4 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD11b + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD11b_CD15 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl10 <- tbl_stack(list(tbl1, tbl2, tbl4, tbl5))

markers_ROIclust_t <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
    filter(intratumoral_i_vs_peripheral_p_ == "Intratumoral") %>% 
  rename(CD3 = CD3_tumor, CD3_CD8 = CD3_CD8_tumor,
         CD3_FoxP3 = CD3_FoxP3_tumor, 
         CD11b = CD11b_tumor, CD11b_CD15 = CD11b_CD15_tumor)
  
tbl1 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD3 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD3_CD8 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl3 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
#                    event = markers_ROIclust_t$surv_vital) ~ CD3_FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
#   tbl_regression(exponentiate = TRUE,
#                  include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# newdata <- survSplit(Surv(time = markers_ROIclust_t$timeint_fu, 
#                    event = markers_ROIclust_t$surv_vital) ~ CD3_FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, id = "suid", data = markers_ROIclust_t, cut=1700, episode='tgroup')   
# 
# tbl3 <- coxph(Surv(time = newdata$tstart, newdata$tstop,
#                    event = newdata$event) ~ CD3_FoxP3:strata(tgroup) + strata(stage) + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, 
#               data =  newdata) %>% 
#   tbl_regression(exponentiate = TRUE,
#                  include = 'CD3_FoxP3:strata(tgroup)') %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD11b + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD11b_CD15 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl11 <- tbl_stack(list(tbl1, tbl2, tbl4, tbl5))

markers_ROIclust_s <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
    filter(intratumoral_i_vs_peripheral_p_ == "Intratumoral") %>% 
  rename(CD3 = CD3_stroma, CD3_CD8 = CD3_CD8_stroma,
         CD3_FoxP3 = CD3_FoxP3_stroma, 
         CD11b = CD11b_stroma, CD11b_CD15 = CD11b_CD15_stroma)

tbl1 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD3 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD3_CD8 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl3 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
#                    event = markers_ROIclust_s$surv_vital) ~ CD3_FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
#   tbl_regression(exponentiate = TRUE,
#                  include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# newdata <- survSplit(Surv(time = markers_ROIclust_s$timeint_fu, 
#                    event = markers_ROIclust_s$surv_vital) ~ CD3_FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, id = "suid", data = markers_ROIclust_s, cut=1700, episode='tgroup')   
# 
# tbl3 <- coxph(Surv(time = newdata$tstart, newdata$tstop,
#                    event = newdata$event) ~ CD3_FoxP3:strata(tgroup) + strata(stage) + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, 
#               data =  newdata) %>% 
#   tbl_regression(exponentiate = TRUE,
#                  include = 'CD3_FoxP3:strata(tgroup)') %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD11b + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD11b_CD15 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl12 <- tbl_stack(list(tbl1, tbl2, tbl4, tbl5))
# tbl13 <- tbl_merge(list(tbl10, tbl11, tbl12), tab_spanner = c("**Overall**", "**Tumor**", "**Stroma**"))



markers_ROIclust_o <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  filter(!str_detect(suid, paste0(remove_id, collapse = "|")), 
         intratumoral_i_vs_peripheral_p_ == "Peripheral") %>% 
  rename(CD3 = CD3_total, CD3_CD8 = CD3_CD8_total,
         CD3_FoxP3 = CD3_FoxP3_total, 
         CD11b = CD11b_total, CD11b_CD15 = CD11b_CD15_total)
  
tbl1 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD3 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD3_CD8 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl3 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
#                    event = markers_ROIclust_o$surv_vital) ~ CD3_FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
#   tbl_regression(exponentiate = TRUE,
#                  include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# newdata <- survSplit(Surv(time = markers_ROIclust_o$timeint_fu, 
#                    event = markers_ROIclust_o$surv_vital) ~ CD3_FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, id = "suid", data = markers_ROIclust_o, cut=1700, episode='tgroup')   
# 
# tbl3 <- coxph(Surv(time = newdata$tstart, newdata$tstop,
#                    event = newdata$event) ~ CD3_FoxP3:strata(tgroup) + strata(stage) + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, 
#               data =  newdata) %>% 
#   tbl_regression(exponentiate = TRUE,
#                  include = 'CD3_FoxP3:strata(tgroup)') %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD11b + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD11b_CD15 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl13 <- tbl_stack(list(tbl1, tbl2, tbl4, tbl5))

markers_ROIclust_t <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  filter(!str_detect(suid, paste0(remove_id, collapse = "|")), 
         intratumoral_i_vs_peripheral_p_ == "Peripheral") %>%
  rename(CD3 = CD3_tumor, CD3_CD8 = CD3_CD8_tumor,
         CD3_FoxP3 = CD3_FoxP3_tumor, 
         CD11b = CD11b_tumor, CD11b_CD15 = CD11b_CD15_tumor)
  
tbl1 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD3 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD3_CD8 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl3 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
#                    event = markers_ROIclust_t$surv_vital) ~ CD3_FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
#   tbl_regression(exponentiate = TRUE,
#                  include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# newdata <- survSplit(Surv(time = markers_ROIclust_t$timeint_fu, 
#                    event = markers_ROIclust_t$surv_vital) ~ CD3_FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, id = "suid", data = markers_ROIclust_t, cut=1700, episode='tgroup')   
# 
# tbl3 <- coxph(Surv(time = newdata$tstart, newdata$tstop,
#                    event = newdata$event) ~ CD3_FoxP3:strata(tgroup) + strata(stage) + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, 
#               data =  newdata) %>% 
#   tbl_regression(exponentiate = TRUE,
#                  include = 'CD3_FoxP3:strata(tgroup)') %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD11b + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD11b_CD15 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl14 <- tbl_stack(list(tbl1, tbl2, tbl4, tbl5))

markers_ROIclust_s <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  filter(!str_detect(suid, paste0(remove_id, collapse = "|")), 
         intratumoral_i_vs_peripheral_p_ == "Peripheral") %>% 
  rename(CD3 = CD3_stroma, CD3_CD8 = CD3_CD8_stroma,
         CD3_FoxP3 = CD3_FoxP3_stroma, 
         CD11b = CD11b_stroma, CD11b_CD15 = CD11b_CD15_stroma)

tbl1 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD3 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD3_CD8 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl3 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
#                    event = markers_ROIclust_s$surv_vital) ~ CD3_FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
#   tbl_regression(exponentiate = TRUE,
#                  include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# newdata <- survSplit(Surv(time = markers_ROIclust_s$timeint_fu, 
#                    event = markers_ROIclust_s$surv_vital) ~ CD3_FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, id = "suid", data = markers_ROIclust_s, cut=1700, episode='tgroup')   
# 
# tbl3 <- coxph(Surv(time = newdata$tstart, newdata$tstop,
#                    event = newdata$event) ~ CD3_FoxP3:strata(tgroup) + strata(stage) + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, 
#               data =  newdata) %>% 
#   tbl_regression(exponentiate = TRUE,
#                  include = 'CD3_FoxP3:strata(tgroup)') %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD11b + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD11b_CD15 + stage + refage + race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl15 <- tbl_stack(list(tbl1, tbl2, tbl4, tbl5))
# tbl14 <- tbl_merge(list(tbl13, tbl14, tbl15), tab_spanner = c("**Overall**", "**Tumor**", "**Stroma**"))
```

## Overall
```{r}
tbl16 <- tbl_stack(list(tbl10, tbl13), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl16
# gt::gtsave(tbl16, paste0(path, "/Table 3. Adjusted hazard ratios and 95% confidence intervals in Overall ROIs cluster option.pdf"))
```

## Tumor
```{r}
tbl17 <- tbl_stack(list(tbl11, tbl14), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl17
# gt::gtsave(tbl17, paste0(path, "/Table 3. Adjusted hazard ratios and 95% confidence intervals in Tumor ROIs cluster option.pdf"))
```

## Stroma
```{r}
tbl18 <- tbl_stack(list(tbl12, tbl15), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl18
# gt::gtsave(tbl18, paste0(path, "/Table 3. Adjusted hazard ratios and 95% confidence intervals in Stroma ROIs cluster option.pdf"))
```

## In White (I can bind W/B later if you want them side by side)
```{r Table % cluster option white}
markers_ROIclust_o <- ROI_global %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  filter(intratumoral_i_vs_peripheral_p_ == "Intratumoral" & race == "White") %>% 
  rename(CD3 = CD3_total, CD3_CD8 = CD3_CD8_total,
         CD3_FoxP3 = CD3_FoxP3_total, 
         CD11b = CD11b_total, CD11b_CD15 = CD11b_CD15_total)
  
tbl1 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD3_CD8 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl3 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
#                    event = markers_ROIclust_o$surv_vital) ~ CD3_FoxP3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
#   tbl_regression(exponentiate = TRUE,
#                  include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD11b + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD11b_CD15 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl10 <- tbl_stack(list(tbl1, tbl2, tbl4, tbl5))

markers_ROIclust_t <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
    filter(intratumoral_i_vs_peripheral_p_ == "Intratumoral" & race == "White") %>% 
  rename(CD3 = CD3_tumor, CD3_CD8 = CD3_CD8_tumor,
         CD3_FoxP3 = CD3_FoxP3_tumor, 
         CD11b = CD11b_tumor, CD11b_CD15 = CD11b_CD15_tumor)
  
tbl1 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD3_CD8 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl3 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
#                    event = markers_ROIclust_t$surv_vital) ~ CD3_FoxP3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
#   tbl_regression(exponentiate = TRUE,
#                  include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD11b + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD11b_CD15 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl11 <- tbl_stack(list(tbl1, tbl2, tbl4, tbl5))

markers_ROIclust_s <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
    filter(intratumoral_i_vs_peripheral_p_ == "Intratumoral" & race == "White") %>% 
  rename(CD3 = CD3_stroma, CD3_CD8 = CD3_CD8_stroma,
         CD3_FoxP3 = CD3_FoxP3_stroma, 
         CD11b = CD11b_stroma, CD11b_CD15 = CD11b_CD15_stroma)

tbl1 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD3_CD8 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl3 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
#                    event = markers_ROIclust_s$surv_vital) ~ CD3_FoxP3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
#   tbl_regression(exponentiate = TRUE,
#                  include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD11b + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD11b_CD15 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl12 <- tbl_stack(list(tbl1, tbl2, tbl4, tbl5))
# tbl13 <- tbl_merge(list(tbl10, tbl11, tbl12), tab_spanner = c("**Overall**", "**Tumor**", "**Stroma**"))



markers_ROIclust_o <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  filter(!str_detect(suid, paste0(remove_id, collapse = "|")), 
         intratumoral_i_vs_peripheral_p_ == "Peripheral", race == "White") %>% 
  rename(CD3 = CD3_total, CD3_CD8 = CD3_CD8_total,
         CD3_FoxP3 = CD3_FoxP3_total, 
         CD11b = CD11b_total, CD11b_CD15 = CD11b_CD15_total)
  
tbl1 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD3_CD8 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl3 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
#                    event = markers_ROIclust_o$surv_vital) ~ CD3_FoxP3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
#   tbl_regression(exponentiate = TRUE,
#                  include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD11b + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD11b_CD15 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl13 <- tbl_stack(list(tbl1, tbl2, tbl4, tbl5))

markers_ROIclust_t <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  filter(!str_detect(suid, paste0(remove_id, collapse = "|")), 
         intratumoral_i_vs_peripheral_p_ == "Peripheral", race == "White") %>% 
  rename(CD3 = CD3_tumor, CD3_CD8 = CD3_CD8_tumor,
         CD3_FoxP3 = CD3_FoxP3_tumor, 
         CD11b = CD11b_tumor, CD11b_CD15 = CD11b_CD15_tumor)
  
tbl1 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD3_CD8 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl3 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
#                    event = markers_ROIclust_t$surv_vital) ~ CD3_FoxP3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
#   tbl_regression(exponentiate = TRUE,
#                  include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD11b + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD11b_CD15 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl14 <- tbl_stack(list(tbl1, tbl2, tbl4, tbl5))

markers_ROIclust_s <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  filter(!str_detect(suid, paste0(remove_id, collapse = "|")), 
         intratumoral_i_vs_peripheral_p_ == "Peripheral", race == "White") %>% 
  rename(CD3 = CD3_stroma, CD3_CD8 = CD3_CD8_stroma,
         CD3_FoxP3 = CD3_FoxP3_stroma, 
         CD11b = CD11b_stroma, CD11b_CD15 = CD11b_CD15_stroma)

tbl1 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD3_CD8 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl3 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
#                    event = markers_ROIclust_s$surv_vital) ~ CD3_FoxP3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
#   tbl_regression(exponentiate = TRUE,
#                  include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD11b + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD11b_CD15 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl15 <- tbl_stack(list(tbl1, tbl2, tbl4, tbl5))
# tbl14 <- tbl_merge(list(tbl13, tbl14, tbl15), tab_spanner = c("**Overall**", "**Tumor**", "**Stroma**"))
```

## Overall
```{r}
tbl16 <- tbl_stack(list(tbl10, tbl13), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl16
# gt::gtsave(tbl16, paste0(path, "/Table 3. Adjusted hazard ratios and 95% confidence intervals in Overall ROIs cluster option.pdf"))
```

## Tumor
```{r}
tbl17 <- tbl_stack(list(tbl11, tbl14), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl17
# gt::gtsave(tbl17, paste0(path, "/Table 3. Adjusted hazard ratios and 95% confidence intervals in Tumor ROIs cluster option.pdf"))
```

## Stroma
```{r}
tbl18 <- tbl_stack(list(tbl12, tbl15), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl18
# gt::gtsave(tbl18, paste0(path, "/Table 3. Adjusted hazard ratios and 95% confidence intervals in Stroma ROIs cluster option.pdf"))
```

## In Black
```{r Table % cluster option black}
markers_ROIclust_o <- ROI_global %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  filter(intratumoral_i_vs_peripheral_p_ == "Intratumoral" & race == "Black") %>% 
  rename(CD3 = CD3_total, CD3_CD8 = CD3_CD8_total,
         CD3_FoxP3 = CD3_FoxP3_total, 
         CD11b = CD11b_total, CD11b_CD15 = CD11b_CD15_total)
  
tbl1 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD3_CD8 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl3 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
#                    event = markers_ROIclust_o$surv_vital) ~ CD3_FoxP3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
#   tbl_regression(exponentiate = TRUE,
#                  include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD11b + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD11b_CD15 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl10 <- tbl_stack(list(tbl1, tbl2, tbl4, tbl5))

markers_ROIclust_t <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
    filter(intratumoral_i_vs_peripheral_p_ == "Intratumoral" & race == "Black") %>% 
  rename(CD3 = CD3_tumor, CD3_CD8 = CD3_CD8_tumor,
         CD3_FoxP3 = CD3_FoxP3_tumor, 
         CD11b = CD11b_tumor, CD11b_CD15 = CD11b_CD15_tumor)
  
tbl1 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD3_CD8 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl3 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
#                    event = markers_ROIclust_t$surv_vital) ~ CD3_FoxP3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
#   tbl_regression(exponentiate = TRUE,
#                  include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD11b + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD11b_CD15 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl11 <- tbl_stack(list(tbl1, tbl2, tbl4, tbl5))

markers_ROIclust_s <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
    filter(intratumoral_i_vs_peripheral_p_ == "Intratumoral" & race == "Black") %>% 
  rename(CD3 = CD3_stroma, CD3_CD8 = CD3_CD8_stroma,
         CD3_FoxP3 = CD3_FoxP3_stroma, 
         CD11b = CD11b_stroma, CD11b_CD15 = CD11b_CD15_stroma)

tbl1 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD3_CD8 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl3 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
#                    event = markers_ROIclust_s$surv_vital) ~ CD3_FoxP3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
#   tbl_regression(exponentiate = TRUE,
#                  include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD11b + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD11b_CD15 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl12 <- tbl_stack(list(tbl1, tbl2, tbl4, tbl5))
# tbl13 <- tbl_merge(list(tbl10, tbl11, tbl12), tab_spanner = c("**Overall**", "**Tumor**", "**Stroma**"))



markers_ROIclust_o <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  filter(!str_detect(suid, paste0(remove_id, collapse = "|")), 
         intratumoral_i_vs_peripheral_p_ == "Peripheral", race == "Black") %>% 
  rename(CD3 = CD3_total, CD3_CD8 = CD3_CD8_total,
         CD3_FoxP3 = CD3_FoxP3_total, 
         CD11b = CD11b_total, CD11b_CD15 = CD11b_CD15_total)
  
tbl1 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD3_CD8 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl3 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
#                    event = markers_ROIclust_o$surv_vital) ~ CD3_FoxP3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
#   tbl_regression(exponentiate = TRUE,
#                  include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD11b + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD11b_CD15 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl13 <- tbl_stack(list(tbl1, tbl2, tbl4, tbl5))

markers_ROIclust_t <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  filter(!str_detect(suid, paste0(remove_id, collapse = "|")), 
         intratumoral_i_vs_peripheral_p_ == "Peripheral", race == "Black") %>% 
  rename(CD3 = CD3_tumor, CD3_CD8 = CD3_CD8_tumor,
         CD3_FoxP3 = CD3_FoxP3_tumor, 
         CD11b = CD11b_tumor, CD11b_CD15 = CD11b_CD15_tumor)
  
tbl1 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD3_CD8 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl3 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
#                    event = markers_ROIclust_t$surv_vital) ~ CD3_FoxP3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
#   tbl_regression(exponentiate = TRUE,
#                  include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD11b + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD11b_CD15 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl14 <- tbl_stack(list(tbl1, tbl2, tbl4, tbl5))

markers_ROIclust_s <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  filter(!str_detect(suid, paste0(remove_id, collapse = "|")), 
         intratumoral_i_vs_peripheral_p_ == "Peripheral", race == "Black") %>% 
  rename(CD3 = CD3_stroma, CD3_CD8 = CD3_CD8_stroma,
         CD3_FoxP3 = CD3_FoxP3_stroma, 
         CD11b = CD11b_stroma, CD11b_CD15 = CD11b_CD15_stroma)

tbl1 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD3_CD8 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD3_CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl3 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
#                    event = markers_ROIclust_s$surv_vital) ~ CD3_FoxP3 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
#   tbl_regression(exponentiate = TRUE,
#                  include = CD3_FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD11b + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD11b_CD15 + stage + refage + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = CD11b_CD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl15 <- tbl_stack(list(tbl1, tbl2, tbl4, tbl5))
# tbl14 <- tbl_merge(list(tbl13, tbl14, tbl15), tab_spanner = c("**Overall**", "**Tumor**", "**Stroma**"))
```

## Overall
```{r}
tbl16 <- tbl_stack(list(tbl10, tbl13), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl16
# gt::gtsave(tbl16, paste0(path, "/Table 3. Adjusted hazard ratios and 95% confidence intervals in Overall ROIs cluster option.pdf"))
```

## Tumor
```{r}
tbl17 <- tbl_stack(list(tbl11, tbl14), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl17
# gt::gtsave(tbl17, paste0(path, "/Table 3. Adjusted hazard ratios and 95% confidence intervals in Tumor ROIs cluster option.pdf"))
```

## Stroma
```{r}
tbl18 <- tbl_stack(list(tbl12, tbl15), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl18
# gt::gtsave(tbl18, paste0(path, "/Table 3. Adjusted hazard ratios and 95% confidence intervals in Stroma ROIs cluster option.pdf"))
```
<br>

# Frequency distribution of the number of cases
<br>

**Removed 4 patients no BMI**

## Overall
```{r}
markers_ROI_o <- markers_ROI %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  rename(CD3 = CD3_total.i, CD3_CD8 = CD3_CD8_total.i,
         CD3_FoxP3 = CD3_FoxP3_total.i,
         CD11b = CD11b_total.i, CD11b_CD15 = CD11b_CD15_total.i)
tbl10 <- markers_ROI_o %>% 
  select(CD3, CD3_CD8,
         CD3_FoxP3, 
         CD11b, CD11b_CD15, vitalstatus) %>% 
  tbl_summary(by= vitalstatus, statistic = list(all_categorical() ~ "{n}")) %>% 
      add_overall() %>% bold_labels()

markers_ROI_t <- markers_ROI %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  rename(CD3 = CD3_tumor.i, CD3_CD8 = CD3_CD8_tumor.i,
         CD3_FoxP3 = CD3_FoxP3_tumor.i,
         CD11b = CD11b_tumor.i, CD11b_CD15 = CD11b_CD15_tumor.i)
tbl11 <- markers_ROI_t %>% 
  select(CD3, CD3_CD8,
         CD3_FoxP3, 
         CD11b, CD11b_CD15, vitalstatus) %>% 
  tbl_summary(by= vitalstatus, statistic = list(all_categorical() ~ "{n}")) %>% 
      add_overall() %>% bold_labels()

markers_ROI_s <- markers_ROI %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  rename(CD3 = CD3_stroma.i, CD3_CD8 = CD3_CD8_stroma.i,
         CD3_FoxP3 = CD3_FoxP3_stroma.i,
         CD11b = CD11b_stroma.i, CD11b_CD15 = CD11b_CD15_stroma.i)
tbl12 <- markers_ROI_s %>% 
  select(CD3, CD3_CD8,
         CD3_FoxP3, 
         CD11b, CD11b_CD15, vitalstatus) %>% 
  tbl_summary(by= vitalstatus, statistic = list(all_categorical() ~ "{n}")) %>% 
      add_overall() %>% bold_labels()
# tbl13 <- tbl_merge(list(tbl10, tbl11, tbl12), tab_spanner = c("**Overall**", "**Tumor**", "**Stroma**"))

markers_ROI_o <- markers_ROI %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  rename(CD3 = CD3_total.p, CD3_CD8 = CD3_CD8_total.p,
         CD3_FoxP3 = CD3_FoxP3_total.p,
         CD11b = CD11b_total.p, CD11b_CD15 = CD11b_CD15_total.p)
tbl13 <- markers_ROI_o %>% 
  select(CD3, CD3_CD8,
         CD3_FoxP3, 
         CD11b, CD11b_CD15, vitalstatus) %>% 
  tbl_summary(by= vitalstatus, statistic = list(all_categorical() ~ "{n}")) %>% 
      add_overall() %>% bold_labels()

markers_ROI_t <- markers_ROI %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  rename(CD3 = CD3_tumor.p, CD3_CD8 = CD3_CD8_tumor.p,
         CD3_FoxP3 = CD3_FoxP3_tumor.p,
         CD11b = CD11b_tumor.p, CD11b_CD15 = CD11b_CD15_tumor.p)
tbl14 <- markers_ROI_t %>% 
  select(CD3, CD3_CD8,
         CD3_FoxP3, 
         CD11b, CD11b_CD15, vitalstatus) %>% 
  tbl_summary(by= vitalstatus, statistic = list(all_categorical() ~ "{n}")) %>% 
      add_overall() %>% bold_labels()

markers_ROI_s <- markers_ROI %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  rename(CD3 = CD3_stroma.p, CD3_CD8 = CD3_CD8_stroma.p,
         CD3_FoxP3 = CD3_FoxP3_stroma.p,
         CD11b = CD11b_stroma.p, CD11b_CD15 = CD11b_CD15_stroma.p)
tbl15 <- markers_ROI_s %>% 
  select(CD3, CD3_CD8,
         CD3_FoxP3, 
         CD11b, CD11b_CD15, vitalstatus) %>% 
  tbl_summary(by= vitalstatus, statistic = list(all_categorical() ~ "{n}")) %>% 
      add_overall() %>% bold_labels()

# tbl14 <- tbl_merge(list(tbl13, tbl14, tbl15), tab_spanner = c("**Overall**", "**Tumor**", "**Stroma**"))
```

### Overall
```{r}
tbl16 <- tbl_stack(list(tbl10, tbl13), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl16
# gt::gtsave(tbl16, paste0(path, "/Table Frequency distribution of the number of cases Overall group.pdf"))
```

### Tumor
```{r}
tbl17 <- tbl_stack(list(tbl11, tbl14), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl17
# gt::gtsave(tbl17, paste0(path, "/Table Frequency distribution of the number of cases Tumor group.pdf"))
```

### Stroma
```{r}
tbl18 <- tbl_stack(list(tbl12, tbl15), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl18
# gt::gtsave(tbl18, paste0(path, "/Table Frequency distribution of the number of cases Stroma group.pdf"))
```

## In White/Black
```{r}
markers_ROI_o <- markers_ROI %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  filter(race == "White") %>% 
  rename(CD3 = CD3_total.i, CD3_CD8 = CD3_CD8_total.i,
         CD3_FoxP3 = CD3_FoxP3_total.i,
         CD11b = CD11b_total.i, CD11b_CD15 = CD11b_CD15_total.i)
tbl10 <- markers_ROI_o %>% 
  select(CD3, CD3_CD8,
         CD3_FoxP3, 
         CD11b, CD11b_CD15, vitalstatus) %>% 
  tbl_summary(by= vitalstatus, statistic = list(all_categorical() ~ "{n}")) %>% 
      add_overall() %>% bold_labels()

markers_ROI_t <- markers_ROI %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
    filter(race == "White") %>% 
rename(CD3 = CD3_tumor.i, CD3_CD8 = CD3_CD8_tumor.i,
         CD3_FoxP3 = CD3_FoxP3_tumor.i,
         CD11b = CD11b_tumor.i, CD11b_CD15 = CD11b_CD15_tumor.i)
tbl11 <- markers_ROI_t %>% 
  select(CD3, CD3_CD8,
         CD3_FoxP3, 
         CD11b, CD11b_CD15, vitalstatus) %>% 
  tbl_summary(by= vitalstatus, statistic = list(all_categorical() ~ "{n}")) %>% 
      add_overall() %>% bold_labels()

markers_ROI_s <- markers_ROI %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
    filter(race == "White") %>% 
rename(CD3 = CD3_stroma.i, CD3_CD8 = CD3_CD8_stroma.i,
         CD3_FoxP3 = CD3_FoxP3_stroma.i,
         CD11b = CD11b_stroma.i, CD11b_CD15 = CD11b_CD15_stroma.i)
tbl12 <- markers_ROI_s %>% 
  select(CD3, CD3_CD8,
         CD3_FoxP3, 
         CD11b, CD11b_CD15, vitalstatus) %>% 
  tbl_summary(by= vitalstatus, statistic = list(all_categorical() ~ "{n}")) %>% 
      add_overall() %>% bold_labels()
# tbl13 <- tbl_merge(list(tbl10, tbl11, tbl12), tab_spanner = c("**Overall**", "**Tumor**", "**Stroma**"))

markers_ROI_o <- markers_ROI %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
    filter(race == "White") %>% 
rename(CD3 = CD3_total.p, CD3_CD8 = CD3_CD8_total.p,
         CD3_FoxP3 = CD3_FoxP3_total.p,
         CD11b = CD11b_total.p, CD11b_CD15 = CD11b_CD15_total.p)
tbl13 <- markers_ROI_o %>% 
  select(CD3, CD3_CD8,
         CD3_FoxP3, 
         CD11b, CD11b_CD15, vitalstatus) %>% 
  tbl_summary(by= vitalstatus, statistic = list(all_categorical() ~ "{n}")) %>% 
      add_overall() %>% bold_labels()

markers_ROI_t <- markers_ROI %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
    filter(race == "White") %>% 
rename(CD3 = CD3_tumor.p, CD3_CD8 = CD3_CD8_tumor.p,
         CD3_FoxP3 = CD3_FoxP3_tumor.p,
         CD11b = CD11b_tumor.p, CD11b_CD15 = CD11b_CD15_tumor.p)
tbl14 <- markers_ROI_t %>% 
  select(CD3, CD3_CD8,
         CD3_FoxP3, 
         CD11b, CD11b_CD15, vitalstatus) %>% 
  tbl_summary(by= vitalstatus, statistic = list(all_categorical() ~ "{n}")) %>% 
      add_overall() %>% bold_labels()

markers_ROI_s <- markers_ROI %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
    filter(race == "White") %>% 
rename(CD3 = CD3_stroma.p, CD3_CD8 = CD3_CD8_stroma.p,
         CD3_FoxP3 = CD3_FoxP3_stroma.p,
         CD11b = CD11b_stroma.p, CD11b_CD15 = CD11b_CD15_stroma.p)
tbl15 <- markers_ROI_s %>% 
  select(CD3, CD3_CD8,
         CD3_FoxP3, 
         CD11b, CD11b_CD15, vitalstatus) %>% 
  tbl_summary(by= vitalstatus, statistic = list(all_categorical() ~ "{n}")) %>% 
      add_overall() %>% bold_labels()

markers_ROI_o <- markers_ROI %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  filter(race == "Black") %>% 
  rename(CD3 = CD3_total.i, CD3_CD8 = CD3_CD8_total.i,
         CD3_FoxP3 = CD3_FoxP3_total.i,
         CD11b = CD11b_total.i, CD11b_CD15 = CD11b_CD15_total.i)
tbl16 <- markers_ROI_o %>% 
  select(CD3, CD3_CD8,
         CD3_FoxP3, 
         CD11b, CD11b_CD15, vitalstatus) %>% 
  tbl_summary(by= vitalstatus, statistic = list(all_categorical() ~ "{n}")) %>% 
      add_overall() %>% bold_labels()

markers_ROI_t <- markers_ROI %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
    filter(race == "Black") %>% 
rename(CD3 = CD3_tumor.i, CD3_CD8 = CD3_CD8_tumor.i,
         CD3_FoxP3 = CD3_FoxP3_tumor.i,
         CD11b = CD11b_tumor.i, CD11b_CD15 = CD11b_CD15_tumor.i)
tbl17 <- markers_ROI_t %>% 
  select(CD3, CD3_CD8,
         CD3_FoxP3, 
         CD11b, CD11b_CD15, vitalstatus) %>% 
  tbl_summary(by= vitalstatus, statistic = list(all_categorical() ~ "{n}")) %>% 
      add_overall() %>% bold_labels()

markers_ROI_s <- markers_ROI %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
    filter(race == "Black") %>% 
rename(CD3 = CD3_stroma.i, CD3_CD8 = CD3_CD8_stroma.i,
         CD3_FoxP3 = CD3_FoxP3_stroma.i,
         CD11b = CD11b_stroma.i, CD11b_CD15 = CD11b_CD15_stroma.i)
tbl18 <- markers_ROI_s %>% 
  select(CD3, CD3_CD8,
         CD3_FoxP3, 
         CD11b, CD11b_CD15, vitalstatus) %>% 
  tbl_summary(by= vitalstatus, statistic = list(all_categorical() ~ "{n}")) %>% 
      add_overall() %>% bold_labels()
# tbl13 <- tbl_merge(list(tbl10, tbl11, tbl12), tab_spanner = c("**Overall**", "**Tumor**", "**Stroma**"))

markers_ROI_o <- markers_ROI %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
    filter(race == "Black") %>% 
rename(CD3 = CD3_total.p, CD3_CD8 = CD3_CD8_total.p,
         CD3_FoxP3 = CD3_FoxP3_total.p,
         CD11b = CD11b_total.p, CD11b_CD15 = CD11b_CD15_total.p)
tbl19 <- markers_ROI_o %>% 
  select(CD3, CD3_CD8,
         CD3_FoxP3, 
         CD11b, CD11b_CD15, vitalstatus) %>% 
  tbl_summary(by= vitalstatus, statistic = list(all_categorical() ~ "{n}")) %>% 
      add_overall() %>% bold_labels()

markers_ROI_t <- markers_ROI %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
    filter(race == "Black") %>% 
rename(CD3 = CD3_tumor.p, CD3_CD8 = CD3_CD8_tumor.p,
         CD3_FoxP3 = CD3_FoxP3_tumor.p,
         CD11b = CD11b_tumor.p, CD11b_CD15 = CD11b_CD15_tumor.p)
tbl20 <- markers_ROI_t %>% 
  select(CD3, CD3_CD8,
         CD3_FoxP3, 
         CD11b, CD11b_CD15, vitalstatus) %>% 
  tbl_summary(by= vitalstatus, statistic = list(all_categorical() ~ "{n}")) %>% 
      add_overall() %>% bold_labels()

markers_ROI_s <- markers_ROI %>%
    filter(!str_detect(suid, remove_id_bmi)) %>% 
    filter(race == "Black") %>% 
rename(CD3 = CD3_stroma.p, CD3_CD8 = CD3_CD8_stroma.p,
         CD3_FoxP3 = CD3_FoxP3_stroma.p,
         CD11b = CD11b_stroma.p, CD11b_CD15 = CD11b_CD15_stroma.p)
tbl21 <- markers_ROI_s %>% 
  select(CD3, CD3_CD8,
         CD3_FoxP3, 
         CD11b, CD11b_CD15, vitalstatus) %>% 
  tbl_summary(by= vitalstatus, statistic = list(all_categorical() ~ "{n}")) %>% 
      add_overall() %>% bold_labels()

tbl1 <- tbl_merge(list(tbl10, tbl16), tab_spanner = c("**White**", "**Black**"))
tbl2 <- tbl_merge(list(tbl11, tbl17), tab_spanner = c("**White**", "**Black**"))
tbl3 <- tbl_merge(list(tbl12, tbl18), tab_spanner = c("**White**", "**Black**"))
tbl4 <- tbl_merge(list(tbl13, tbl19), tab_spanner = c("**White**", "**Black**"))
tbl5 <- tbl_merge(list(tbl14, tbl20), tab_spanner = c("**White**", "**Black**"))
tbl6 <- tbl_merge(list(tbl15, tbl21), tab_spanner = c("**White**", "**Black**"))
```

### Overall
```{r}
tbl16 <- tbl_stack(list(tbl1, tbl4), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl16
# gt::gtsave(tbl16, paste0(path, "/Table Frequency distribution of the number of cases Overall group.pdf"))
```

### Tumor
```{r}
tbl17 <- tbl_stack(list(tbl2, tbl5), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl17
# gt::gtsave(tbl17, paste0(path, "/Table Frequency distribution of the number of cases Tumor group.pdf"))
```

### Stroma
```{r}
tbl18 <- tbl_stack(list(tbl3, tbl6), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl18
# gt::gtsave(tbl18, paste0(path, "/Table Frequency distribution of the number of cases Stroma group.pdf"))
```
<br>

***

# HR interaction terms by race
Cross product interaction terms between race and the immune markers group.  
Adjusted for stage, age and race and with cluster option.  

**Removed 4 patients no BMI**

<!-- inline_text(tbl1, variable = "CD3:race", level = "high * White", pattern = "{p.value}", pvalue_fun = purrr::partial(style_pvalue, digits = 2)) -->

```{r Table interactions by race cluster option}
markers_ROIclust_o <- ROI_global %>%
      filter(!str_detect(suid, remove_id_bmi)) %>% 
filter(intratumoral_i_vs_peripheral_p_ == "Intratumoral") %>% 
  rename(CD3 = CD3_total, CD3_CD8 = CD3_CD8_total,
         CD3_FoxP3 = CD3_FoxP3_total, 
         CD11b = CD11b_total, CD11b_CD15 = CD11b_CD15_total)
  
tbl1 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu,
                   event = markers_ROIclust_o$surv_vital) ~ CD3 + stage + refage + race + CD3*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = !CD3:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))

tbl2 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD3_CD8 + stage + refage + race + CD3_CD8*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD3_CD8:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))

tbl3 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD3_FoxP3 + stage + refage + race + CD3_FoxP3*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD3_FoxP3:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))

tbl4 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD11b + stage + refage + race + CD11b*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD11b:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))

tbl5 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD11b_CD15 + stage + refage + race + CD11b_CD15*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD11b_CD15:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))

tbl10 <- tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5))

markers_ROIclust_t <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
    filter(intratumoral_i_vs_peripheral_p_ == "Intratumoral") %>% 
  rename(CD3 = CD3_tumor, CD3_CD8 = CD3_CD8_tumor,
         CD3_FoxP3 = CD3_FoxP3_tumor, 
         CD11b = CD11b_tumor, CD11b_CD15 = CD11b_CD15_tumor)
  
tbl1 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD3 + stage + refage + race + CD3*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = !CD3:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>%
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl2 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD3_CD8 + stage + refage + race + CD3_CD8*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD3_CD8:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl3 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD3_FoxP3 + stage + refage + race + CD3_FoxP3*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD3_FoxP3:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl4 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD11b + stage + refage + race + CD11b*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD11b:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl5 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD11b_CD15 + stage + refage + race + CD11b_CD15*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD11b_CD15:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))

tbl11 <- tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5))

markers_ROIclust_s <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
    filter(intratumoral_i_vs_peripheral_p_ == "Intratumoral") %>% 
  rename(CD3 = CD3_stroma, CD3_CD8 = CD3_CD8_stroma,
         CD3_FoxP3 = CD3_FoxP3_stroma, 
         CD11b = CD11b_stroma, CD11b_CD15 = CD11b_CD15_stroma)

tbl1 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD3 + stage + refage + race + CD3*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD3:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl2 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD3_CD8 + stage + refage + race + CD3_CD8*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD3_CD8:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl3 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD3_FoxP3 + stage + refage + race + CD3_FoxP3*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD3_FoxP3:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl4 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD11b + stage + refage + race + CD11b*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD11b:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl5 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD11b_CD15 + stage + refage + race + CD11b_CD15*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD11b_CD15:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))

tbl12 <- tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5))
# tbl13 <- tbl_merge(list(tbl10, tbl11, tbl12), tab_spanner = c("**Overall**", "**Tumor**", "**Stroma**"))



markers_ROIclust_o <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  filter(!str_detect(suid, paste0(remove_id, collapse = "|")), 
         intratumoral_i_vs_peripheral_p_ == "Peripheral") %>% 
  rename(CD3 = CD3_total, CD3_CD8 = CD3_CD8_total,
         CD3_FoxP3 = CD3_FoxP3_total, 
         CD11b = CD11b_total, CD11b_CD15 = CD11b_CD15_total)
  
tbl1 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD3 + stage + refage + race + CD3*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = !CD3:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl2 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD3_CD8 + stage + refage + race + CD3_CD8*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD3_CD8:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl3 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD3_FoxP3 + stage + refage + race + CD3_FoxP3*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD3_FoxP3:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl4 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD11b + stage + refage + race + CD11b*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD11b:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl5 <- coxph(Surv(time = markers_ROIclust_o$timeint_fu, 
                   event = markers_ROIclust_o$surv_vital) ~ CD11b_CD15 + stage + refage + race + CD11b_CD15*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_o) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD11b_CD15:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))

tbl13 <- tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5))

markers_ROIclust_t <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  filter(!str_detect(suid, paste0(remove_id, collapse = "|")), 
         intratumoral_i_vs_peripheral_p_ == "Peripheral") %>% 
  rename(CD3 = CD3_tumor, CD3_CD8 = CD3_CD8_tumor,
         CD3_FoxP3 = CD3_FoxP3_tumor, 
         CD11b = CD11b_tumor, CD11b_CD15 = CD11b_CD15_tumor)
  
tbl1 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD3 + stage + refage + race + CD3*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = !CD3:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl2 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD3_CD8 + stage + refage + race + CD3_CD8*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD3_CD8:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl3 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD3_FoxP3 + stage + refage + race + CD3_FoxP3*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD3_FoxP3:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl4 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD11b + stage + refage + race + CD11b*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD11b:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl5 <- coxph(Surv(time = markers_ROIclust_t$timeint_fu, 
                   event = markers_ROIclust_t$surv_vital) ~ CD11b_CD15 + stage + refage + race + CD11b_CD15*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_t) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD11b_CD15:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))

tbl14 <- tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5))

markers_ROIclust_s <- ROI_global %>% 
    filter(!str_detect(suid, remove_id_bmi)) %>% 
  filter(!str_detect(suid, paste0(remove_id, collapse = "|")), 
         intratumoral_i_vs_peripheral_p_ == "Peripheral") %>% 
  rename(CD3 = CD3_stroma, CD3_CD8 = CD3_CD8_stroma,
         CD3_FoxP3 = CD3_FoxP3_stroma, 
         CD11b = CD11b_stroma, CD11b_CD15 = CD11b_CD15_stroma)

tbl1 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD3 + stage + refage + race + CD3*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD3:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl2 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD3_CD8 + stage + refage + race + CD3_CD8*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD3_CD8:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl3 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD3_FoxP3 + stage + refage + race + CD3_FoxP3*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD3_FoxP3:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl4 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD11b + stage + refage + race + CD11b*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD11b:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))
tbl5 <- coxph(Surv(time = markers_ROIclust_s$timeint_fu, 
                   event = markers_ROIclust_s$surv_vital) ~ CD11b_CD15 + stage + refage + race + CD11b_CD15*race + BMI_recent_grp + diab + smoker, cluster = suid, data =  markers_ROIclust_s) %>%
  tbl_regression(exponentiate = TRUE,
                 include = !CD11b_CD15:race, pvalue_fun = purrr::partial(style_pvalue, digits = 2)) %>% 
  bold_p(t = .05) %>% 
  modify_column_hide(c(estimate, ci))

tbl15 <- tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5))
# tbl14 <- tbl_merge(list(tbl13, tbl14, tbl15), tab_spanner = c("**Overall**", "**Tumor**", "**Stroma**"))
```

## Overall
```{r}
tbl16 <- tbl_stack(list(tbl10, tbl13), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl16
# gt::gtsave(tbl16, paste0(path, "/Table 4. Adjusted hazard ratios interaction in Overall ROIs cluster option.pdf"))
```

## Tumor
```{r}
tbl17 <- tbl_stack(list(tbl11, tbl14), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl17
# gt::gtsave(tbl17, paste0(path, "/Table 4. Adjusted hazard ratios interaction in Tumor ROIs cluster option.pdf"))
```

## Stroma
```{r}
tbl18 <- tbl_stack(list(tbl12, tbl15), group_header = c("Intratumoral", "Peripheral")) %>% as_gt()
tbl18
# gt::gtsave(tbl18, paste0(path, "/Table 4. Adjusted hazard ratios interaction in Stroma ROIs cluster option.pdf"))
```


# HR Cluster
`r emo::ji("pad")` Note to remember. The cluster were built on the data with the averaged measurement. I am not using the cluster option in the coxph even though I saw a really slight change in CI values but not in p value.  

**Removed 4 patients no BMI**

## Overall
```{r Table HR cluster}
markers_ROI <- markers_ROI %>% filter(!str_detect(suid, remove_id_bmi))


tbl1 <- coxph(Surv(time = markers_ROI$timeint_fu, 
                   event = markers_ROI$surv_vital) ~ clusters_all_IandP + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = clusters_all_IandP) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROI$timeint_fu, 
                   event = markers_ROI$surv_vital) ~ dbl_pos + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI) %>%
  tbl_regression(exponentiate = TRUE,
                 include = dbl_pos) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- coxph(Surv(time = markers_ROI$timeint_fu, 
                   event = markers_ROI$surv_vital) ~ clusters_CD3CD8 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI) %>%
  tbl_regression(exponentiate = TRUE,
                 include = clusters_CD3CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROI$timeint_fu, 
                   event = markers_ROI$surv_vital) ~ clusters_CD3FoxP3 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI) %>%
  tbl_regression(exponentiate = TRUE,
                 include = clusters_CD3FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROI$timeint_fu, 
                   event = markers_ROI$surv_vital) ~ clusters_FoxP3_ + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI) %>%
  tbl_regression(exponentiate = TRUE,
                 include = clusters_FoxP3_) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl6 <- coxph(Surv(time = markers_ROI$timeint_fu, 
                   event = markers_ROI$surv_vital) ~ clusters_CD11bCD15 + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI) %>%
  tbl_regression(exponentiate = TRUE,
                 include = clusters_CD11bCD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl10 <- tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6))
tbl10
```

## In White (I can bind W/B if you want them side by side)
```{r Table HR white}
markers_ROI_white <- markers_ROI %>% filter(!str_detect(suid, remove_id_bmi)) %>%
  filter(race == "White")
  
tbl1 <- coxph(Surv(time = markers_ROI_white$timeint_fu, 
                   event = markers_ROI_white$surv_vital) ~ clusters_all_IandP + stage + refage + BMI_recent_grp + diab + smoker, data =  markers_ROI_white)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = clusters_all_IandP) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROI_white$timeint_fu, 
                   event = markers_ROI_white$surv_vital) ~ dbl_pos + stage + refage + BMI_recent_grp + diab + smoker, data =  markers_ROI_white) %>%
  tbl_regression(exponentiate = TRUE,
                 include = dbl_pos) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- coxph(Surv(time = markers_ROI_white$timeint_fu, 
                   event = markers_ROI_white$surv_vital) ~ clusters_CD3CD8 + stage + refage + BMI_recent_grp + diab + smoker, data =  markers_ROI_white) %>%
  tbl_regression(exponentiate = TRUE,
                 include = clusters_CD3CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROI_white$timeint_fu, 
                   event = markers_ROI_white$surv_vital) ~ clusters_CD3FoxP3 + stage + refage + BMI_recent_grp + diab + smoker, data =  markers_ROI_white) %>%
  tbl_regression(exponentiate = TRUE,
                 include = clusters_CD3FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROI_white$timeint_fu, 
                   event = markers_ROI_white$surv_vital) ~ clusters_FoxP3_ + stage + refage + BMI_recent_grp + diab + smoker, data =  markers_ROI_white) %>%
  tbl_regression(exponentiate = TRUE,
                 include = clusters_FoxP3_) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl6 <- coxph(Surv(time = markers_ROI_white$timeint_fu, 
                   event = markers_ROI_white$surv_vital) ~ clusters_CD11bCD15 + stage + refage + BMI_recent_grp + diab + smoker, data =  markers_ROI_white) %>%
  tbl_regression(exponentiate = TRUE,
                 include = clusters_CD11bCD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl10 <- tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6))
tbl10
```

## In Black
```{r Table cluster black}
markers_ROI_black <- markers_ROI %>% filter(!str_detect(suid, remove_id_bmi)) %>%
  filter(race == "Black")
  
tbl1 <- coxph(Surv(time = markers_ROI_black$timeint_fu, 
                   event = markers_ROI_black$surv_vital) ~ clusters_all_IandP + stage + refage + BMI_recent_grp + diab + smoker, data =  markers_ROI_black)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = clusters_all_IandP) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROI_black$timeint_fu, 
                   event = markers_ROI_black$surv_vital) ~ dbl_pos + stage + refage + BMI_recent_grp + diab + smoker, data =  markers_ROI_black) %>%
  tbl_regression(exponentiate = TRUE,
                 include = dbl_pos) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- coxph(Surv(time = markers_ROI_black$timeint_fu, 
                   event = markers_ROI_black$surv_vital) ~ clusters_CD3CD8 + stage + refage + BMI_recent_grp + diab + smoker, data =  markers_ROI_black) %>%
  tbl_regression(exponentiate = TRUE,
                 include = clusters_CD3CD8) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl4 <- coxph(Surv(time = markers_ROI_black$timeint_fu, 
                   event = markers_ROI_black$surv_vital) ~ clusters_CD3FoxP3 + stage + refage + BMI_recent_grp + diab + smoker, data =  markers_ROI_black) %>%
  tbl_regression(exponentiate = TRUE,
                 include = clusters_CD3FoxP3) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- coxph(Surv(time = markers_ROI_black$timeint_fu, 
                   event = markers_ROI_black$surv_vital) ~ clusters_FoxP3_ + stage + refage + BMI_recent_grp + diab + smoker, data =  markers_ROI_black) %>%
  tbl_regression(exponentiate = TRUE,
                 include = clusters_FoxP3_) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl6 <- coxph(Surv(time = markers_ROI_black$timeint_fu, 
                   event = markers_ROI_black$surv_vital) ~ clusters_CD11bCD15 + stage + refage + BMI_recent_grp + diab + smoker, data =  markers_ROI_black) %>%
  tbl_regression(exponentiate = TRUE,
                 include = clusters_CD11bCD15) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl10 <- tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6))
tbl10
```
<br>

# HR immunoscore  

`r emo::ji("pad")` Note to remember. The immunoscore were built on the data with the averaged measurement. I am not using the cluster option in the coxph even though I saw a really slight change in CI and p value.  

**Removed 4 patients no BMI**

## Overall
```{r Table HR Immunoscore}
markers_ROI_imm <- markers_ROI %>% filter(!str_detect(suid, remove_id_bmi))

tbl1 <- coxph(Surv(time = markers_ROI_imm$timeint_fu, 
                   event = markers_ROI_imm$surv_vital) ~ immunoscore_patients + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_imm)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = immunoscore_patients) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROI_imm$timeint_fu, 
                   event = markers_ROI_imm$surv_vital) ~ immunoscore_2018lancet_patients + stage + refage + race + BMI_recent_grp + diab + smoker, data =  markers_ROI_imm) %>%
  tbl_regression(exponentiate = TRUE,
                 include = immunoscore_2018lancet_patients) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl10 <- tbl_stack(list(tbl1, tbl2))
tbl10
```

## In White (I can bind W/B if you want them side by side)
```{r Table HR Immunoscore white}
markers_ROI_white <- markers_ROI %>% filter(!str_detect(suid, remove_id_bmi)) %>%
  filter(race == "White")
  
tbl1 <- coxph(Surv(time = markers_ROI_white$timeint_fu, 
                   event = markers_ROI_white$surv_vital) ~ immunoscore_patients + stage + refage + BMI_recent_grp + diab + smoker, data =  markers_ROI_white)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = immunoscore_patients) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROI_white$timeint_fu, 
                   event = markers_ROI_white$surv_vital) ~ immunoscore_2018lancet_patients + stage + refage + BMI_recent_grp + diab + smoker, data =  markers_ROI_white) %>%
  tbl_regression(exponentiate = TRUE,
                 include = immunoscore_2018lancet_patients) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl10 <- tbl_stack(list(tbl1, tbl2))
tbl10
```

## In Black
```{r Table HR Immunoscore black}
markers_ROI_black <- markers_ROI %>% filter(!str_detect(suid, remove_id_bmi)) %>%
  filter(race == "Black")
  
tbl1 <- coxph(Surv(time = markers_ROI_black$timeint_fu, 
                   event = markers_ROI_black$surv_vital) ~ immunoscore_patients + stage + refage + BMI_recent_grp + diab + smoker, data =  markers_ROI_black)  %>% 
  tbl_regression(exponentiate = TRUE,
                 include = immunoscore_patients) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- coxph(Surv(time = markers_ROI_black$timeint_fu, 
                   event = markers_ROI_black$surv_vital) ~ immunoscore_2018lancet_patients + stage + refage + BMI_recent_grp + diab + smoker, data =  markers_ROI_black) %>%
  tbl_regression(exponentiate = TRUE,
                 include = immunoscore_2018lancet_patients) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl10 <- tbl_stack(list(tbl1, tbl2))
tbl10
```
<br>














