---
title: "WTS analysis"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: cerulean
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
h1.title {
  font-size: 25px;
}
.figure {
   margin-top: 25px;
   <!-- margin-bottom: 100px; -->
}

table {
    margin-top: 25px;
    <!-- margin-bottom: 100px !important; -->
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

<style>
div.blue { background-color:#0099CC; border-radius: 5px; padding: 20px; font-size: 38px}
</style>
<div class = "blue">

<span style="color: white;">WTS analysis</span>

</div>
<br>

```{r library, include=FALSE}
library(tidyverse)
library(data.table)
library(gtsummary)
library(survival)
library(survminer)
library(psych)
# library(corrplot)
library(ggcorrplot)
library(mclust)
```

```{r load}
# loadd(clinical_data, ROI_tumor ,ROI_stroma ,ROI_total,
#       cases_match)

ROI_global <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_AACES_NCOCS/ROI_global.rds")
markers_ROI <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_AACES_NCOCS/markers_ROI.rds")
# clinical_data <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_AACES_NCOCS/clinical_data.rds")

# Rewove patients not matched or lost match
# ROI_global <- left_join(ROI_global, clinical_data, by="suid") %>% drop_na(pair_id) %>% 
#   group_by(pair_id) %>% 
#   mutate(have_a_match = dense_rank(interaction(suid, pair_id))) %>% 
#   group_by(pair_id) %>% 
#   mutate(is_paired = max(have_a_match)) %>% 
#   filter(is_paired == 2) %>% 
#   select(pair_id, everything(), -c(is_paired, have_a_match)) %>% 
#   ungroup()

# markers_match <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_AACES_NCOCS/markers_match.rds")
path <- fs::path("","Volumes","Peres_Research","K99_R00", "Image analysis data", "WTS Margins Analysis 20 Slides Peres_P1 May 2021")

# CODE TO CLEAN AND SAVE WTS DATA

# fct_name_repair <- function(colnms) {
#   tolower(gsub("[ ():]", "_", colnms))
# }
# 
# wts_total <-
#   readxl::read_xlsx(paste0(path,
#       "/Peres_P1_20WTS_Margins_CD3_CD8_Analysis.xlsx"
#     ), .name_repair = fct_name_repair)
# wts_tumor <-
#   readxl::read_xlsx(paste0(path,
#       "/Peres_P1_20WTS_Margins_CD3_CD8_Analysis.xlsx"
#     ), sheet = "Tumor", .name_repair = fct_name_repair)
# wts_stroma <-
#   readxl::read_xlsx(paste0(path,
#       "/Peres_P1_20WTS_Margins_CD3_CD8_Analysis.xlsx"
#     ), sheet = "Stroma", .name_repair = fct_name_repair)
# 
# fct_name_repair2 <- function(data) {
#   data <- data %>%
#   rename_all(.  %>%
#                # paste(colnames(.), "wts", sep = "_") %>%
#                gsub("__", "_", .) %>%
#                gsub("%", "percent", .) %>%
#                gsub("²", "2", .) %>%
#                gsub("\\+", "plus", .))
# }
# wts_total <- fct_name_repair2(wts_total)
# wts_tumor <- fct_name_repair2(wts_tumor)
# wts_stroma <- fct_name_repair2(wts_stroma)
# 
# wts_data <-
#   full_join(wts_tumor, wts_stroma, by = "image_tag", suffix = c("_tumor", "_stroma")) %>%
#   full_join(., wts_total, by = "image_tag") %>%
#   mutate(suid = str_match(image_tag,
#                             "(Peres_P1_AACES.|Peres_P1_AACEES.|Peres_P1_OV|Peres_P1.|)([:digit:]*)")[,3]) %>%
#   mutate(suid = as.character(suid)) %>%
#   select(suid, everything())
# write_rds(wts_data, "wts_data.rds")

wts_data <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_AACES_NCOCS/wts_data.rds") %>% 
  mutate(percent_tumor = round((tumor_total_cells / total_cells)*100, 2)
         ) %>% 
  mutate(percent_stroma = round((stroma_total_cells / total_cells)*100, 2)
         )

```

```{r merging}
# wts_datas <- left_join(wts_data, markers_ROI, by = "suid")
uid <- paste0(wts_data$suid, collapse = "|")

markers_ROI <- markers_ROI[(grepl(uid, markers_ROI$suid)),] %>% 
  rename("tumor_percent_cd3_opal_650_positive_cells" = percent_CD3_tumor.p,
         "tumor_percent_cd8_opal_570_positive_cells" = percent_CD8_tumor.p,
         "tumor_percent_cd3plus_cd8plus_positive_cells" = percent_CD3_CD8_tumor.p,
         "stroma_percent_cd3_opal_650_positive_cells" = percent_CD3_stroma.p, 
         "stroma_percent_cd8_opal_570_positive_cells" = percent_CD8_stroma.p,
         "stroma_percent_cd3plus_cd8plus_positive_cells" = percent_CD3_CD8_stroma.p,
         "percent_cd3_opal_650_positive_cells" = percent_CD3_total.p,
         "percent_cd8_opal_570_positive_cells" = percent_CD8_total.p,
         "percent_cd3plus_cd8plus_positive_cells" = percent_CD3_CD8_total.p
)
wts_datas <- bind_rows(wts_data, markers_ROI) %>% 
  select("suid", "tumor_percent_cd3_opal_650_positive_cells", 
         "tumor_percent_cd8_opal_570_positive_cells",
         "tumor_percent_cd3plus_cd8plus_positive_cells",
         "stroma_percent_cd3_opal_650_positive_cells",
         "stroma_percent_cd8_opal_570_positive_cells",
         "stroma_percent_cd3plus_cd8plus_positive_cells",
         "percent_cd3_opal_650_positive_cells",
         "percent_cd8_opal_570_positive_cells",
         "percent_cd3plus_cd8plus_positive_cells")

wts_datas <- as.data.frame(wts_datas)
```

# Average % tumor and stroma for the WTS

```{r}
average_wts <- wts_data %>% 
  select("tumor_percent_cd3_opal_650_positive_cells", 
         "tumor_percent_cd8_opal_570_positive_cells",
         "tumor_percent_cd3plus_cd8plus_positive_cells",
         "stroma_percent_cd3_opal_650_positive_cells",
         "stroma_percent_cd8_opal_570_positive_cells",
         "stroma_percent_cd3plus_cd8plus_positive_cells") %>% 
  summarise(across(where(is.numeric), mean)) %>% 
  t() %>% 
  `colnames<-`(c("wts"))

average_ <- markers_ROI %>% 
  select("tumor_percent_cd3_opal_650_positive_cells", 
         "tumor_percent_cd8_opal_570_positive_cells",
         "tumor_percent_cd3plus_cd8plus_positive_cells",
         "stroma_percent_cd3_opal_650_positive_cells",
         "stroma_percent_cd8_opal_570_positive_cells",
         "stroma_percent_cd3plus_cd8plus_positive_cells") %>% 
  summarise(across(where(is.numeric), mean, na.rm = TRUE)) %>% 
  t() %>% 
  `colnames<-`(c("roi")) %>% 
  bind_cols(., average_wts, .id = c("tumor_percent_cd3", 
         "tumor_percent_cd8",
         "tumor_percent_cd3plus_cd8plus",
         "stroma_percent_cd3",
         "stroma_percent_cd8",
         "stroma_percent_cd3plus_cd8plus")) %>% 
  select(marker = .id, everything())
average_

markers_ROI %>%
  select(suid, percent_tumor_roi.periph = mean_tumor.p, percent_stroma_roi.periph = mean_stroma.p) %>% 
  full_join(., wts_data %>% select(suid, percent_tumor_wts = percent_tumor, percent_stroma_wts = percent_stroma), by = "suid") %>% 
  select(-suid) %>% 
  tbl_summary(digits = list(everything() ~  2),
              statistic = list(everything() ~ "{mean} ({min}, {max})")
              )
  
```

# Correlations between the % positivity of CD3 and CD8 between the WTS and peritumoral region ROIs

```{r}
cor_wts <- wts_data %>% 
  select(suid, "tumor_percent_cd3_opal_650_positive_cells", 
         "tumor_percent_cd8_opal_570_positive_cells",
         "tumor_percent_cd3plus_cd8plus_positive_cells",
         "stroma_percent_cd3_opal_650_positive_cells",
         "stroma_percent_cd8_opal_570_positive_cells",
         "stroma_percent_cd3plus_cd8plus_positive_cells") %>% 
  mutate(slide = "wts")

cor_roi <- markers_ROI %>% 
  select(suid, "tumor_percent_cd3_opal_650_positive_cells", 
         "tumor_percent_cd8_opal_570_positive_cells",
         "tumor_percent_cd3plus_cd8plus_positive_cells",
         "stroma_percent_cd3_opal_650_positive_cells",
         "stroma_percent_cd8_opal_570_positive_cells",
         "stroma_percent_cd3plus_cd8plus_positive_cells") %>% 
  mutate(slide = "roi") %>% 
  bind_rows(., cor_wts)
cor_roi

cor_data <- data.frame(matrix(nrow=1, ncol=0))

for(i in 1:length(colnames(wts_datas))) {
  
  ids <- wts_datas %>% select(suid)

  if(class(wts_datas[,i]) == "numeric" | class(wts_datas[,i]) == "integer") {
    
    cor_df <- cbind(ids, value = wts_datas[,i])
    cor_df <- cor_df %>%
      mutate(iteration = "iteration0") %>%
      group_by(suid) %>%
      mutate(n = row_number(suid)) %>%
      ungroup() %>%
      unite(iteration, iteration:n, sep = "", remove = TRUE, na.rm = TRUE) %>%
      pivot_wider(names_from = iteration, values_from = value) %>%
      select(c(starts_with("iteration")))

    cor <- cor(cor_df, use = "complete.obs")[1,2]
    cor_data <- cbind(cor_data,cor)
    
  }
  
}

colnames(cor_data) <- colnames(wts_datas)[2:ncol(wts_datas)]
cor_data

rm(cor_df, cor, ids)

```


# Overall ICC

I am comparing the new wts data (1 slide) with the ROI peripheral data (average of 3ish slide).  
I selected only the % as I am working more with that and the cell numbers or density will obviously be different.  
```{r}
ICC_data <- data.frame(matrix(nrow=1, ncol=0))

for(i in 1:length(colnames(wts_datas))) {
  
  ids <- wts_datas %>% select(suid)

  if(class(wts_datas[,i]) == "numeric" | class(wts_datas[,i]) == "integer") {
    
    ICC_df <- cbind(ids, value = wts_datas[,i])
    ICC_df <- ICC_df %>%
      mutate(iteration = "iteration0") %>%
      group_by(suid) %>%
      mutate(n = row_number(suid)) %>%
      ungroup() %>%
      unite(iteration, iteration:n, sep = "", remove = TRUE, na.rm = TRUE) %>%
      pivot_wider(names_from = iteration, values_from = value) %>%
      select(c(starts_with("iteration")))

    ICC <- ICC(ICC_df)$results[4,2]
    ICC_data <- cbind(ICC_data,ICC)
    
  }
  
}

rm(ICC_df, ICC, ids)
colnames(ICC_data) <- colnames(wts_datas)[2:ncol(wts_datas)]

library(plotly)
plot <- ICC_data %>% 
  pivot_longer(cols = everything()) %>% 
  mutate(ICC = "ICC") %>% 
  mutate(reliability = case_when(
    value < 0.5 ~ "poor",
    value >= 0.5 &
      value < 0.75 ~ "moderate",
    value >= 0.75 &
      value < 0.9 ~ "good",
    value >= 0.9 ~ "excellent"
  )) %>% 
  mutate(text = paste("Measurement: ", name, "\nICC: ", round(value, 2), "\nStrict Reliability: ", reliability, sep="")) %>% 
  ggplot(aes(x = ICC, y = value, color = reliability, text=text))+
  labs(title = "General Reliability of the measurement iteration value", x= NULL, y= "ICC value")+
  scale_color_brewer(palette = "Set2") +
  scale_x_discrete(labels = "")+
  theme_minimal()+
  geom_point(size = 1, position=position_jitter(w=0.8))
plot <- ggplotly(plot, tooltip="text")
plot
plot <- ICC_data %>% 
  pivot_longer(cols = everything()) %>% 
  mutate(reliability = case_when(
    value < 0.5 ~ "poor",
    value >= 0.5 &
      value < 0.75 ~ "moderate",
    value >= 0.75 &
      value < 0.9 ~ "good",
    value >= 0.9 ~ "excellent"
  ))
plot
```
<br>
<br>

***

# Correlation per patient
Look at the correlation between each patients (using only the % variables).  
I simplified the plot to find this correlation within patient on the diagonal.  
```{r}
wts_datas1 <- wts_datas %>% 
  drop_na() %>% 
  arrange(suid) %>% 
  group_by(suid) %>% 
  mutate(n= n()) %>% 
  filter(!n == 1) %>% 
  mutate(n = row_number()) %>% 
  mutate(wts = ifelse(n == 2, "wts_", "ini_")) %>% 
  unite(suid, c("wts", "suid"), sep = "", remove = FALSE) %>% 
  select(-n) %>% 
  ungroup()

ids <- paste(paste0(" ",wts_datas1$suid, sep = ""))

a <- t(wts_datas1 %>% select(-suid, -wts)) %>% `row.names<-`(NULL)
colnames(a) <- (ids)

mat <- cor(a, use = "pairwise.complete.obs")

mat1 <- as.data.frame(mat) %>% select(contains("wts")) %>% t() %>% 
  as.data.frame(., row.names = NULL) %>% select(contains("ini")) %>% as.matrix()

upper_gamb <- mat1
upper_gamb[lower.tri(upper_gamb)] <- NA

ggcorrplot(upper_gamb, hc.order = FALSE, method = "square", 
           type = "lower", 
           lab = TRUE, 
           title = "Correlation between slides",
           show.legend = TRUE, legend.title = "Correlation", show.diag = TRUE,
           lab_col = "darkblue", lab_size = 3, 
           sig.level = 0.05, insig = c("pch", "blank"), pch = 4, pch.col = "black", pch.cex = 10, 
           tl.cex = 10, tl.col = "red", tl.srt = 40,
           digits = 2
)
```

# Compare general %
Look at the abundance of cells comparing the 19 slides.  

```{r}
wts_datas1 %>% 
  select(-suid) %>% 
  tbl_summary(by = wts, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing = "no", digits = list(all_continuous() ~ 2)) %>%
  add_p()
```

# Patients Group category
Each patient is categories to be low (<1%) or high (>1%)


```{r}
cold_hot <- function(data){
  data <- data %>% 
  mutate(CD3_tumor = case_when(
    tumor_percent_cd3_opal_650_positive_cells <= 1      ~ "low",
    tumor_percent_cd3_opal_650_positive_cells > 1       ~ "high"
  ), CD3_tumor = factor(CD3_tumor, levels = c("low","high"))) %>% 
  mutate(CD8_tumor = case_when(
    tumor_percent_cd8_opal_570_positive_cells <= 1      ~ "low",
    tumor_percent_cd8_opal_570_positive_cells > 1       ~ "high"
  ), CD8_tumor = factor(CD8_tumor, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_tumor = case_when(
    tumor_percent_cd3plus_cd8plus_positive_cells <= 1      ~ "low",
    tumor_percent_cd3plus_cd8plus_positive_cells > 1       ~ "high"
  ), CD3_CD8_tumor = factor(CD3_CD8_tumor, levels = c("low","high"))) %>% 
  
  mutate(CD3_stroma = case_when(
    stroma_percent_cd3_opal_650_positive_cells <= 1      ~ "low",
    stroma_percent_cd3_opal_650_positive_cells > 1       ~ "high"
  ), CD3_stroma = factor(CD3_stroma, levels = c("low","high"))) %>% 
  mutate(CD8_stroma = case_when(
    stroma_percent_cd8_opal_570_positive_cells <= 1      ~ "low",
    stroma_percent_cd8_opal_570_positive_cells > 1       ~ "high"
  ), CD8_stroma = factor(CD8_stroma, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_stroma = case_when(
    stroma_percent_cd3plus_cd8plus_positive_cells <= 1      ~ "low",
    stroma_percent_cd3plus_cd8plus_positive_cells > 1       ~ "high"
  ), CD3_CD8_stroma = factor(CD3_CD8_stroma, levels = c("low","high"))) %>% 
  
  mutate(CD3_total = case_when(
    percent_cd3_opal_650_positive_cells <= 1      ~ "low",
    percent_cd3_opal_650_positive_cells > 1       ~ "high"
  ), CD3_total = factor(CD3_total, levels = c("low","high"))) %>% 
  mutate(CD8_total = case_when(
    percent_cd8_opal_570_positive_cells <= 1      ~ "low",
    percent_cd8_opal_570_positive_cells > 1       ~ "high"
  ), CD8_total = factor(CD8_total, levels = c("low","high"))) %>% 
  mutate(CD3_CD8_total = case_when(
    percent_cd3plus_cd8plus_positive_cells <= 1      ~ "low",
    percent_cd3plus_cd8plus_positive_cells > 1       ~ "high"
  ), CD3_CD8_total = factor(CD3_CD8_total, levels = c("low","high")))
}

# markers_ROI <- cold_hot(markers_ROI)
# wts_data <- cold_hot(wts_data)
wts_datas1 <- cold_hot(wts_datas1)
# wts_datas <- bind_rows(wts_data, markers_ROI)


# wts_datas1 <- left_join(wts_data, markers_ROI, by = "suid", suffix = c("", "_wts")) %>%
#   select("suid", starts_with("tumor_percent_cd3_opal_650_positive_cells"),
#          starts_with("tumor_percent_cd8_opal_570_positive_cells"),
#          starts_with("tumor_percent_cd3plus_cd8plus_positive_cells"),
#          starts_with("stroma_percent_cd3_opal_650_positive_cells"),
#          starts_with("stroma_percent_cd8_opal_570_positive_cells"),
#          starts_with("stroma_percent_cd3plus_cd8plus_positive_cells"),
#          starts_with("percent_cd3_opal_650_positive_cells"),
#          starts_with("percent_cd8_opal_570_positive_cells"),
#          starts_with("percent_cd3plus_cd8plus_positive_cells")) %>%
#   drop_na()

wts_datas1 %>% 
  select(CD3_tumor, CD8_tumor, 
         CD3_CD8_tumor, CD3_stroma, 
         CD8_stroma, CD3_CD8_stroma,
         wts) %>% 
  tbl_summary(by = wts, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing = "no", digits = list(all_continuous() ~ 2)) %>% add_p()
```

6 patient were "low" for CD3 in initial slides, 7 are now "low" in the wts. etc

## Kappa 

```{r}
wts_datas2 <- wts_datas1 %>% select(suid, CD3_tumor : CD3_CD8_total) %>% 
  mutate(suid = str_remove(suid, "ini_|wts_")) %>% 
  as.data.frame()

library(irr)

kappa_data <- data.frame(matrix(nrow=1, ncol=0))

for(i in 1:length(colnames(wts_datas2))) {
  
  ids <- wts_datas2 %>% select(suid)

  if(class(wts_datas2[,i]) == "numeric" | class(wts_datas2[,i]) == "integer") {
    
    kappa_df <- cbind(ids, value = wts_datas2[,i])
    kappa_df <- kappa_df %>%
      mutate(iteration = "iteration0") %>%
      group_by(suid) %>%
      mutate(n = row_number(suid)) %>%
      ungroup() %>%
      unite(iteration, iteration:n, sep = "", remove = TRUE, na.rm = TRUE) %>%
      pivot_wider(names_from = iteration, values_from = value) %>%
      select(c(starts_with("iteration")))

    kappa <- kappa2(kappa_df, "unweighted")$value
    kappa_data <- cbind(kappa_data, kappa)
    
  }

}
```

CD3_tumor
```{r}
kappa_df <- cbind(ids, value = wts_datas2[,"CD3_tumor"])
kappa_df <- kappa_df %>%
      mutate(iteration = "iteration0") %>%
      group_by(suid) %>%
      mutate(n = row_number(suid)) %>%
      ungroup() %>%
      unite(iteration, iteration:n, sep = "", remove = TRUE, na.rm = TRUE) %>%
      pivot_wider(names_from = iteration, values_from = value) %>%
      select(c(starts_with("iteration"))) %>% 
  rename(roi = iteration01, wts = iteration02)
print(kappa_df)
table(kappa_df$roi, kappa_df$wts)
kappa2(kappa_df, "unweighted")$value
```

CD8_tumor
```{r}
kappa_df <- cbind(ids, value = wts_datas2[,"CD8_tumor"])
kappa_df <- kappa_df %>%
      mutate(iteration = "iteration0") %>%
      group_by(suid) %>%
      mutate(n = row_number(suid)) %>%
      ungroup() %>%
      unite(iteration, iteration:n, sep = "", remove = TRUE, na.rm = TRUE) %>%
      pivot_wider(names_from = iteration, values_from = value) %>%
      select(c(starts_with("iteration"))) %>% 
  rename(roi = iteration01, wts = iteration02)
print(kappa_df)
table(kappa_df$roi, kappa_df$wts)
kappa2(kappa_df, "unweighted")$value
```

CD3_CD8_tumor
```{r}
kappa_df <- cbind(ids, value = wts_datas2[,"CD3_CD8_tumor"])
kappa_df <- kappa_df %>%
      mutate(iteration = "iteration0") %>%
      group_by(suid) %>%
      mutate(n = row_number(suid)) %>%
      ungroup() %>%
      unite(iteration, iteration:n, sep = "", remove = TRUE, na.rm = TRUE) %>%
      pivot_wider(names_from = iteration, values_from = value) %>%
      select(c(starts_with("iteration"))) %>% 
  rename(roi = iteration01, wts = iteration02)
print(kappa_df)
table(kappa_df$roi, kappa_df$wts)
kappa2(kappa_df, "unweighted")$value
```

CD3_stroma
```{r}
kappa_df <- cbind(ids, value = wts_datas2[,"CD3_stroma"])
kappa_df <- kappa_df %>%
      mutate(iteration = "iteration0") %>%
      group_by(suid) %>%
      mutate(n = row_number(suid)) %>%
      ungroup() %>%
      unite(iteration, iteration:n, sep = "", remove = TRUE, na.rm = TRUE) %>%
      pivot_wider(names_from = iteration, values_from = value) %>%
      select(c(starts_with("iteration"))) %>% 
  rename(roi = iteration01, wts = iteration02)
print(kappa_df)
table(kappa_df$roi, kappa_df$wts)
kappa2(kappa_df, "unweighted")$value
```

CD8_stroma
```{r}
kappa_df <- cbind(ids, value = wts_datas2[,"CD8_stroma"])
kappa_df <- kappa_df %>%
      mutate(iteration = "iteration0") %>%
      group_by(suid) %>%
      mutate(n = row_number(suid)) %>%
      ungroup() %>%
      unite(iteration, iteration:n, sep = "", remove = TRUE, na.rm = TRUE) %>%
      pivot_wider(names_from = iteration, values_from = value) %>%
      select(c(starts_with("iteration"))) %>% 
  rename(roi = iteration01, wts = iteration02)
print(kappa_df)
table(kappa_df$roi, kappa_df$wts)
kappa2(kappa_df, "unweighted")$value
```

CD3_CD8_stroma
```{r}
kappa_df <- cbind(ids, value = wts_datas2[,"CD3_CD8_stroma"])
kappa_df <- kappa_df %>%
      mutate(iteration = "iteration0") %>%
      group_by(suid) %>%
      mutate(n = row_number(suid)) %>%
      ungroup() %>%
      unite(iteration, iteration:n, sep = "", remove = TRUE, na.rm = TRUE) %>%
      pivot_wider(names_from = iteration, values_from = value) %>%
      select(c(starts_with("iteration"))) %>% 
  rename(roi = iteration01, wts = iteration02)
print(kappa_df)
table(kappa_df$roi, kappa_df$wts)
kappa2(kappa_df, "unweighted")$value
```


function not working to build the kappa. do it by hand

Kappa are :
CD3_tumor 0.4171779  
CD8_tumor 0.6885246  
CD3_CD8_tumor 0.8938547   
CD3_stroma 0.379085   
CD8_stroma 0.4864865   
CD3_CD8_stroma 0.5026178  

