---
title: "Report June 11th 2020"
author: "Christelle M Colin-Leitzinger"
date: "6/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.width = 10, fig.height = 7)
```
<br>

***
## Report

```{r library, include=FALSE}
library(drake)
library(tidyverse)
```

```{r}
loadd(clinical_data, ROI_tumor ,ROI_stroma ,TMA_tumor ,TMA_stroma, 
      TMA2_tumor, TMA2_stroma, TMAcases_remove,
      common_ROITMA_IDs)
```
##Data
Loading and cleaning of clinical data, TMAs and ROIs data.
I made sure that all the present in the TMAs and ROIs files were removed.
I also removed the 4 cases which were excluded.
```{r}
# III-Remove the TMA IDs from patient excluded from the study
# Should only be done for TMAs
# Plus remove TMA with no IDs = controls images
uid <- paste(unique(TMAcases_remove$Subject_IDs), collapse = "|")
TMA_tumor <-
  TMA_tumor[(!grepl(uid, TMA_tumor$suid)), ] %>% 
  filter(!is.na(suid))
TMA_stroma <-
  TMA_stroma[(!grepl(uid, TMA_stroma$suid)),] %>% 
  filter(!is.na(suid))

# Did it for ROIs too in case  #------------------ All good so don't run anymore but still create suid 
ROI_tumor$suid <- substr(ROI_tumor$image_tag, start = 10, stop = 15)
# ROI_tumor <-
#   ROI_tumor[(!grepl(uid, ROI_tumor$suid)), ]
ROI_stroma$suid <- substr(ROI_stroma$image_tag, start = 10, stop = 15)
# ROI_stroma <-
#   ROI_stroma[(!grepl(uid, ROI_stroma$suid)), ]

# Cleaning
rm(TMA2_tumor, TMA2_stroma, uid, fct_name_repair, # roir_import,
   data_import, roit_import, rois_import, tmat_import, tmas_import,
   tma2t_import, tma2s_import, common_ROITMA_import, # tmar_import, 
   TMAcases_remove, case_remove_import)


#-----------------------------------------------------------------------------------------------------------------

# 1.	Calculate the % tumor and % stroma within each ROI/TMA core. 
# Provide the mean, median, and range of the % tumor and % stroma 
# for the TMA cores, intratumoral ROIs, and peripheral ROIs. 
# Also assess the variation by case in terms of the % tumor and % stroma. 



ROI_global <- merge.data.frame(ROI_tumor, ROI_stroma,
                               by.x = "image_tag", by.y = "image_tag",
                               all = TRUE) %>% 
  mutate(total_cell_number = tumor__total_cells + stroma__total_cells
         ) %>% 
  mutate(percent_tumor = round((tumor__total_cells / total_cell_number)*100, 2)
         ) %>% 
  mutate(percent_stroma = round((stroma__total_cells / total_cell_number)*100, 2)
         ) %>% 
  mutate_at(("intratumoral__i__vs_peripheral__p_.x"), ~ case_when(
    intratumoral__i__vs_peripheral__p_.x == "p" ~ "Peripheral",
    intratumoral__i__vs_peripheral__p_.x == "i" ~ "Intratumoral")
    ) %>% 
  mutate(suid.x = factor(suid.x))

TMA_global <- merge.data.frame(TMA_tumor, TMA_stroma,
                               by.x = "image_tag", by.y = "image_tag",
                               all = TRUE) %>% 
  mutate(total_cell_number = tumor__total_cells + stroma__total_cells
         ) %>% 
  mutate(percent_tumor = round((tumor__total_cells / total_cell_number)*100, 2)
         ) %>% 
  mutate(percent_stroma = round((stroma__total_cells / total_cell_number)*100, 2)
         ) %>% 
  mutate(suid.x = factor(suid.x))
```

```{r }
head(clinical_data)
# summary(TMA_tumor)
# summary(TMA_stroma)
# summary(ROI_tumor)
# summary(ROI_stroma)
```
I merged tumor and stroma data using image_tag into the same dataframe.
**TMA_global**
```{r }
dim(TMA_global)
```

**ROI_global**
```{r }
dim(ROI_global)
```

## Tables

## Including Plots
```{r}
variations_TMA <- group_by(TMA_global, suid.x) %>% 
  summarize(mean_tumor = mean(percent_tumor), mean_stroma = mean(percent_stroma)) %>% 
  mutate(ID = seq(1:nrow(.)))# %>% 
# mutate(suid.x = factor(suid.x))

variations_ROIip <- group_by(ROI_global, suid.x, intratumoral__i__vs_peripheral__p_.x) %>% 
  summarize(mean_tumor = mean(percent_tumor), mean_stroma = mean(percent_stroma))
setDT(variations_ROIip)[, ID := .GRP, .(suid.x)]

variations_ROI <- group_by(variations_ROIip, suid.x) %>% 
  summarize(mean_tumor = mean(mean_tumor), mean_stroma = mean(mean_stroma)) %>% 
  mutate(ID = seq(1:nrow(.)))

variations_TMA$tumor_variation <- variations_TMA$mean_tumor - mean(TMA_global$percent_tumor)
variations_TMA$stroma_variation <- variations_TMA$mean_stroma - mean(TMA_global$percent_stroma)
variations_ROIip$tumor_variation <- variations_ROIip$mean_tumor - mean(ROI_global$percent_tumor)
variations_ROIip$stroma_variation <- variations_ROIip$mean_stroma - mean(ROI_global$percent_stroma)
variations_ROI$tumor_variation <- variations_ROI$mean_tumor - mean(ROI_global$percent_tumor)
variations_ROI$stroma_variation <- variations_ROI$mean_stroma - mean(ROI_global$percent_stroma)


```
You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
